\documentclass[10pt,oneside]{book}
\usepackage[utf8x]{inputenc}
\usepackage[english]{babel}
%%%%%
% Make 1.0" margins on all sides
\usepackage[top=1.0in,bottom=1.0in,left=1.0in,right=1.0in]{geometry}

%opening
\begin{document}
\title{Saving Connor}
\date{October 5, 2005}
\author{Lightning on the Wave \and Assembled in \LaTeX \\ by Tyler Davis \\ \texttt{tydavis@gmail.com}}
\maketitle
\tableofcontents

% \textbf{Story:} Saving Connor\\
% \textbf{Storylink:} \url{https://www.fanfiction.net/s/2580283/1/}\\
% \textbf{Category:} Harry Potter\\
% \textbf{Genre:} Adventure\\
% \textbf{Author:} Lightning on the Wave\\
% \textbf{Authorlink:} \url{https://www.fanfiction.net/u/895946/}\\
% \textbf{Last updated:} 10/05/2005\\
% \textbf{Words:} 81263\\
% \textbf{Content:} Chapter 1 to 22 of 22 chapters

\chapter{Brother's Keeper}\label{chapter-1-chapter-1}

``What are your vows, Harry?''

Harry knew what they were, even though he was only five. He whispered them as
his mother held him over his brother's bed, and his mother said them with him,
murmured hypnotic words that Harry had heard his whole life.

``To keep Connor safe. To always protect him. To insure that he lives as
untroubled a life as he can, until he has to face Lord Voldemort again.''
There was the pause for breath that his mother always took, as though she were
frightened. Harry waited until she started speaking again, and then joined his
voice to hers. ``To be his brother and his friend and his guardian. To love
him. To never compete with him, never show him up, and never let anyone else
know that I'm so close to him. To be ordinary, so that he can be
extraordinary.''

Harry remembered stumbling on that last word, back on his and his brother's
birthday, when his mother had first coached him into saying it and not just
listening to her say it. He'd never asked what it meant, though. His parents
thought he was smarter than he really was, sometimes. But now he wanted to
know, so he turned around as his mother bore him towards the other bed and
asked.

``Mum, what does extraordinary mean?''

Lily Evans Potter hesitated for a long moment, looking down at Harry as though
she didn't know how to answer that. Then she smiled faintly, and shook her
head, and sat on the bed beside him. Harry wriggled under the covers. He kept
his eyes on her face, never taking them off. They both had eyes the same
extreme, bright green, while Connor and their father James shared bright hazel
eyes. Harry considered, in the secret box of his thoughts where he put
everything he couldn't say aloud, that he and his mother had a special bond
because they had the same eyes. He knew it wasn't really true, of course, not
when Connor was the Boy-Who-Lived, but Harry liked to pretend, sometimes.

Lily smoothed back his fringe from the scar on Harry's forehead, absently. It
was shaped like a lightning bolt. Harry knew how he'd gotten the scar---from a
bit of falling rock when Voldemort attacked, on that horrible night he
couldn't quite remember, when Lily and James had been lured away from home by
the idea that their twin sons had already been kidnapped. Voldemort had
stamped in, and shot the \emph{Avada Kedavra} curse at Connor, and Connor had
deflected it and destroyed him. He had a cut shaped like a heart on his
forehead, a curse scar. Thinking about that night, Harry realized he knew the
meaning of ``extraordinary'' even before Lily whispered it to him.

``It means---special, Harry. It means not ordinary. It means standing out from
the crowd.'' She hesitated again, as though she didn't know how to speak the
next words.

``And I have to be ordinary, so that Connor can be special,'' said Harry,
nodding. He understood. His little brother would need help from him. It wasn't
an easy destiny, Lily had explained to him every day, being the one expected
to defeat Lord Voldemort from scratch. Voldemort wasn't really gone, and would
come back someday. Connor had to be ready for that day, had to
\emph{concentrate}, which was another word that Harry had learned early. So
Harry would help him \emph{concentrate} by being ordinary.

He didn't know just how that would work yet, but he would find out. Whenever
he looked over at Connor, he felt a fierce surge of love for his little
brother. Connor was special, and he was going to be special. Harry would help
him.

When he glanced back at his mother, she was smiling at him, that secret little
smile that only the two of them shared. She nodded, whispered, ``Yes, Harry,
that's it exactly,'' and kissed him before she stood and walked out of the
room.

And Harry knew then, in a rush of joy, that their special bond wasn't fake
after all. His mum trusted him to take care of his little brother. That was
important. That was special.

He turned and bowed in the direction of Connor's bed, a gesture he'd learned
about from an old story his godfather had told him the other day. ``I'll
protect you, Connor,'' he said. ``I'll be your knight, and you can be king.''

Connor sighed in his sleep.

Harry grinned, knowing he wouldn't wake up---Connor was too heavy a sleeper
for that---and closed his eyes.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``Good try, Harry! You almost caught the Snitch.''

Harry grinned and landed lightly, stabbing his feet into the dirt so that he
wouldn't accidentally take off again. He loved to fly so much that he was
quite capable of shooting himself up to the sky without meaning to. ``Thanks,
Connor,'' he said, climbing off the broom and nodding to his brother. ``I'll
keep trying. I'm sure with you for a coach, it won't take me long to get
better.''

Connor, already off his own broom, bounced over and messed up Harry's hair,
not that it needed the help. ``You'll get better,'' he said. ``Next match.''
Then he tossed the fluttering Snitch into the air, ran over to his broom,
leaped on it, and started chasing the little golden ball.

Harry leaned back on the sun-warmed grass and watched. Connor was already
fifty feet off the ground, then sixty. Then he spiraled down in a daring dive
that just missed the Snitch and the grass both. He pulled out of it, and Harry
let out an anxious little breath. He'd showed his brother how to do the dive
himself, because Connor had to be a good flyer, but he couldn't help the dread
in his throat just in case \emph{this} was the time that Connor crashed.

A hand fell on his shoulder, and Harry rolled his head back, smiling when he
saw who it was. ``I didn't know you were here, Padfoot,'' he said, and sat up
to hug Sirius. His godfather hugged him back, one-armed, and sat down beside
him. His eyes were also on Connor. Firmly convinced that that was the way it
should be, Harry leaned against Sirius and closed his eyes.

``James wanted to take your mother out somewhere private,'' said Sirius
finally, and then leered at Harry.

``Sirius! Ew.'' Harry wrinkled up his nose. He didn't really want to think
about his parents having sex. Their eleventh birthday was tomorrow, and they
would receive their Hogwarts letters then. Harry knew that his parents were
probably feeling anxious about this last month before they had to let Connor
go out into the big wide wizarding world, but he would just as soon not know
what they were doing to settle their nerves.

Sirius messed up his hair in turn. Harry was resigned to it by now.
``Anyway,'' Sirius added, ``they wanted someone here to look after you. Just
in case.''

Harry stiffened and drew away. ``I look after Connor,'' he said. ``That's what
I do.''

Sirius smiled gently at him. ``I know, Harry, but Connor's still a child.'' He
sighed and looked up as Connor missed the Snitch and flipped his broomstick
half upside-down to chase after it. ``And even though Peter---'' he spat the
name ``---is in Azkaban, there are other Death Eaters who might be looking for
a chance to harm him.''

Harry nodded. He knew all about the Death Eaters. His parents had given him
the names of the ones they knew for certain and had him study their families
and their powers, and practice a few essential spells until he was almost good
enough to stop Death Eaters. \emph{Almost}, Harry repeated to himself. He
wanted to think he was good enough, already, but that was hard to say until he
actually faced a Death Eater in battle. Besides, he had to practice in secret.
He was a little quicker than Connor to pick up spells, sometimes, and he
couldn't embarrass or show up his brother.

\emph{A little quicker, that's all,} he protested, and leaned back again to
watch Connor once again catch the madly fluttering Snitch. \emph{And I'm a
little quicker on the broom, too, but I always hold myself just under his
speed. He'll never know. And no one else ever will, either. They'll all think
he's the best.}

That pleased Harry. Quite apart from giving Connor his place in the sunshine
---which was what he deserved, after being marked for death by Voldemort---the
extra advantages would come in handy someday. A Death Eater who thought Harry
was slow on a broom might underestimate him, and then Harry would slam into
him and take anyone trying to hurt his brother down.

``Merlin, Harry, you act like the weight of the world is on your shoulders
sometimes,'' said Sirius, breaking his reverie. ``Are you all right?''

Harry hunched for a moment, then relaxed. He reminded himself that Sirius, and
Remus too, thought that he was just being earnest and childish when he talked
about protecting his brother. They didn't know the truth, like his mum did. No
one would know the truth. Harry would be ordinary.

``I'm fine,'' he said. ``And I'm not carrying the weight of the world on my
shoulders. That's for Connor.''

Sirius's face softened, and he once again watched Connor until he caught the
Snitch. ``He's going to have a rough road ahead of him,'' he agreed.

\emph{Not as rough as it could be,} Harry promised himself, drawing his knees
up to his chin and putting his arms around them. \emph{I'll always be at your
right shoulder, Connor. I've got your back, and no one will see me until they
try to hurt you and I hurt them instead.}

It was life. It was a way to be ordinary and yet ready to defend the
Boy-Who-Lived. It was a way to make sure that Connor survived.

Harry listened to his twin, destined for a life of hardship and pain,
laugh, and couldn't imagine anything he wouldn't sacrifice to keep that
laughter intact.

\chapter{Meetings, Cordial and Otherwise}\label{chapter-2-meetings-cordial-and-otherwise}

``Now, Connor, be good for your professors. Do you have Godric? Good.
Keep him in his cage for right now, at least until you get to Hogwarts.
James, you are \emph{not} sending the Invisibility Cloak with him. Yes,
I saw you take it out of your pocket. Put it back right now. He doesn't
need that in his first year\ldots{}''

Harry trailed behind his parents as they escorted Connor towards
Platform $9 ^3/_4$, smiling as he listened. Normally his mother wasn't this
fussy, but normally she had Connor right at home where she could keep an
eye on him, or have Harry or Sirius or Remus keep an eye on him, and
could pull her wand instantly if someone who might be a Death Eater
approached. In the shouting, clamoring bustle of King's Cross, filled
with Muggles as well as wizards, there were more opportunities for
someone to draw near and take aim at Connor.

Harry wasn't that worried. He had tried a few of his favorite spells
with his new wand the moment he bought it, and to his relief, they
worked even better with that than they had with the practice wand. He
even thought he could trust his snowy owl, Hedwig, to spy out danger if
it approached. She sat in her cage on top of his trolley right now,
staring in several directions with bright golden eyes. She seemed more
alert than Godric, Connor's black eagle-owl, who either sat with his
eyes closed or craned his head around to stare at people Harry knew from
the set of their faces were innocent.

``Harry.''

Harry looked up, startled. They'd almost reached the magical wall that
permitted passage between the station and the Platform, and he hadn't
noticed his mother dropping back to walk beside him. Of course, she was
an automatic non-threat, like Sirius or Remus. Harry resolved to be more
careful, though. There wouldn't be any automatic non-threats on the
train.

``Yes, Mum?'' he murmured.

Lily hesitated for a long moment, as though she were thinking of giving
him the stream of advice she'd handed Connor. Harry waited patiently.
She was only going to say one thing, and he knew what it was. But, at
the same time, he needed to hear it. It was confirmation of his purpose,
of his loyalties and his position in the world.

``Take care of your brother,'' said Lily at last, and something coiled
and tense in Harry's head breathed out a sigh of relaxation.

``Of course, Mum,'' he said.

Lily's hand swept across his fringe, stroking the scar that Harry knew
was a distorted, imperfect reflection of his twin's curse scar. ``You're
the lightning bolt,'' she whispered. ``You strike hard and fast, and you
don't leave any remains behind. Connor's the heart. Protect his
innocence, Harry. Make sure that he's still pure and unspoiled at the
end of it all. Headmaster Dumbledore said that Connor would have the
power the Dark Lord knows not. That's his ability to love, it has to be.
But if he has to grow up too fast, he'll lose it.'' She bent down and
kissed Harry on his scar. ``Be sure that he can stay a child for just a
little while longer.''

``I will, Mum.'' Harry forced the words out through the lump in his
throat. She had never said anything like that to him, ever. It was
Connor's scar that was significant, Connor's scar that marked him for
death and glory. To think that he was part of what his brother was a
part of, even for a little while\ldots{}

Lily looked as if she would have said something more, but Connor yelled
from ahead. ``Harry, come on! The train's getting ready to leave!''

Harry and Lily exchanged smiles. Connor was innocently excited about
going to Hogwarts, and perhaps anticipating, just a little, what they
would make of the Boy-Who-Lived. He saw it as such a big change in the
life he'd lived so far, as if everything would be different and nothing
the same ever again.

In some ways, Harry thought, that was true. Connor would be doing real
spells now, much more often than he'd done them at home. He would have
to start growing up, losing his innocence, learning to love not just his
parents and Harry and Sirius and Remus, but the whole wizarding world
he'd have to protect someday.

Harry was glad that his own life was so simple in comparison. His
responsibility was what it had always been: protect Connor.

He touched his mother's hand one more time, then turned and walked
through the barrier onto the platform. Hedwig hooted softly as he did
so, as if impressed by the size and noise of the train.

Harry kept an eye on his brother as they boarded, but Connor luckily
chose an empty compartment. Harry slid in behind him and raised his
eyebrows at him.

Connor grinned cheekily back. They didn't actually look much like twins,
Harry thought absently, the old insight brought home to him with new
force because of seeing his brother in an entirely new place. Connor had
black hair, but it was less messy than Harry's, so that his scar was
usually half-visible, the lower curve of the heart just peeking out. He
had James's hazel eyes, and Lily's lack of need for glasses, and more of
James's looks.

\emph{Even that can be an advantage,} Harry thought as he took a seat
across from his brother. \emph{There's no possible way a Death Eater can
mistake him, of course, but they might also not think I'm his brother.}

``Aren't you excited?'' Connor asked him.

Harry smiled. ``Of course I am,'' he said. ``But the best part is
watching you bounce around like a Chocolate Frog.''

``I am \emph{not} bouncing,'' said Connor, bouncing.

``Yes, you are.''

``Am not.''

``Yes, you are.''

``Am not.''

So they continued, enjoying the completely childish argument that their
parents would have been yelling at them to stop inside two minutes.
They'd probably been at it for ten minutes when the door slid open.
Harry turned to face it at once, making sure that his expression was
welcoming and pleasant, just like Connor's innocent smile. His hand was
on his wand, but that hung in the loose pocket of his school robes,
which he already wore, and no one else had to know.

The boy in the open door stood blinking for a moment, as if he had not
expected two of them. Then he moved forward. Harry studied his red hair
and worn, if clean, clothes, and then slowly took his hand off his wand.
The boy was almost certainly a Weasley, and the whole of that family was
loyal to Dumbledore and fought for the Order of the Phoenix. The current
mother had even lost relatives to Voldemort. Harry could trust this boy
not to hurt Connor, at least until he proved otherwise.

``Hi,'' said the boy, and sat down across from Connor, next to Harry.
``I heard that Connor Potter was in this compartment. Is that you?''

Connor grinned and lifted the fringe so that the boy could see the
heart-shaped scar. The Weasley blinked and gaped in awe, then stuck out
a hand, grinning. ``My name's Ron Weasley. It's brilliant to meet you.
Do you know my parents? I think they know yours. Mum said something
about visiting you once, and Dad said it was restricted, but\ldots{}''

Harry sat back and let the chatter wash over him, watching through
half-lowered eyes as his brother responded, skittish at first, and then
gaining confidence as he saw how fascinated with his presence Ron was.
Connor had never been around other children his own age, any more than
Harry had. It really was too dangerous for others to visit them, at
least as long as Voldemort had a chance of coming back. That was one of
the many reasons Harry was pleased they were going to Hogwarts now.
Connor would have many friends. Not \emph{all} of them could be the
children of Death Eaters assigned to spy on him, though Harry was
willing to think that many were, especially if they came from Slytherin
House.

The door of the compartment abruptly slid open again, and another boy
stood just inside it. Harry tensed. This wizard had blond hair and the
practiced bored expression of a pureblood, and two other wizards flanked
him like house elves. He glanced at the Weasley and sneered, and Harry's
hand went to his wand.

``You're the Boy-Who-Lived,'' he said to Connor. ``Aren't you.'' His
tone, a lazy drawl that was too obviously forced, didn't make it a
question.

Connor nodded, his shoulders tense. Harry gave his brother full points
for observation. He didn't know who this was yet, though he had his
suspicions, and Connor, sheltered from the outside world, disliked the
boy on principle. A good sign of an innocent heart.

``My name's Draco Malfoy,'' said the boy, and stepped forward, hand out
as if he expected Connor to actually shake it.

Harry stood, fully prepared to speak a hex. Lucius Malfoy had stood high
in Voldemort's circle, and then escaped Azkaban on the flimsiest of
excuses. Of all the children attending Hogwarts this year, his son was
the one Harry would choose for Most Likely to Try and Kill Connor.

Malfoy gave him an odd glance, then laughed. ``And who is this?'' he
asked. ``Someone else paying court to you, Potter, like the Weasley?''

\emph{That's it,} Harry thought, as he saw a familiar fire ignite in
Connor's eyes. \emph{He's just lost his chance.}

``This is my brother Harry,'' said Connor, also standing up. He was
slightly taller than he looked, and when he turned his gaze on Malfoy,
the man he would become was visible. Harry nearly stopped breathing with
admiration. If Connor had to lose a piece of his innocence today, he was
doing so for a worthy cause. ``And this is Ron Weasley, my friend.
You're never going to be, so don't insult your betters.''

Malfoy froze for a moment, his eyes wide. Harry peered at him, wondering
why.

Then he understood. Malfoy was an innocent in his own way, it seemed. He
had come into the compartment as he probably walked everywhere,
swaggering and drawling, and expected Connor to accept him as everyone
must have accepted him. The Malfoys would have raised their son around
other purebloods, groomed into perfect statuary by their parents to show
obedience to the rich and powerful---and the Malfoys were both. Why
should the Boy-Who-Lived be different from the children Draco had known
all his life?

Harry sighed, feeling an odd pity for the boy, and took his hand off his
wand. And then he heard Connor snicker.

``Not that I'd want you to be my friend,'' he said. ``You have an ugly
name.''

``Connor!'' Harry cried, shocked. Defending the innocent was one thing.
Hurling a childish insult was quite another. The purebloods were part of
the wizarding world, too, and Connor should have been above the kind of
retaliation that Harry fully expected from someone like Draco. The hurt
was still visible on Malfoy's face; he'd been too startled to hide it.
Connor could have made the rebuke sting a little less with the right
words, and been on the road to gaining a valuable ally. These were
definitely \emph{not} the right words, for all that they set Ron to
laughing.

They closed off that little hurt look on Malfoy's face. He straightened,
and the wizards with him looked to him for orders. But Malfoy merely
glared down his nose at Connor, said, ``I should have expected that
someone with a Mudblood for a mother would have no sense of
\emph{proper} manners,'' and swept out the door.

Connor cried out, and Ron said, ``That's tough, mate, what he said about
your mum\ldots{}''

Harry walked out the door of the compartment after Malfoy. What he'd
said had been harsh, but Connor had provoked him. Harry knew the rules
of wizarding courtesy from his father and Sirius, purebloods both.
Malfoy deserved an apology.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Draco rubbed his forehead as he walked. He'd got a headache in five
seconds, being inside that compartment with such a powerful wizard.
Potter's magic hummed and sang around him, and filled the air with a
faint ringing vibration that Draco, like all properly trained Malfoys,
could feel. It made his skull hurt. Clearly, Draco reflected, he'd have
to put up tougher shields once he got to Hogwarts. He'd have to do that
anyway, with so many other wizards around, but he blamed Potter for
giving him a headache this early.

``Malfoy.''

Draco glanced over his shoulder, and then stared. Behind him stood the
other wizard, the one Potter had claimed was his brother. He'd been so
quiet that Draco had barely noticed him, and had included him in the
insult tossed at the Weasley mainly by force of habit. He had dark hair
even messier than Potter's, and green eyes behind ugly glasses.

And he made the air around him sing.

Draco's eyes narrowed further, and then further again. ``Is this some
kind of bloody trick?'' he snarled, taking a step back towards---Harry,
that was his name. He wouldn't have used such language ordinarily, but
he hated being insulted or fooled. His father would have understood.
``You're the Boy-Who-Lived, aren't you?''

Harry blinked. ``What?'' But he wasn't as confused as he pretended to
be. Around him, his magic tensed and tightened into a single sharp
arrowhead aimed straight at Draco.

Draco ground his teeth. ``You're the Boy-Who-Lived,'' he said. ``Not the
other one. Did you think I'd think it was \emph{funny}, and come
crawling back to you? Malfoys don't crawl.''

``Not even for the Dark Lord?'' Potter murmured. His eyes sparked with
lazy amusement.

Beyond infuriated, Draco tried to turn around again, but Potter's hand
caught his arm. Vincent and Gregory started forward, but halted when
Draco shook his head slightly. They were well-trained, but there was no
way they were ready to face a wizard of Potter's power. Draco stood
stiffly, fully expecting a hex he knew he couldn't stop.

So, of course, he was utterly astonished when Potter passed one hand
across his brow, lifting up the fringe enough to let Draco see that his
scar was a lightning bolt, not a heart, and murmured, ``In Merlin's name
I ask that you forgive me, for my unfair, hasty words, and my brother
for his. I do not know if you will accept these terms, but I ask them:
truce between us, and neutrality henceforth.''

Draco stared again. He was spending an unworthy amount of time doing
that today. But all the words were correct, and Potter's face was
earnest when he offered them, his eyes meeting Draco's steadily. It
didn't, of course, stop that ringing, impossible power, compacted and
folded into perfect obedience, which still continued to give Draco a
headache, but perhaps it didn't need to.

This Potter knew pureblood courtesies. This Potter had come to offer
them to Draco. This Potter let go of his arm the moment the ceremony was
done and backed off a cautious distance, his magic swirling in lazy
patterns of sound, ready to attack but not poised as it had been
before---the absolutely proper thing to do, given that Draco hadn't
responded yet.

This Potter hummed and sang with pure \emph{magic}, and if he wasn't the
major source of the power that Draco had sensed in the compartment, he
would eat his own hand.

And yet he wasn't the Boy-Who-Lived.

Draco had two choices in that moment: he could continue to believe he
was being tricked, and stomp away in righteous indignation, or he could
accept what was offered and see what happened. Perhaps Connor Potter was
more powerful than Harry. Perhaps he was so powerful that Draco couldn't
sense him.

Or perhaps Harry, who, after all, couldn't feel his own strength, didn't
know anything about the aura he carried, and had even more hidden
depths, ones that didn't have anything to do with spells.

Draco knew what he would prefer to be true. But he would at least take
the chance offered, and see what happened.

He laid a fist over his heart, bowed, and extended a hand. Harry
actually exhaled with relief when he took it.

``Thank you,'' he said, and bowed back, and walked back into the
compartment without trying to explain himself. That was also absolutely
proper, Draco thought, watching him go with a hunger that had no name
yet. He would have to write a letter to his father when he arrived at
the school. He wondered what Lucius would make of it.

``Why did that happen?'' Vincent whispered. His voice was tinged with
awe. He couldn't feel Harry, but he knew that Draco wouldn't have
accepted an apology from just anyone.

``I don't know,'' said Draco. ``Not yet. But I'll tell you one
thing\ldots{}'' He left it at the end of a deliciously long pause.

``Yeah?'' Gregory asked, leaning forward.

Draco smiled at the compartment door, which was now closed. ``There's
going to be a Potter in Slytherin.''

\chapter{Arguments With the Sorting Hat}\label{chapter-3-arguments-with-the-sorting-hat}

Harry listened to the murmur of awe all around him as the first-years
rode the boats across the lake towards Hogwarts. He was busy studying
the castle, too, and he had to admit it was beautiful, a welcoming blaze
of light in the by-now-absolute darkness.

He suspected he was looking for slightly different things than the rest
of the students looked for, though. They would gasp and exclaim at the
windows, and the enchanted ceiling of the Great Hall when they reached
it, and the soaring turrets of stone that broke the horizon in odd
places. Harry studied the thickness of the walls, the width of the
windows, and the crackling, glowing haze of those spells he had managed
to train himself to see. Hogwarts looked as if it were on fire in that
kind of sight, though the fire did not consume the stone but slowly and
continually shifted on top of it, altering colors. And Harry was sure
that many spells he could not see also defended the school. They would
range from new to old, some doubtless laid down by the Founders
themselves.

But were they enough? Would they keep Connor safe if Death Eaters came
hunting him? If Voldemort did? If an accident nearly deprived the world
of the Boy-Who-Lived, before he got the chance to strike the final blow
in the battle?

Frowning, Harry barely noticed Connor nudging him in the side to get him
out of the boats as they slid to a stop. He did get out, but it was
training that kept him close to his brother, and not attention or
anticipation. He knew all about the speech that someone---the Deputy
Headmistress McGonagall, from the sound of it, and his future Head of
House---was giving to the first-years. He knew about the Sorting Hat and
the ghosts who swooped through the waiting room and the blend of surging
excitement and nervousness that consumed his peers like an echo of the
spells on the castle.

He did not know how much he could trust Hogwarts yet. Until he could, he
had to keep an eye on it.

``You aren't frightened, are you?''

Harry blinked and turned his head, at least once he could be sure that
the question was addressed to him. He didn't know what to make of the
tone once he found Malfoy standing next to him, staring at him intently.
Was Malfoy taunting? Asking a serious question? Asking it in admiration?
His eyes and voice gave nothing away anymore. Harry found himself
relieved. He would prefer not to have to smooth things over between
Connor and the possible future Death Eater all the time.

``No,'' Harry said, and faced the doors again.

They swung wide, which prevented Malfoy from asking anything else.
McGonagall herded them along beneath the enchanted ceiling, over a stone
floor, beneath the gazes of both professors and other students. Harry
heard constant gasps from around him, even when the Sorting Hat began to
sing, and wondered why. The only overwhelming, and therefore
interesting, things were the lines of spells that danced down from the
ceiling and curled like ivy around the student tables. He knew only one
or two of them, such as the ones that would soothe thoughts which might
lead to deadly displays of magic. He would have to learn the others.

``Abbott, Hannah!''

Harry watched as the girl trotted forward, placed the Hat on her head,
and got Sorted into Hufflepuff. He nodded. The Sorting Hat worked
exactly the way that his parents had told him, then, and any possible
danger was removed. He leaned sideways to watch the green tracery of a
spell snake around the Slytherin table. He wondered what it did. Its
signatures were similar to those that enclosed a defensive spell, but it
had sharp projections from the sides, as though it were meant to act
offensively.

His attention returned to the Sorting only in fits and starts, such as
when there was an extremely long silence between ``Granger, Hermione!''
and the Hat's announcement. Harry leaned forward, curious, to see the
girl sitting firmly beneath the Hat. He could hear a faint murmur of
voices, and thought she was arguing with it.

``GRYFFINDOR!'' the Hat shouted.

Granger put it back down on its stool and trotted away, looking very
pleased with herself. Harry concealed a smile .So she was going to be in
Connor's House, then. He hoped she would become his friend. Someone so
determined might be a good ally. And she had a name he didn't recognize
as belonging to any wizarding family, which meant she was a Muggleborn,
which meant she would have more reason than some of the others to be on
Connor's side.

He also paid attention when a name he recognized came up, and was
pleased beyond words to see Neville Longbottom go into Gryffindor. Lily
had told him the solemn story of how Neville's parents had lost their
minds to the Lestranges' Cruciatus curses. Harry had wondered if their
courage would pass into their son. It seemed it had.

Malfoy went into Slytherin. Harry was absolutely not surprised. He
didn't understand why Malfoy felt the need to smirk at him as he walked
over to the Slytherin table, though, nor why he sat down and kept
watching until Harry grimaced at him and turned away.

Then came the moment he'd been waiting for.

``Potter, Connor!''

The murmurs started almost at once. Harry saw his brother flush and
stumble a bit as he hurried forward to the Hat, as if he hadn't expected
this. Of course, he had, but it was one thing to imagine it and another
to hear it, Harry thought, heart aching with sympathy. Luckily, Connor
made it to the stool despite the voices that followed him.

``Is that really him?''

``\emph{The} Connor Potter?''

``Can you see his scar?''

``I don't know, he looks smaller than I imagined him\ldots{}''

Connor put the Hat on his head and closed his eyes. Harry could see his
brother's lips moving, and knew the kind of reassurances he would try to
murmur to himself. Then he went still, and Harry knew the Hat's voice
was speaking into his head.

It lasted a very short time, as Harry had known it would, but that
moment still had claws, and they prickled all up and down his back as he
waited.

``GRYFFINDOR!''

The Hall erupted into noise---cheers from the Gryffindor table and
relieved shouts from the others, all except Slytherin. Harry nodded as
Connor took the Hat off his head, beaming. Of course he was essentially
good. He had defeated Voldemort, hadn't he? But this was the first time
that someone outside his family had ever judged Connor. It must feel
good to be told that his family's instincts were right, Harry thought.

Connor settled at the Gryffindor table and then turned around and
grinned at his twin. Harry smiled at him and walked forward as
McGonagall called his name.

The Hat settled over his ears, and chuckled into his mind. \emph{You
already think you know your House, don't you?}

\emph{I think so,} Harry responded, calmly. His mother had told him that
he could think and the Hat would hear him. It was valuable advice, as
his enemies might possibly be able to gain something of Harry's private
thoughts if he spoke aloud. \emph{I'm going into Gryffindor, to protect
my brother.}

\emph{You} want \emph{to go into Gryffindor,} the Hat corrected him.
\emph{That doesn't mean that you wouldn't be better-suited for another
House.}

Harry had the odd, uncomfortable sensation of the room spinning around
him and turning sharp-edged, as though the Hat had put his vision into
another part of his brain while it looked at his memories. Then it said,
\emph{No one can question your loyalty. Or your courage---how many
children are prepared to die for their brothers at eleven years old?}
For some reason, it sounded sad about that, but Harry didn't get the
chance to question it. \emph{Or your intelligence, for that matter, to
learn so many spells so young.}

\emph{But what holds you together, Mr. Potter, is your cunning, your
care, your ability to hide what you really are and your determination to
succeed. I think you're hiding better than most people will ever know,}
it added cryptically.

Harry didn't care about that last sentence; his mind was on the one
before it. \emph{But you can't mean to put me in---}

``SLYTHERIN!'' the Hat boomed cheerfully.

For one flaming moment, Harry thought about arguing. He was supposed to
be in \emph{Gryffindor}, that's where he \emph{belonged,} that's what
they'd \emph{planned} on, and how was he supposed to \emph{protect} his
brother when he wouldn't even see him for large portions of the day? The
Hat had known all that, and it still put him elsewhere. Harry wanted to
scream or shout. For the first time in years, he thought he might even
want to cry.

But then he stifled the impulse and stuffed it back down into the small
and secret box of his thoughts. No, he couldn't protest. That would call
attention to himself. Besides, there might be advantages to being in
Slytherin. He'd have access to the children most likely to belong to the
opposite side. He didn't think he could pretend to be one of them, ever,
but simple proximity and familiarity might make them careless around
him.

He took off the Hat to a moment of dead silence, as he'd expected. Harry
schooled his features into calmness and faced the Slytherin table. He'd
walk over there, and the silence would continue, and then the Sorting
would start again. This would be only a small bump in the road, he
fervently hoped. There were other students to put into their Houses. If
Connor---

Then the silence broke.

Harry stared as Draco Malfoy stood up from the Slytherin table and began
to applaud. He did it as coolly as if this happened every day of his
life, and his eyes were fixed on Harry's face, not glancing around to
see what kind of attention he could draw. A few other Slytherins
staggered to their feet and joined in, but, mostly, Harry walked to the
table under the aegis of exactly one pair of clapping hands, making the
entire sorry performance even more noticeable than it already was.

Then Malfoy had the audacity to wave the boy sitting next to him over,
so that Harry had an empty place to sit down. Harry took it, his face
flaming, since he suspected that avoiding him would only prompt Malfoy
to do something even more dramatic and ridiculous in the name of---what?

``Do you think it's funny to embarrass me?'' Harry hissed at him. He
could hear the Sorting begin again, luckily. He could also feel his twin
looking at him from the Gryffindor table. Coward that he was, he didn't
think he could meet Connor's eyes yet, so he settled for glaring at
Malfoy, who only leaned back and smiled at him.

``I wasn't aware that I was embarrassing you,'' Malfoy drawled. ``I was
only welcoming the newest member of House Slytherin. I suppose that your
impeccable manners don't extend to a friendly welcome, then? For shame.
You're clearly different than I thought you were.'' His smile grew
wider, a smirk, and he watched Harry to see what he would do.

Harry recognized the baiting, but only had one choice, and he suspected
it was the one that would please Malfoy the most. He took a deep breath
and forced a smile. ``Of course not,'' he said. ``Forgive me. I
misunderstood. I thought I was going into Gryffindor with my twin.''

Malfoy leaned nearer to him, implying a familiarity that Harry didn't
think was there. ``Twins are different sometimes,'' he whispered. ``At
least, I always thought so. And I thought from the first moment we met
on the train that you would be a Slytherin.''

Harry jerked his eyes away from Malfoy and swallowed. \emph{Shit. What
did I do wrong?} he thought in misery. \emph{What kind of---of} thing
\emph{in me makes me a Slytherin so that someone else can see it? And
why didn't my family ever tell me?}

He still didn't feel up to looking across the room, even as Ron Weasley
became a Gryffindor, so he looked at the head table instead. He nodded
in gloomy unsurprise when he realized that Severus Snape, the head of
Slytherin House, was staring back at him. His father had told Harry all
about the rivalry between the Marauders and Snape when they attended
Hogwarts, but also about the wizard's debt that Snape owed James, and
that the scowling, snapping, sniping man was a member of the Order of
the Phoenix. Snape would help protect Connor, but he would hardly make
his life pleasant. And he didn't look pleased to have a Potter in his
House, either.

Harry abruptly hissed. His head hurt. He raised a hand and rubbed it
across his scar, then blinked when he brought it down and found the palm
smeared with blood. He shoved it under the table in confusion

Malfoy, of course, tried to grab his arm. ``Let me see.''

``No!'' Harry said, and twisted away. Confused, lost, needing
\emph{some} taste of home, he lifted his eyes and looked across the
room, to the Gryffindor table where he should have been, where Connor
and Ron sat in camaraderie.

Connor was staring at him, as though he hadn't stopped since the moment
Harry was Sorted. His eyes were big, and he shook his head back and
forth, back and forth. Harry winced and turned away again. It was the
first time he'd ever seen betrayal on his brother's face.

He breathed carefully to himself, ignoring Headmaster Dumbledore's
speech and the appearance of the food, at least until Malfoy leaned over
and said, ``Everyone's going to think you're sulking if you don't eat,
you know.''

\emph{I can't afford this,} Harry thought. \emph{I can't afford to draw
attention to myself. People will think too much about me, and they'll
not look at Connor as much as they should. I have to get control of
myself.}

It was his mother's voice that came back to him. ``\emph{You're the
lightning bolt. You strike hard and fast, and you don't leave any
remains behind. Connor's the heart. Protect his innocence, Harry. Make
sure that he's still pure and unspoiled at the end of it all.}''

Harry let out one last anxious breath, the last one he'd permit himself,
and then started eating. He could do this. It was only another challenge
to protecting Connor. No one had ever said it was \emph{easy.} Harry
tended to fling himself at challenges and batter them until they were
gone. He could do it with this one, too.

``Do you want some pumpkin juice, Harry?''

Malfoy had decided to address him by his first name? This was news to
Harry. But he managed to nod, and smile, and even say, ``Thank you,
Draco.''

Draco poured. Harry kept his eyes away from the Gryffindor table for
right now. He would explain to Connor that being put in Slytherin House
didn't mean his goals in life had changed, but he would do it tomorrow,
when they weren't in front of so many other people.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Draco wasn't stupid. He'd seen the blood come out of Harry's scar. He
certainly hadn't missed the panicked expression on Harry's face when the
Hat had announced him for Slytherin, or the way he had noticed his
brother and Snape and the Weasley all staring at him as if he'd grown a
second head.

Draco didn't care. Anticipation sweetened every mouthful of food he ate
and every move he made, especially now that he'd managed to shield
against Harry's pure power. He'd known what to expect at Hogwarts from
his father's tales of it, and what standards he was expected to carry
and maintain as a Malfoy. He'd known that the Boy-Who-Lived was coming,
and all things considered, he wasn't surprised that he and that
Gryffindor prat were probably going to wind up enemies. He had expected
to enjoy Hogwarts a little, but be bored out of his skull most of the
time.

No one had told him about Harry. For all Draco knew, his father didn't
consider the existence of the second Potter twin important.

\emph{But he is,} Draco thought, and poured the pumpkin juice so that
he'd have an excuse to keep watching Harry. \emph{He's powerful, and he
acts like he doesn't know it, and he certainly didn't} expect \emph{to
be put in Slytherin, so he doesn't know much about his own character,
either. I've got a leg up on Harry and Potter, and maybe even on Snape,
too.}

\emph{I don't know exactly what's going to happen next, but it's going
to be so much} fun.

\chapter{Detention With the Potions Master}\label{chapter-4-detention-with-the-potions-master}

``Wake up, Harry!''

``I'm already up, Draco,'' Harry said, sitting up and stretching lazily.
Draco, who'd flung back the green-and-silver hangings on Harry's bed,
looked startled for a second, but then grabbed his arm and dragged him
out. Harry sighed, but said nothing. Most of the time, the only people
who touched him were his parents, Connor, Sirius, and Remus. He would
have to get used to other people doing it, especially when said other
people were trying so hard to be his friends.

That was what he didn't understand, Harry admitted as Draco all but
dragged him through the common room, down the dungeon corridor, and
towards the Great Hall. Draco was acting---well, not like a Malfoy---in
his attempt to get Harry to pay attention to him. But there were other
people in Slytherin, including Vincent and Gregory, whom Harry had met
last night, perfectly glad to give Draco all the attention he wanted.
What could be gained by badgering \emph{him}?

\emph{Because you're the brother of the Boy-Who-Lived, of course,}
whispered a voice in his head that Harry distrusted. It sounded awfully
like the voice of a snake, or a Slytherin. \emph{Draco wants to get at
Connor. He wanted to be his friend, and now he probably wants to be his
enemy. What better way to do that than convince Connor his brother's
turned against him?}

They were in the Great Hall by then, and Harry could see Connor sitting
with Ron at the Gryffindor table. This time, his twin didn't meet his
eyes, just turned his head away and talked more loudly.

\emph{We'll have a conversation this afternoon,} Harry promised his twin
mentally, as he sat down and helped himself to a plate of eggs.
\emph{I'm not going to let my brother hold these ridiculous prejudices
against me. Everyone else in Slytherin might be a slimy snake, but I'm
not.}

``Professor Snape's staring at you again.''

Harry blinked at Draco's words, but didn't look up at the head table. He
could feel the professor's eyes, after all. ``Yeah, I know,'' he said,
and then paused to get a drink of pumpkin juice down his throat without
spraying it all over the table. ``He hated our father in school.'' He
thought about telling Draco about the life-debt and that Snape was
really good, but refrained. Maybe Draco wasn't a Death Eater, yet, but
Lucius Malfoy still might learn about that interesting tidbit a few
moments after Harry said it.

\emph{I hate that I have to keep secrets,} he whined to himself, just
before putting the whining in the secret box of his mind. \emph{If I was
in Gryffindor, it wouldn't be like this. We could trust most people
there to be for the Light.}

He shut the lid of the box firmly when he was done. He was in Slytherin,
and Snape hadn't yet come up and suggested that a son of the Potter
family really belonged in Gryffindor, so he supposed he'd have to make
the best of it.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

As it turned out, Friday came around before Harry saw his brother for
more than a few minutes at a time, or closer than on the other side of a
sea of uncomprehending faces. All the students were constantly on the
move, going to one class or another, and chattering so loudly that
Harry's gentle call to Connor in a corridor almost always went unheard.
Or perhaps ignored; Harry had to concede that Connor might be too angry
to pay attention to him even if he heard.

Draco didn't particularly help. He stuck to Harry's side like a burr,
and uttered a constant stream of bright chatter that Harry was sure was
false. When Harry tried to win free to go to the library---really in
hope of finding the way up to Gryffindor Tower---Draco invited himself
along. He said nothing about Connor, or about Gryffindors, but kept a
constant eye on Harry, and smirked whenever someone mentioned the
Boy-Who-Lived in passing.

\emph{I could deal with Slytherins better,} Harry thought as they moved
into Potions, \emph{if they didn't smirk all day long.}

It was true that he hadn't really met many Slytherins other than Draco
yet, but they all seemed to smirk, except for Vincent and Gregory, who
were mostly expressionless. Blaise Zabini stared and smirked, Pansy
Parkinson simpered and smirked, Millicent Bulstrode glared and smirked,
and the older years smirked at the mere thought of paying attention to
someone from a younger year. Harry was afraid that his smile would be a
smirk by the time that he got back to Connor, and was determined not to
let it be.

``You'll love this class,'' Draco whispered to the back of Harry's head
as they set up at the desks. ``Snape is a brilliant teacher. And we have
class with the Gryffindors, which I know you were looking forward to.''
He smiled blandly when Harry whipped his head around and scowled at him.

Harry had known about the schedule, of course. But he hadn't known that
Draco had noticed.

\emph{Maybe asking him about it directly would work.}

``Why do you care?'' he whispered fiercely. ``Of course I want to say
hello to my brother. We've never been apart until we came here. Why do
you smirk at me like that's unusual?''

Draco smirked at him, and didn't answer.

Harry turned around again, grinding his teeth in frustration, and saw
the Gryffindor first-years tumble in around the door. Hermione Granger
walked in by herself, consulting a book as she did so. Harry blinked
when she also took a seat by herself. \emph{Why hasn't she made friends?
She doesn't look as though shyness is going to stop her.}

Connor and Ron came next. Harry waited until his brother didn't have an
excuse not to look across the room, then caught his eye and smiled
hopefully. Connor sent him a tentative smile, but it broke apart when
Ron's elbow went into his ribs. Then they turned away and sat down at a
desk.

Draco snickered, Harry was sure of it, but he didn't get a chance to
confront him about it before Snape swept to the front of the classroom.

He stared out over the students. Harry stared back, and noticed that he
felt no pain in his scar this time when he met Snape's eyes. That was
worth paying attention to, maybe---though maybe not, since he still
didn't know why his scar had bled in the first place.

\emph{There are so} many \emph{things I don't know,} Harry thought,
tapping his quill against his parchment in agitation. \emph{How am I
ever going to protect Connor if I can't learn what I need to know to do
it?}

``You are here to learn the subtle science and exact art of
potionmaking,'' Snape was saying. Harry didn't pay that much attention
to his rattle, even when he got to an apparently practiced speech about
brewing glory. Of course Snape would try to impress students. He didn't
want them acting up in his class.

``\ldots{}if you aren't as big a bunch of dunderheads as I usually have
to teach,'' he finished, and Harry nodded. Yes, Snape worked to
intimidate. His tactics were the same as James said they had been when
he and the Marauders were in school. Harry would work to get along with
him, the same way he would with the rest of the Slytherins, but he
didn't intend to let Snape impress or goad him.

As though his nod had been a signal, Snape turned on him. Harry studied
his sneer, but couldn't make out whether it came from speaking to a
Potter, to the brother of the Boy-Who-Lived, or to the Potter and the
brother of the Boy-Who-Lived who had somehow wound up in Slytherin
House. \emph{No doubt he thinks it unfair.}

\emph{Well, on that we can agree, at least.}

``Potter,'' said Snape. ``What would I get if I added powdered root of
asphodel to an infusion of wormwood?''

``The Draught of Living Death, sir,'' said Harry. That much he knew,
having scrambled through his Potions textbook over most of the last
week, after he found out Snape would be his Head of House. He had
memorized by sheer force as much information as he could. If Snape asked
him for details, he'd be in trouble, but he thought he could manage
general answers.

Snape stepped back, head tilted. Harry couldn't read the expression on
his face, but his eyes never left Harry's, so Harry never glanced away
from him, either.

``Where would you look if I asked you to find me a bezoar?''

``In the stomach of a goat, sir.'' That was also luck, Harry reflected;
he'd seen the odd word while flipping through the book, and stopped to
read about it since he didn't recognize it.

``And what is the difference between monkshood and wolfsbane?'' Snape
asked the question with a much milder tone in his voice than before.
Harry dared not hope he'd impressed him, especially because he wasn't
sure of the answer to this one; he only knew about the plants at all
because he was friends with Remus.

``They're the same plant, sir.''

Snape nodded at him. ``Five points to Slytherin for displaying some
actual study skills,'' he said, and then whirled on Connor before Harry
could draw in a breath of relief. ``And you, Mister Potter, our
newest\ldots{}celebrity. Tell me, what are the ingredients for a boil
cure potion?''

Connor froze, eyes wide. Beside him, Hermione Granger's hand appeared to
have taken on a life of its own and was crawling up the air. Connor
nodded to her. ``Why don't you ask Hermione?'' he said. ``I think she
knows.''

Snape lost all traces of amusement, and took a long, heavy step forward.
Harry tensed, but Snape only said, his voice cold, ``I asked \emph{you},
Mr. Potter.''

``I don't know,'' said Connor, through gritted teeth. Harry sympathized.
He didn't know, either. Out of everyone in the class, probably only
Hermione did.

Snape sneered at him. ``Clearly, fame isn't everything,'' he said, and
turned to write on the board. ``Five points from Gryffindor for severely
\emph{lacking} study skills. The ingredients of a boil cure potion are
dried nettles, crushed snake fangs, stewed horned slugs, and porcupine
quills. You must add the porcupine quills \emph{after} you take the
cauldron off the fire, unless you want a nasty mess. When you put the
nettles in\ldots{}''

Harry sat back in his seat, stomach churning. Snape had deliberately set
him and Connor against each other, and he didn't like the feeling. He
glanced over to see Connor staring at him with a mixture of
embarrassment and resentment, at least until he ducked his head.

Draco poked him in the back. Harry whirled around. ``\emph{What}?'' he
snarled. He was fighting hard not to draw his wand.

Draco blinked at him and said, ``Want to partner up?''

Harry sighed, nodded, and went to fetch the ingredients.

Of course, as James had warned him, Snape turned out to be an
intimidating teacher, too, sweeping around the room, staring into
students' cauldrons, and making impatient comments---comments aimed only
at the Gryffindors. ``That's not the right consistency, Longbottom. Did
you imagine that you could put the snake fangs in \emph{without}
crushing them, Weasley? I am awed by the bottomless display of your
incompetence, Thomas, but not by the color of your potion.''

Harry soon found that he had to try to ignore Snape as much as possible.
When Snape commented on Connor's potion, there was an extra sneer in his
voice, and it infuriated Harry. He crushed the snake fangs and stirred
the potion with just enough violence that it didn't slop over the side,
and watched Connor.

That was how he noticed his brother was about to add the porcupine
quills before taking the cauldron off the fire. Harry winced. He could
imagine not only the mess that would result, but the punishment Connor
would receive from Snape, and he wasn't about to let that happen.

He whispered to Draco, ``Duck,'' and then tossed his own handful of
porcupine quills into his potion.

Snape was just swooping down on Connor when Harry's cauldron produced a
nasty plume of green smoke and a noise that rivaled a swarm of bees.
Snape stiffened, and then turned slowly to face the Slytherin side of
the classroom. Draco had ducked out of the way. That left Harry to
shuffle his feet and blink at Snape as if he didn't know what was going
on.

``And what exactly was \emph{that}, Potter?'' Snape hissed.

Harry blinked at the cauldron, at the floor where the cauldron was
melting and nearly burning a hole in his shoes, and at the gaping faces
of his peers. Then he shrugged. ``Oops?'' he offered.

Snape strode over to him, stared into the cauldron, sneered, and
announced, ``You put the porcupine quills in before you removed the
cauldron from the fire.'' Harry was gratified to see Connor hastily
snatch his hand back and gently lay the quills down beside the potion.
``Could you not clearly see the written instructions?''

``Oops,'' said Harry again. He kept his head up, and even let a faint
hint of a smile play about his lips. Snape wouldn't know the real
reason. He would only think Harry was being the mocking son of James
Potter.

``Detention, Mister Potter,'' said Snape softly. ``Eight'-o'-clock
tonight, in this classroom. I shall expect you no later than that.''

``Yes, sir,'' said Harry, ducking his head as Snape moved away. The
ruined cauldron vanished a moment later. Harry eyed the mess for a
moment. He could owl home and get his parents to send him another one.
He was sure that his mother would oblige, once she heard he'd ruined it
for a good cause.

A hand gripped his arm just then, forcing Harry to pay attention to the
gripper---Draco. ``Why did you do that?'' Draco whispered at him. ``You
whispered to me to duck. You \emph{knew} what was going to happen.''

Harry nodded.

Draco's grip only grew firmer, and he scowled as though this somehow
personally affected him. ``\emph{Why}?'' he repeated.

Harry shook his hand loose. ``I didn't lose any points for Slytherin, so
what do you care?'' he whispered, and sat back to listen to the rest of
the class suffer from Snape's sharp-edged tongue. Connor and Ron didn't
brew their potion perfectly, but then, no one in the class except
Hermione did. They also suffered from Snape's insults, but Harry was
fast becoming resigned to not being able to do anything about that. He
could at least save Connor from detention.

He didn't mind giving up his evenings for the rest of the year, come to
that. It was for the highest purpose imaginable.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

A knock sounded on Snape's door at precisely eight-o'-clock. He looked
up, checked the time, and raised his eyebrows. \emph{So the brat does
have some semblance of good manners.}

``Enter.''

Potter---not the famous one, Snape corrected in his mind, which sounded
awkward---entered and nodded to him. ``I've come about my detention,
sir. What do you want me to do?''

Snape studied him for a moment. The boy was unmistakably Potter's son,
given that hair and those glasses, but he didn't carry himself like
James. His head was up all the time, and he met Snape's eyes without
flinching. Curious, Snape used a gentle touch of Legilimency, and found
a memory of Harry arguing with Draco Malfoy just before he came here.
Draco wanted to know why Harry had done what he had done in Potions.
Harry had shrugged him off and run to his detention.

Snape ended his probe into the boy's head in time to see Harry's calm
mask split into a frown. He lifted a hand and rubbed his temple,
gingerly, as though his head hurt and he didn't know why.

\emph{Interesting. His mistake during Potions was deliberate, then?}
Snape kept the thought tucked behind his own mask, and snapped, ``Clean
up the mess that you and your fellow idiots caused today. You may not
use magic.''

``Yes, sir.''

Potter located a brush and a pail of water without being told, which
took him a few minutes, and then began to scrub down the classroom.
Snape marked essays and watched him from the corner of his eye. Potter
worked calmly, without complaint, his face reflecting far less emotion
than Snape would have thought possible for a son of James. His twin, the
famous one, was open enough, his hazel eyes spitting fire about the
unfairness of it all whenever Snape was within sight.

Snape grimaced in distaste. \emph{And I have to protect the brat. That
does not mean I have to like him.}

He went back to marking essays, at least until a faint, nagging buzz
broke his concentration. He looked up, an insult on the tip of his
tongue, but the loudest noise Potter made was the rasp of his brush over
the tables. The buzzing noise came from something else.

Snape touched his left forearm, and then shook his head. For all that he
did not believe the Potter brat had managed to banish Voldemort forever,
his lord was not yet able to command any former Death Eaters. Had he
been, the first sign of his presence would hardly be such a gentle
manifestation.

Then he thought of someone trying to spy on the detention, and cast a
\emph{Revealo} with his wand under the table. Nothing showed.

He worked through several other possibilities before one occurred to him
that hadn't in years---the memory jogged, perhaps, by the sight of the
Malfoy boy in Potter's mind. He reached out for the shield Lucius had
taught him, after teaching him to hear the faint ringing vibrations that
encircled powerful wizards, and let it down for the first time in years.

The buzzing noise sharpened immediately. Snape stared at Potter, who was
currently kneeling down and trying to reach a particularly stubborn
spill half under Longbottom's table. The air around him sang with power
like a finger running around a wineglass.

\emph{Why didn't I sense it when he was in class?} Snape wondered, and
then snorted to himself. \emph{He was among a dozen other brats, that's
why. Their power would have covered his.}

\emph{Strange, that the twin who did not defeat Voldemort has such an
aura about him. Perhaps the other one is even stronger, and will provide
our true `last best hope' after all.} Snape grimaced. He'd spoken to
Dumbledore several times about Connor Potter as the true focus of the
prophecy, and still felt ill at the thought of that \emph{child} being
the only one who stood between the wizarding world and Voldemort's
return. \emph{It's very romantic, of course, but not very practical.}

A glance at the clock showed that it was almost ten, and that Potter's
detention was finished. Snape shook his head and put the shield back up.
``Potter!'' he barked.

Harry started, but did not bang his head into the table, as Snape had
half-hoped he would. He stood and turned around, bucket and brush held
loosely in his hands. ``Yes, sir?'' he asked.

``Your detention is done, and the room is not passable,'' said Snape
coldly. ``You will return on Monday night, also at eight, and make sure
it is finished then.''

For a moment, a bare moment, the brat's eyes flickered. He was doubtless
thinking that the Monday potions classes would cause an even greater
mess, and more work. But he said only, ``Yes, sir,'' and moved to put
the cleaning supplies away.

Snape leaned forward. ``One more thing, Potter.''

Potter---no, he would think of this boy as Harry, since he didn't think
he would ever be able to muster the same amount of venom for him as he
could for the Boy-Who-Lived---looked up at him. ``Yes, sir?''

``If I find out that you have deliberately made a mistake in my class
again,'' Snape said softly, ``I will give you a week's worth of
detentions. I will \emph{not} have any of my Slytherins working at less
than their full potential, especially in an art I know they have basic
knowledge in. Is that clear?''

Harry's shoulders tensed for a moment, but he only tilted his head and
said, ``With all due respect, sir, I'm only a first-year, and I don't
know much about Potions. I'm sure I'll make lots of mistakes.''

Snape narrowed his eyes and stared at Harry. Harry stared straight back
at him. Snape hissed. \emph{Does he think that he can really best} me
\emph{in the arts of cunning?}

The set of Harry's face told him the answer. \emph{He doesn't know if he
can. But he knows he's going to try.}

``Then I suggest you study, Mister Potter,'' Snape told him flatly. ``As
the dividing line between a deliberate mistake and a true one may grow
hard to see when you've spent multiple nights scrubbing the Potions
classroom.''

``Yes, sir,'' said Harry, and walked to the door.

Snape watched him go, then leaned back in his seat and tried to play his
memories of class over. Harry had caused the mistake when---

When he'd just been about to descend on Potter for incompetence.

Snape snarled and stood up. \emph{If one Potter thinks to interfere for
another, he should think again. I will not tolerate celebrity treatment
of that brat in my classroom, even if his brother is the cause.}

\chapter{The Lion and the Serpent}\label{chapter-5-the-lion-and-the-serpent}

Harry hesitated for a long moment, and considered pulling open the
silver-and-green hangings of the bed next to his, just to be sure that
Draco was still asleep.

Then a long snore reassured him. Harry smiled as he tiptoed out of the
room, past Greg and Vince deep in sleep, and Blaise's empty bed. The
other Slytherin boy rose early every morning, and it seemed that
Saturday was no exception.

It was definitely an exception for Draco, though, which was the precise
reason Harry had chosen to sneak out now. Once he was in the common
room, he actually broke into a jog. No one was in there this early in
the morning, except a seventh-year who had fallen asleep in a chair with
a book on his lap. He opened an eye as Harry hurried past, then snorted
and shut it again, not deigning to talk to someone whose head barely
reached his chest.

Harry slipped out the door and shut it carefully behind him. Once it was
closed, it blended with the join of the stone wall and was hard to see.
Harry shook his head. The Slytherins were incredibly paranoid, to think
that none of the other Houses should be sure of exactly where they
lived.

Of course, he might say the same thing about the Gryffindors. Gryffindor
prefects were always watching to be sure that no one else---though
especially no Slytherins---followed the younger years back to the Tower.
Gryffindors traveled in clumps of their own year-mates much as did
everyone else in the school; Harry had been at Hogwarts only a week, and
already he knew that inter-House friendships were rare. And of course he
didn't know the Gryffindor password.

None of that was going to matter.

He drew his wand, cypress with a dragon heartstring core, and laid it
across his palm. ``\emph{Point Me} Connor Potter,'' he commanded, throwing
all his will forward. Their father insisted that this was not a hard
spell, but it had drained Harry the few times he attempted it in the
past. Of course, that was with a practice wind; perhaps it would work
better with the real thing.

It seemed to. The wand spun across his palm, then halted, pointing
forward. Harry smiled and began walking the dungeon corridor.

Up staircase after staircase he went, the wand sometimes vibrating but
always showing him at once where he needed to turn. Harry ducked Peeves,
who didn't seem to notice him; dodged past grumbling, half-awake
portraits; and waited patiently while a moving staircase tried to decide
where to dump him. Each time afterwards, he moved on, eyes fixed on the
wand as it shifted. At last the wand led him to a portrait of a snoozing
woman dressed in pink, vibrated once, and fell still.

Harry nodded and sat down outside the portrait. The woman snorted once
or twice and woke when he'd been there for ten minutes.

``Who are you, dear?'' she asked, peering at him. If she noticed the
Slytherin crest on his robes, she didn't seem inclined to comment, for
which Harry was grateful.

``My name's Harry Potter,'' he said quietly. ``I'm Connor's brother.
Would it be possible for me to go in and see him?''

``Certainly, dear, if you have the password.''

Harry shook his head. ``I'll wait out here for him, then,'' he said, and
leaned on the wall. Connor had never been an early riser even on
Saturdays when they \emph{didn't} have an exhausting week of classes
behind them. Harry doubted that would be different here. Connor would
have to come out to go to breakfast in the Great Hall sooner or later,
and then he and Harry would talk.

``Suit yourself,'' said the woman, with a shrug, and began humming to
herself while she examined her nails. Now and then she darted him a
glance. Harry focused on his breathing. He'd gotten quite good at being
still for hours when he was home, practicing for the time when he might
be following Connor on a dangerous mission into the heart of enemy
territory. After he'd been quiet for ten minutes, the portrait seemed to
forget all about him, and the people who came in and out of the
portrait---none of whom were Connor---never even looked at Harry.

And then, surprise of surprises, Connor came walking up the corridor
from the direction of the Great Hall, Ron at his side. Harry swallowed
an unexpected lump in his throat. \emph{Has he changed that much
already? How am I ever going to keep up with him?}

Ron was in the middle of a joke when Connor held a hand up to stop him.
Harry critically studied his posture, then nodded. It would do. Their
mother had been after Connor for years to sit up straighter and express
himself with the grace that a proper leader of the wizarding world
should have. Some of her lessons had apparently rubbed off.

Then his twin's eyes caught his, quiet and intense, and Harry could
think of nothing else.

``Harry,'' Connor said, his eyes shadowed and his voice just this side
of formal. ``What are you doing here?''

``I thought we could talk,'' said Harry, unfolding from the wall. He saw
Ron's face flush, but the other boy was standing behind Connor's right
shoulder, where Connor couldn't see him. ``Please, Connor. I know that I
haven't acted like your brother should this week, but there are things I
need to clear up.''

Connor chewed his lip for a moment, watching him. Harry stared back. He
was struck with how \emph{young} his brother looked, and used that to
reassure himself that nothing had changed. Connor was still an innocent
child, and his innocence was still Harry's to protect and cherish.

``Alright,'' Connor said suddenly. ``Come on in, then.'' He moved
towards the portrait of the woman in pink and said something, too low
for Harry to hear. She nodded, and the portrait swung outward, revealing
a round entrance beyond.

That seemed to wake Ron from his stupor. ``Connor!'' he objected. ``You
can't mean to invite him inside.''

Connor turned around and glared. Harry ducked his head to cover a smile,
sensing it wouldn't be diplomatic right now. ``And why not?''

``He's a Slytherin!''

``He's my brother,'' Connor corrected, and then gestured at Harry.
``Besides, you're never going to beat me into the common room,'' he
added brightly, and then disappeared through the hole while Ron was
still spluttering protests and Harry was still moving towards him.

The ball of tension in the middle of Harry's stomach dissolved. He
smiled at Ron, who scowled at him but followed him into the common room,
where Connor cast himself down in a chair before the fire and declared,
``I win!''

Harry looked around. The common room was furious with color, bright and
warm with golds and reds. Chairs and couches stood everywhere, wider
than the ones in the Slytherin common room, as if students should feel
free to sit close together here. Harry's heart warmed and sank
simultaneously. He was glad that Connor had a place like this, a place
that felt like home. At the same time, his week-old resentment towards
the Sorting Hat had woken up. He should be here, too, where he could
smile at Connor's jokes and watch his back and play Exploding Snap with
people like Ron Weasley. Harry still didn't know why the Hat had placed
him in Slytherin. He wondered if he would ever find out.

\emph{Well, I can at least do this,} he realized, when he turned back
around and realized that Connor and Ron were both waiting for him to
take a seat. \emph{I can make sure that I'm invited back.}

``Sit down, Harry,'' said Connor. ``And then tell us about Slytherin. Is
it true that they make you eat snakes for breakfast every day for a
month?'' He sounded revolted and fascinated at the same time.

Harry smiled and sat down in a chair that all but embraced him.
Resisting the urge to squirm until he was even more comfortable, he
said, ``No. But it's true that everyone smirks all the time. I haven't
figured out why, yet.''

Connor laughed. Harry bathed in the sound. \emph{I miss this. I wish I
was right by his side every moment. But making a fuss would just call
attention to myself. Time to mend the bridges.}

Ron gave him the perfect opportunity by bursting in with, ``But the Hat
put \emph{you} in Slytherin. It must be for a reason.''

Connor stopped laughing and stared at Harry. His eyes blazed with that
inner fire that Harry knew would make him a great leader someday, when
he was able to live out a normal childhood and then lay it down and step
into an extraordinary adulthood. ``Yes, Harry,'' he said. ``I want to
know why.''

``I've thought about it,'' Harry admitted quietly. ``I've only thought
of two reasons, though, and only one of them is good.''

``You can tell me about both of them,'' said Connor, and reached over
the chairs to grasp his hand. ``I promise. Whatever it is, whatever
reason you've imagined, I know that my brother can't be evil.''

Harry closed his eyes. ``Well, one is that I might be able to spy on the
children of families who used to be in the Death Eaters. I could listen
to them talk to their parents, find out what they think about Voldemort,
and give you information that you can use in the war.''

He opened his eyes to find Connor touching his scar, the way he did
whenever someone said Voldemort's name. Harry wondered if it hurt. He
wanted to ask Connor if it had bled since they came here, but Ron was
interrupting.

``And what's the other reason?''

Harry licked his lips. This was the part he didn't want to speak aloud.
But Connor was there, waiting, his eyes open and luminous. Harry
reminded himself of the words Connor had just spoken. \emph{I know that
my brother can't be evil.}

``Maybe I really \emph{am} a Slytherin,'' he whispered. ``Maybe somehow
everyone missed it---Mum, Dad, Sirius, everyone---''

He couldn't talk after that, because Connor had swept him up in a
reassuring hug. Harry laid his head on his brother's shoulder and hung
on. He was supposed to be the one who reassured and comforted most of
the time, but sometimes, it was all right if Connor was. Harry knew his
place, and if his brother needed someone to be strong for, as well as
someone to protect him so well that he didn't even notice it happening,
then Harry could do that, too.

``You're not a Slytherin,'' Connor whispered to him. ``I think there's a
third possibility: the Hat made a mistake, that's all. It's old. Maybe
it starts forgetting things the way that Frederick the Frumpy did.''

Harry smiled, remembering the portrait of the old wizard who had hung on
the wall of their parents' bedroom. First he'd forgotten the names of
everyone in the house, calling Harry by his grandfather's name and
Sirius by his mother's. Then he'd started wandering around from portrait
to portrait dressed only in his bathrobe. Then he became convinced he
was still in the war against Grindelwald, and their parents had to give
the portrait up. The mental image of the Sorting Hat losing its place in
the song cheered Harry up immensely.

\emph{I can't be evil. Connor says I can't be, so I'm not.}

``I'm never going to give you up like our parents did Frederick,'' said
Connor, stepping away from him and staring firmly into Harry's eyes. ``I
know that Headmaster Dumbledore probably wouldn't consent to letting you
be in Gryffindor, but we can still be friends, and play together, and of
course we'll spend Christmas together.'' He nodded firmly, then smiled.
It was a cheeky smile, the kind that Harry remembered Connor giving just
before he attempted to play some practical joke on Sirius that would
always backfire. ``And if someone tries to convince you that you're in
Slytherin, then you can just tell them that you're only there because of
a mistake. Let them wonder about it .''

Harry let out a small relieved sigh, feeling better than he had ever
imagined he could when he first came to the portrait hole. ``Thank you,
Connor,'' he said. ``I knew that you'd comfort me, but it's so much
better hearing you say it.''

``I suppose I can accept that,'' said Ron, though he didn't look
completely convinced. ``You really wish you were in Gryffindor, Harry?''

Harry decided to take it as a sign of progress that he'd earned
``Harry'' and not ``Slytherin.'' He turned to face Ron and nodded.
``With all my heart,'' he said. ``It's the House our parents were in,
and our godfathers, and now my brother.'' He glanced at Connor and
received a punch on the shoulder in return, as though Connor objected to
coming at the end of the list, though he was grinning. Harry returned
his gaze to Ron. ``It's the place I belong,'' he finished. ``I'm not
going to let Slytherin House transform me into something I'm not. I
promise.''

``Why're you friends with bloody \emph{Malfoy}, then?'' Ron demanded. ``If
what you say is true, then you should want to ignore the lot of them,
and that prat the most!''

Harry sighed softly. ``He's decided that he wants to be my friend,'' he
admitted. ``And it's easier to respond to him than ignore him all the
time. Besides, his father was a Death Eater. I still might be able to
spy on Draco and get information about Lucius Malfoy through him.''

Ron just shook his head, but appeared slightly more at ease in Harry's
company than before. ``Well, just don't invite him along the next time
you come back,'' he muttered, and ran up the stairs.

\emph{The next time you come back.} Harry concealed the small flame of
joy that lit inside him until he turned towards Connor, and saw it
confirmed in his eyes and grin. Then he let himself smile.

``I'll make sure that you get all the same chances I do,'' Connor
promised, as they went to the portal. ``Ron'll get over his distrust
eventually, and then we can go around together. His brothers are the
best practical jokers I've \emph{ever} seen. They've promised to show me
all the secret passages. I'll come and get you when we explore them.''

Harry nodded. He had to go back to the dungeon again, and he wouldn't
ask his brother for the Gryffindor password---there was too much chance
he might accidentally reveal it to someone from Slytherin---but he felt
more at ease than he had been since term started. ``Bye, Connor.''

Connor smiled at him as he left through the portrait hole. ``Bye,
Harry.''

Harry could still see the smile when he reached the Great Hall.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Draco narrowed his eyes as he watched Harry come into the Great Hall and
make a beeline for the Slytherin table. He was already feeling out of
sorts, since he'd awakened to find Harry gone and Vince and Greg utterly
no help as to \emph{where} he'd gone. Then he met a sixth-year who said
he'd seen Harry walking upstairs.

Upstairs probably meant Gryffindor Tower, Draco thought. And Harry's
Gryffindor prat of a brother.

Draco knew it meant it when Harry sat down next to him and actually gave
him a smile that Draco didn't have to drag out of him. Unfortunately,
that just made the foul mood he was in worse.

``Where have you \emph{been}?'' he whispered, as Harry heaped his plate.
``I wanted to go to the library.''

Harry paused to blatantly stare at him. ``Before breakfast?''

\emph{Well,} Draco conceded to himself, \emph{that was a bit stupid.}
``To breakfast, then,'' he said. ``Tell me where you were.''

``Visiting Connor,'' said Harry, the prat, who had the audacity to look
as if everything were right with the world, with small bluebirds singing
in the corners of the room. He took a large bite of his breakfast, not
seeming to care that he'd put Draco off his appetite entirely. Draco had
finished eating already, of course, but that wasn't the \emph{point.}

``Why do you want to visit him?'' Draco asked, unable to keep a whine
from creeping out in his voice. ``You're in Slytherin, and he's in
Gryffindor.''

Harry paused for a long moment, then turned sideways on the bench to
face Draco. His face had gone entirely serious, and when Draco peeked
out around his shield, he could feel Harry's power, focused down to a
shimmering arrowhead pointing at him. He winced and repaired his shield.

``Draco,'' Harry said softly, ``I'm not ungrateful for everything you've
done for me. You've tried to make me feel welcome in Slytherin,
and---and, well, with some of the politics behind the Boy-Who-Lived,
that can't be easy.''

Draco stayed quiet. He wasn't about to turn free praise down. Besides,
Harry couldn't feel his own power, and didn't know that he was, or was
supposed to be, Draco's release from boredom.

``But there's one thing you've got to understand,'' Harry went on,
leaning closer. His messy black hair fell over his forehead, entirely
covering his scar and shading his green eyes. ``No matter what happens to
us in school, no matter what House I'm in or Connor's in, no matter what
classes we take, my first loyalty is \emph{always} going to be to my
brother. I've made up with him. I've even made up with Ron Weasley---''

``I didn't know the Weasleys mattered to you,'' Draco snapped, furious
and hurt.

``Anyone who's my brother's friend matters to me,'' said Harry calmly.
``And I still think I should have been in Gryffindor. So. I appreciate
everything you've tried to do for me, but I don't want to leave you
under any false impressions. I can't be your friend, not wholly and
completely. My first responsibility is always being Connor's brother.''
He paused, then shrugged, something in his eyes that was not quite
regret. ``I'm sorry if that hurts you.''

He turned away and started eating again, leaving Draco to stare at the
side of his head. But Draco's own emotions weren't anger or hurt or
frustration so much as shock.

\emph{He thinks he should have been in} Gryffindor? \emph{Not feeling
his own power is one thing, but---Great Merlin! Is he} blind

He must be, Draco thought, and his eyes narrowed into slits as he
changed his plans slightly. Harry wasn't going to be just a prize to be
won, or a release from boredom. He was a Slytherin who was going to be
made to acknowledge that he was a Slytherin.

\emph{If I can win that victory,} Draco thought, \emph{it won't matter
what the Gryffindor Hero does or says. I'll still have gotten him back.
And then Harry will be more fun than ever, once he knows the truth about
himself.}

Pleased with his own reasoning, Draco waited patiently for Harry to
finish breakfast.

\chapter{Suspicious Eyes}\label{chapter-6-suspicious-eyes}

``Flying lessons!'' Connor declared as they walked outside. The sun
blazed above them as if in approval of his grin, Harry thought, and he
spun around with arms out as if embracing the wind. ``Aren't you
excited?''

``Very,'' said Harry quietly, and heard Hermione Granger, walking not
far away from him, snort. He turned and smiled at her. Hermione appeared
startled for a moment, then buried her head in the book that she carried
and refused to raise it again. Harry sighed. He had attempted to
encourage Connor's friendship with her, but it had faltered on both
parts; Hermione was too interested in studying, and Connor was too much
interested in everything else.

``Harry, there you are.''

Draco jogged up behind him, earning a swift offended look from Ron and a
suspicious glance from Connor. He ignored them both effortlessly, and
smiled at Harry. ``Excited to have flying lessons with the
Gryffindors?''

``\emph{Someone} is probably missing the broom his daddy bought him,''
said Ron, just loud enough to be heard.

``At least I \emph{have} a broom, and not a twig,'' Draco retorted.

Connor shook his head, and stepped away from both of them. ``Ignore him,
Ron,'' he instructed his flushing friend. ``We have\ldots{}'' He paused
for a long moment, then yelled ``Flying lessons!'' and whooped his way
down the field towards the line of waiting brooms. Ron hesitated, gave
Draco a glare that said they'd resume the argument later, and took off
after him.

``Do you \emph{have} to do that?'' Harry asked, dropping back with Draco
towards where the other Slytherins walked.

``Yes.'' Draco appeared almost angelic now, but Harry wasn't fooled; he
knew it was only because the other boy had gotten his way. He slung an
arm over Harry's shoulders, and that was an act, too, a play for some
invisible crowd. ``I know he's your brother, but he chooses to hang out
with a blood traitor. He can't help some of it rubbing off on him, I
suppose.''

Harry wondered wearily what bothered him more: the cheerful
condescension in Draco's voice, or the fact that trying to point it out
would involve meeting his blank stare. In the end, he kept silent. He
had discovered in the last five days that trying to negotiate between
Gryffindors and Slytherins involved an awful lot of just knowing when to
keep his mouth shut.

They arrived at the line of brooms at last, and moved to take their
places. Harry wound up opposite Connor, who grinned at him. They'd both
flown at home often enough to do it in their sleep. This wasn't going to
be an effort.

\emph{Maybe not for us,} Harry thought, hearing an audible gulp from the
side. He glanced that way and found Neville Longbottom looking at his
broom with a mixture of horror and sick fear. Harry cocked his head. He
should be alert in case the other boy needed help.

\emph{Technically, Connor should be alert. But I can watch for him.}

``Take your places!'' Madam Hooch instructed as she walked up between
the brooms, ignoring the fact that most of them had already done so. She
was a stockier witch than Harry had expected, with hair that looked
permanently frazzled, as if it had blown in too many winds to ever calm
down. She pivoted in a slow circle as she looked at them, gaze narrowed
and slicing over their faces. Harry lifted his chin under her scrutiny,
and noticed with amusement that Draco did the same thing, as if they had
something to prove. Draco spoiled the effect by catching his eye and
grinning, of course.

``Welcome to your first flying lesson,'' the witch continued. ``As we
will be controlling the brooms by means of our own magic and not our
wands, I must ask you to lay them aside.'' Harry saw a general rustle as
a few students tucked their wands away; Hermione reluctantly put the
book she'd been reading back into a huge bag near her feet, then kicked
the bag behind her. ``As for the procedure of controlling the brooms,
it's very simple,'' Madam Hooch said, and then stalked over to a larger
broom laid near the end of the line. ``You hold your hand over it and
say---''

\emph{Up}, Harry mouthed, and Connor mouthed it back to him across the
line.

``Up!''

A ragged chorus of voices gave the command, and for a moment Harry saw
the air blaze and shimmer with light as various wills reached out for
the brooms. Some people were more successful than others. His broom
leaped up, and Connor's, and Draco's, and Ron's, and Hermione's. Others
made it halfway up and then fell. Neville's smacked into his hand with
such force that the plump Gryffindor sat down on the grass. Harry winced
for him.

``Good and not so good,'' said Madam Hooch, who was, of course, holding
her broom. ``You must \emph{believe} in it when you summon the broom, or
else it won't work. Take you, Mister Longbottom.'' She swooped down on
Neville, who looked terrified to be singled out, but let her help him
sling a leg over the broom. ``You have the strength, but no finesse.
When you ride the broom---no, not like that---''

But Neville's broom was already rising, and carrying him along. He clung
to it and shrieked. Other students began to cat-call or laugh or cry out
in worry as was their wont. Harry narrowed his eyes. He could see
Neville's hands beginning to slip off the broom, and knew he wouldn't
hold on for very long.

His eyes shot to Connor. His brother was gaping like the rest of them,
but he had one leg half-lifted, poised to descend on the other side of
the broom.

Harry seized his wand and cast an unobtrusive Sticking Charm in
Neville's general direction. It wouldn't hold long either, at this
distance and with the broom bucking like it was, but it would be long
enough for Connor to do something.

His brother remembered himself a moment later. He rose like the expert
flyer he was, shot across to Neville, and caught his arm just as the
Sticking Charm failed. For a moment, Neville's weight dragged him
towards the ground, and Harry caught his breath in alarm, wondering if
Connor would manage to juggle him. He did, though, and landed on the
grass to the cheers of the Gryffindors. Something small and round
dropped from Neville's robe and rolled into the grass, too, but Harry
doubted that anyone noticed or cared. Connor's face was flushed with
triumph, and Neville was looking at him as if he were the sun.

``Now,'' said Madam Hooch, showing up beside the two boys so quickly
that Harry blinked in surprise. ``That was \emph{some} flying, Mr.
Potter.'' Connor's flush altered to one of pride, and Harry smiled. He
deserved it. Hooch turned to examine Neville, bending down until her
nose was an inch away from his face. ``What about you, Mr. Longbottom?
Set to fly?''

``I---I think---'' Neville began, and then fainted dead away.

Madam Hooch snorted, placed her broom gently on the ground, and picked
Neville up, nodding to Connor to carry his feet. ``We'll take him to
Madam Pomfrey,'' she said, as they began to walk. ``Don't worry about
missing the lessons, Mr. Potter, we'll be back in two shakes of an owl's
tail, and you've shown that you've got the basics mastered already.''
She turned around and gave the rest of the students a severe stare from
hawk-yellow eyes. ``All of the rest of you, \emph{remain on the ground.}
If I find out that anyone has been flying, I can and \emph{shall} issue
detentions.''

Harry was happy to remain on the ground. He watched Neville and Connor
pass out of sight, and sighed. That had gone well. Neville had been
spared serious injury, and Connor had looked like a hero. Things were
the way they should be.

``Look what I've got!''

Harry hissed as he turned around. Draco's voice, speaking in that tone,
meant things were \emph{not} as they should be, or would not be very
shortly.

Draco had found the small round thing that Neville had dropped in the
grass, and now tossed it in the air, grinning. It landed in his hand
with a soft \emph{smack}. That and the red color told Harry it was a
Remembrall. He wasn't surprised that Neville had one; the poor boy
forgot every ingredient in a potion almost as soon as Snape wrote it on
the board. Draco had evidently forgotten something, too.

\emph{Such as not being a git,} Harry thought, stepping forward. ``Give
it here, Draco,'' he ordered, holding out a hand.

Draco grinned at him. Harry blinked. There was no malice in that
expression, only a clear and childish delight that puzzled him. If Draco
had taken the Remembrall to humiliate Neville, he should have been
cracking a joke, or sneering, or in general lamenting the intelligence
of Gryffindors as compared to Slytherins. The way he backed away from
Harry, holding the Remembrall not quite out of jumping height, argued it
was something else.

``Why should I?'' Draco asked. ``It's not yours. I'll just hang onto it
until Longbottom remembers to ask for it. Which would be never.'' He
snickered, and this time Harry heard the sneer in it.

``Give it \emph{back},'' said Harry, wishing that he knew how to sound
more commanding. It was one of the arts their mother had tried to teach
Connor, but Harry had learned more about hiding and silence.

``No, I don't think so,'' said Draco, and then abruptly hopped a step
backwards, grabbed Neville's broom, mounted it, and took off in a
dizzying spiral like a lark's. ``If you want to come and get it,'' he
called over his shoulder, ``please feel free to do so.''

Harry ground his teeth for a moment, then darted a glance around. The
other Slytherins were watching him, expressions mildly curious. It was
the Gryffindors who concerned him, though. Their eyes were narrowed, and
they had been about to jump Malfoy themselves, but now they stared at
him.

\emph{Show us you're different from the rest of the slimy snakes,} their
gazes challenged him. \emph{Show us that you really would defend Neville
like one of your own.}

Harry grimaced, cast a quick glance at the school, and raced back to his
own broom. When he looked up, Draco was hovering overhead, waiting for
him. He swallowed and kicked off from the ground.

The same transformation happened that always happened, the moment his
feet left the grass. He was thrilled, exalted, at peace, like a bird
balanced on the wind. He couldn't help smiling as he circled towards
Draco, even given what had happened to inspire this, even though he was
breaking the rules. He loved flying too much.

Draco was grinning at him again, and though his eyes were narrowed,
Harry saw a variant of the same challenge that the Gryffindors had
showed.

``Show me what you can do, Harry,'' he breathed, and then turned and
cast the Remembrall in a high, descending arc.

Harry snapped his head forward, eyes locked on the glitter, and then
flew after it. Connor wasn't here, and so no one could compare his
performance to his brother's. He was free to unleash all the speed he
normally kept constrained. The wind shrieked past his ears, and his hand
curved out at the proper moment, and he turned, and the Remembrall fell
with a triumphant sound into his palm. Harry folded his fingers around
it, holding it safe. After the difficulty of grasping and holding a
fluttering Snitch, this was no problem at all.

He wheeled around to see Draco hastily flying back towards the ground.
Harry dropped like a falcon. Madam Hooch was coming back, or she'd sent
some other Professor out to supervise the class. Harry cursed quietly as
he landed and hopped back from the broom like it was on fire.

Draco strode up to him just before Hooch and Connor returned, grinning
like the idiot he was. ``That was impressive,'' he whispered.

Harry eyed him. Draco seemed perfectly cheerful, as though everything
had gone according to plan, but Harry didn't know why. With a shrug, he
turned away from the Slytherin and extended the Remembrall as Madam
Hooch entered the pitch again.

``Neville dropped this, ma'am,'' he murmured.

Madam Hooch nodded and pocketed it, and the lesson, complete with happy
Connor and ridiculously happy Draco, went on.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Draco grabbed Harry's arm when he tried to leave the field with the
Gryffindors. Harry turned and scowled at him. Draco knew that he hadn't
earned his goodwill earlier, even if flying about with Neville's
Remembrall had no direct reflection on the Gryffindor prat twin.

\emph{He'll see differently,} Draco promised, and then smiled at Harry.
``Come on, we have to see Professor Snape.''

Harry blinked. ``What? Why?''

``Because we do,'' said Draco, and dragged him off. Harry went with him,
steps slow but not actually resisting. He probably would have been
struggling like a trapped unicorn if he knew what Draco actually
intended.

That didn't matter. This was one of those times where Harry would just
have to listen to good sense. And once Draco described what he'd seen,
he knew what their Head of House would say.

They hurried down a dungeon corridor and towards Professor Snape's
office, where Draco knocked importantly on the door. Harry fidgeted
nervously, continually glancing in the direction Connor had gone. Draco
snorted, caught his eyes, and forced him to stop it.

``You're not in trouble,'' he said. ``Quite the opposite.''

Harry opened his mouth to ask why, but didn't get to, as Snape's voice
said, ``Enter,'' just then, and Draco took the chance to open the door
and push Harry inside, ahead of him.

Snape looked up from his essays, eyes narrowing. Draco widened his eyes
innocently. Snape wouldn't fall for it, but at least it reassured him
that Draco was here in a spirit of mischief---and improving Slytherin's
Quidditch team, he told himself virtuously---and not because he was in
trouble.

``Potter, Malfoy,'' Snape said, rising to his feet. ``Why have you
disturbed me?''

Harry just stared. Draco took the chance to talk. If Harry would not
speak up to defend or spare himself, he thought, he deserved what he
got. ``We just came from flying lessons, Professor. Madam Hooch left us
alone briefly, and I took the opportunity to test Harry.'' He smiled at
Harry, who still looked bewildered, and not unhappy yet. ``I suspected he
might be, and he \emph{is.} Bloody amazing on a broom. He caught a
Remembrall from fifty feet up and ten feet behind. We've got ourselves a
Seeker.''

Ah, \emph{there} was the unhappy expression. Draco peeked around his
shield. Harry's power was growing claws. He retracted his awareness
hastily and glanced at Snape, whose face showed he'd picked up on it,
too.

\emph{And doesn't he wonder why the less powerful Potter twin shows this
much power?} Draco thought. \emph{I know I do.}

``Sir, I'm sorry,'' said Harry, tensing his shoulders as though he were
facing a strong wind. ``I didn't know that Draco brought me here for
this. I know I wasn't supposed to be flying on a broom while Madam Hooch
was gone, and I'll gladly accept my detention.'' He recited the last
words in a monotone, his eyes cast down. Draco snorted. He knew well
enough that that humility was a mask, having seen Harry's eyes flash
whenever he thought something might have upset his brother. Who did
Harry think he was fooling?

Not Snape, as became clear from the professor's voice a moment later.
``As you doubtless know, Potter, first-years are not allowed to possess
their own brooms, much less allowed on the House Quidditch teams.''

Harry looked up, a faint smile of relief curling the corners of his
mouth. ``Yes, sir. I realize that. Again, I'm sorry for interrupting
you.''

``However,'' Snape continued, and Draco watched with interest as Harry's
smile froze, ``Slytherin has been in solid possession of the House Cup
for some time now. I do not wish that to alter, particularly as
our---new celebrity---has been Sorted into another House, and may expect
to receive \emph{special treatment.}'' The sarcasm on the last words was
as thick as treacle. ``If you are truly as good as Draco says, then I
would be a fool not to put you on the team. Rules can be bent for a good
cause.''

Harry didn't miss the cue. ``He's probably mistaken, sir. I did dive
after a Remembrall, but not from as far away or as high up as Draco
says.''

``That's right,'' said Draco.

He received a death glare from Snape, but it lasted only until he added,
``It was from sixty feet up and fifteen feet behind. I forgot.''

Snape lifted his eyebrows and altered the frigidity of the stare by only
a touch. Draco endured it. He knew that Snape could read minds, and
deliberately let his memory of Harry diving after the tiny ball play
across the surface of his thoughts. Snape snapped the gaze a moment
later, and nodded.

``You will play Seeker on Slytherin's team this year, Potter,'' he said,
and turned away with a dismissive sweep of his robes. ``I will speak to
Headmaster Dumbledore about it. You need only show up to practice and at
games, and then you need only catch the Snitch.''

``No, sir.''

Draco stared at Harry. He had his arms folded over his chest now, and he
had dropped the mask of humility entirely. His eyes flashed green fire.
He didn't quail even when Snape turned around, slowly, and asked, ``What
did you say?''

``No, sir,'' Harry repeated, his voice flat, but not at all dull. ``I
will \emph{not} play Seeker on the Slytherin House team. I'm only a
first-year, and I haven't had much time to make friends yet---other than
Draco.'' His stare said what he thought of that friendship at the moment.
``I'd cause resentment and dissension, not only in Slytherin but in the
other Houses as well, sir. I feel it's best if I don't play.''

Draco knew that wasn't true, of course, though it was quite possibly the
best lie Harry could come up with on the spot. He knew the real reason.
\emph{He won't play because his twin isn't on Gryffindor's team. Prat!}
He was not sure if he meant Harry or Connor with that last thought.

``You can play, Mr. Potter, and you will,'' Snape told him, in a voice
even softer than before. Draco shivered. Snape didn't raise his voice
when he was truly angry, and he was truly angry now. ``I will speak to
Headmaster Dumbledore about it. You need not concern yourself.''

``I believe that there's no rule saying that someone can be \emph{forced}
to play Quidditch if he doesn't want to,'' said Harry, head up. His
lightning bolt scar showed clearly through his fringe. Even with Snape's
anger, Draco saw the professor's eyes dart to the scar, and his faint,
questioning frown. ``I've chosen, and I won't be moved from this. Sir.''

``You will,'' said Snape. ``Or I can make life unpleasant for you, do
not doubt.''

``I don't doubt it, sir,'' Harry said. Snape winced, and Draco wondered
how far his shield against power-headaches was down. ``But I am prepared
to endure that. I'm prepared to die against Voldemort, if it comes to
that. Somehow, I don't think you'll be quite that bad.'' His hand
actually drifted sideways to rest on his robe, as if he would draw his
wand at any moment.

Snape stared into Harry's eyes for what was probably only a minute, but
felt much longer to Draco, given the freezing silence. Draco shifted. He
wished he knew what Snape saw there.

``You are right,'' Snape said abruptly. ``I ask your forgiveness, Mr.
Potter.'' His voice had risen slightly, but was still soft and mocking.
``I forgot that some of my Slytherins prefer to contribute to the
welfare of their House, and others do not.''

As Draco had suspected, that insult slid off Harry like water. \emph{He
probably doesn't even think it's an insult, since he wants so much to be
a Gryffindor,} Draco thought spitefully. ``Thank you, sir. May I go now?
I have a long Potions essay to finish.''

``You may,'' said Snape, as if he had lost interest, and Draco watched
Harry stride out the door, as though he thought he had won this battle.

Snape turned around when the door shut, and it was obvious from his
expression that he hadn't given up the battle at all, only retreated to
firmer ground. Draco smiled at him.

``I was right, wasn't I, to bring him here?'' He didn't mean the
question to sound quite so anxious, but Snape only nodded.

``You were. The boy doesn't think he's a Slytherin.'' There was
disbelief in his voice, but anger as well. ``And he's as arrogant as
ever James Potter was about it.'' Now hatred, and Draco shivered as the
tone chilled again. ``Well. No matter. We shall show him in the end.''
His smile came back, the kind of smile that Draco had seen when he
walked in on Snape and his father trading stories of Voldemort's first
rise. ``And James Potter, as well. I shall enjoy using his son to win
and keep the House Cup.''

He nodded at Draco. ``You may also go.''

Draco left, comforted. \emph{Well, that didn't work. But it's not as
though Harry can hide forever. Talent is going to show itself, and if he
isn't playing on the House team before the year's out, I'll eat five
Galleons. No, ten. In front of Weasley.}

\chapter{Humility}\label{chapter-7-humility}

``\emph{Fumo!}''

``Harry!''

Harry smiled slightly as smoke filled the first-year boys' bedroom, to
cries of protest and disgust from Greg and Vince, who had been studying,
and Blaise, half-asleep on his bed. Blaise actually fell off the bed,
choking and coughing. Harry might have choked himself, but he'd already
cast the \emph{Specularis} charm in front of him. A small, clear window
of air hovered there, diverting the smoke to either side and letting him
breathe. It also moved with him, so that he could see a short distance
ahead.

He pronounced it again, this time more firmly and with a wider wand
movement, and the smoke dissipated. Vince and Greg stared at him. Blaise
glared up from the floor.

``Why did you do \emph{that},'' he asked, treating the word like a dead
frog the Kneazle had dragged in, ``in the middle of our bedroom?''

``Because Draco didn't think I could do it,'' said Harry with a shrug,
falling back on his bed and hugging the knowledge that he hadn't
forgotten the Smoke Charm to himself. He had the feeling that he might
need it, just as he'd need \emph{Protego} and all the rest of the shield
and hiding spells his mother had insisted he learn. ``Talk to him.''

``I didn't mean that you had to demonstrate it right \emph{now},'' Draco
whined from the bed next to his.

Harry closed his eyes and let the argument play around him. Such
chatter, without a mention of his name or Connor's except in play, was
the next best thing to silence---which he wasn't going to get with Draco
around---for thinking about the dreams that had been plaguing him
lately.

The dreams had been vague at first, formations of darkness that did not
impress Harry, who'd grown up immersed in stories of Voldemort's first
rise and the truly horrible things the Death Eaters did under his
guidance. But gradually they sharpened, and he found himself in a maze
of twisting corridors, advancing towards a door that opened on sharp,
snarling teeth.

Then another figure had started appearing between him and the door. The
figure was small and stooped, inconsequential. Harry supposed that was
to stop anyone from looking too closely. But since he was someone who
relied on the same defenses, he'd looked, and recognized the purple
turban that wrapped the figure's head. And then he woke with his scar
bleeding, which was, he thought, the last proof he needed. Professor
Quirrell meant harm of some kind to Connor.

On the face of it, that was ridiculous. The professor stammered all the
time and taught Defense Against the Dark Arts with shuffling
incompetence. Harry did not care, though. He planned to follow Professor
Quirrell tonight and see what he could discover about him.

\emph{``Harry!''}

Harry blinked and sat up. Draco and Blaise were looking expectantly at
him, Blaise holding his wand out in front of him. Above it floated a
clear glass bubble that Harry recognized as a beginner's try at the
\emph{Specularis} spell.

``Not like that,'' he said, and settled down to show them the proper
wrist movements. He supposed he might be asking for trouble, teaching
magic to possible future Death Eaters, but refusing would only earn him
a reputation as a smug git, and Harry wanted to avoid any kind of
reputation at all. Besides, Harry rather thought some of them might be
turned. Not all Slytherins were evil. Even Draco wasn't that bad most of
the time.

``Come on, Blaise, a Gryffindor could do better than that,'' Draco
taunted, and Harry sighed and revised his estimate of how much time this
would take.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Harry waited quietly outside the Great Hall that night until Professor
Quirrell emerged, and then fell in behind him. He wished he had their
father's Invisibility Cloak, but he was quite sure that Lily hadn't
allowed James to send it. He would have to rely on his trained silence
and hiding abilities, and on the spells that he had learned if
necessary, just in case Quirrell glanced around and saw him.

The professor continued hurrying ahead, though, as involved in his own
thoughts as the other Slytherins had been in the argument about
Quidditch that Harry had stirred up at dinner. He certainly never
glanced behind him to see if anyone was there, and Harry was able to
follow him easily through corridors and doors, up staircases, and around
corners.

\emph{Then why do I still feel watched?} Harry thought, as they rounded
a corner and came to a shut door.

He didn't know, just as he didn't know for certain what the source of
the pain in his scar was, but he knew enough to duck out of sight when
Professor Quirrell looked around at last. Then the professor carefully
withdrew a large silver key from a chain around his neck and fitted it
into the door. A low \emph{snick}, and he was past and in.

Harry waited in silence for one moment, then two, then ten. Then he
crept towards the door, hoping it would be unlocked.

It was, but Harry could see little when he knelt and put his eye to the
crack, and he didn't dare move the door. He did hear growling, though,
and Quirrell talking in a low murmur, too quiet to make out what he was
saying. Harry cocked his head. Was the professor not stuttering, or was
that his imagination?

``Why are you here?''

Harry tensed all his muscles to keep from flinching or crying out, and
then turned and glared at Draco, who had come up behind him. At least
he'd had the sense to keep his voice to a whisper. ``Working to protect
Connor,'' Harry whispered back. ``Why are \emph{you} here?''

``I followed you from dinner,'' said Draco, with a shrug. ``I know you
made up that argument on purpose so no one would notice you leave.'' He
crouched down beside Harry and grinned at him. ``That was very Slytherin
of you, really, Harry. A Gryffindor would just have dumped his plate
over someone's head.''

Harry resisted the urge to get into an argument about his proper House.
``Be \emph{quiet},'' he whispered instead. ``Professor Quirrell's in that
room, and I don't want him to know we're out here.''

``Why not?'' Draco asked, too loudly. ``He's a professor, isn't he?
Why---''

Harry grabbed his arm and held it tight as the growls beyond the
half-open door resolved into a chorus of barking. A moment later, there
came a stabbing pain in his scar, which Harry took to mean that
Professor Quirrell was running back towards them.

Harry didn't hesitate, but reached inside his robes for his wand.
``\emph{Fumo}!''

Smoke gusted from the tip and filled the corridor with a mist of gray.
Harry grimaced; he'd forgotten to cast \emph{Specularis}, and he could
hear Draco choking, trying desperately not to give them away. And now he
didn't know which way Quirrell would run. He was annoyed at himself.

He chose a direction that he vaguely remembered as being down the hall,
away from the door, and tugged Draco in it. Draco came with him, his
coughs escaping in small, muffled noises. Harry crouched over him and
drew his wand fully. He could fight Professor Quirrell, if it came to
that. He would have to, if the professor figured out who'd cast the
Smoke Charm.

But the professor had gone. By the time the smoke cleared, Harry
couldn't see anyone. He sighed, and scowled when he noticed the door was
locked. There had gone his chance to see what was behind it.

His nostrils and lungs were stinging, but he wasn't badly off. Draco,
however, would have to go to Madam Pomfrey. Harry coaxed him onto his
feet, then coaxed him into walking, and shook his head as they staggered
to the first staircase.

``Why did you follow me, anyway?'' he muttered at him. ``You didn't have
to.''

``I wanted to,'' Draco whispered, and then burst into another round of
coughing.

Harry sighed and kept them moving. \emph{How very Malfoyish that answer
is.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Harry didn't get another chance to follow Professor Quirrell. Draco had
taken to clinging to his side again. He always had some excuse. He had
missed writing down the Potions homework that day. He wanted Harry to
teach him the Smoke Charm. Did Harry realize that it'd been \emph{ages}
since they played Exploding Snap together? He badgered and coaxed and
snorted and taunted, and Harry wound up spending more time than ever in
the Slytherin common room and the library as the weeks passed.

And, of course, he spent time away from Connor.

That drove Harry particularly mad, as he knew that Draco was doing it on
purpose. But drawing too much attention would \emph{also} be against his
self-imposed rules. He knew that Draco wrote to his father every few
days. Would Lucius Malfoy like to hear that the Potters' elder son felt
so worried over the safety of the younger one that he couldn't trust the
professors and the spells on Hogwarts Castle to protect him? And what
would Draco think, if he began to consider that Harry's desperate
attempts to get back to Connor might be prompted by more than mere
sibling affection? Harry had shown, unwisely, how good he was at magic
that most students didn't learn until second or third year. He practiced
more often in broom closets and isolated classrooms after that, but the
damage had been done. Blaise and Greg and Vince all watched him with
something like respect, Draco with something like delight. And, of
course, Draco insisted on learning every charm that Harry knew.

On and on it went, until Harry began to feel, exasperated, more like a
Slytherin student than his brother's protector.

And then came Halloween. It stuck out in Harry's mind for other reasons
afterwards, but the first thing that brought it to mind was the fact
that he heard Connor be deliberately unkind.

That did not please him.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``Come on, Harry! I'm hungry.''

``Just a minute, Draco,'' Harry said absently, craning his neck. Ron and
Connor were just coming out of Charms class with the rest of the
Gryffindors. He wanted to see his brother and wish him a happy
anniversary. It was on this day ten years ago that Connor had defeated
Voldemort and saved the wizarding world, after all.

They were just in front of him, and Harry was smiling and about to say
something, when Connor snickered and remarked, apparently in response to
something Ron had said, ``Well, Hermione's \emph{got} to be good at
books; what else is she for?''

Harry stared. The remark reminded him of the one about Draco's name on
the train. Connor was \emph{capable} of deliberate malice, but it was
always sudden flashes like this, which faded into appropriate remorse.
And this one seemed so---undeserved. Hermione wasn't a Death Eater, not
anything like one, and she hadn't taunted Connor that Harry had ever
heard. At least Draco's father was a known quantity, a known enemy, and
Draco could have been, too.

He found his voice at last. ``Connor---'' he began.

And then pounding footsteps interrupted him, and Hermione fled past them
in tears. She vanished around the far corner of the hall before Harry
could put out a hand or speak the words that might have stopped her.

Harry turned his head back and gave Connor a slow, deliberate glance.
Connor flushed and opened his mouth, then hung his head.

``Go after her,'' said Harry. ``\emph{Apologize}, for Merlin's sake,
Connor. That was uncalled-for.'' He paused for a long moment. ``And
unworthy of you.''

Then he turned and stalked off, despite the fact that it was the longest
conversation he'd had with his brother in a week. Connor gasped and
shouted after him. Harry ignored him. The future leader of the wizarding
world could not afford such flaws in his character. Lily had handled
them with the silent treatment at home. Harry didn't know how well it
would work here, but he was prepared to try the same thing.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Draco was very quiet during the Halloween Feast. He ate, of course, but
he mostly watched Harry. Harry was brooding, and despite the pleading
glances that regularly came his way from the Gryffindor table, he
refused to look in that direction---perhaps because the Mudblood Granger
still hadn't come back to sit with everyone else.

\emph{Interesting. I think he'd give up his life for his brother, but
he's not willing to give up that fussiness he'd probably call his
morals. Hmmm.}

Draco at last opened his mouth to speak to Harry about it, but swung his
head sharply around when the doors of the Great Hall flew open with a
bang. Professor Quirrell staggered in and stood blinking on the
threshold for a moment. His turban had come half-unwrapped from his
head. The look in his eyes made Draco roll his.

``T-troll,'' he said at last, faintly. ``In the dungeons. I thought you
ought to know.'' Then he swayed and fainted dead away.

Chaos erupted then, with the Heads of House snapping at the prefects to
take the younger children back to the safety of the common rooms, and
the professors spreading out grimly to search the castle. Draco wasn't
scared; he rose with the rest of the Slytherin table when he was told
to, and headed calmly towards the dungeons. They passed Professor Snape
on the way, his stride firm and his dark eyes flashing dangerously.
Draco smirked. He felt rather sorry for any troll that had to face
Professor Snape.

Then, of course, he saw Harry peel off from the rest of the House and
hurry away.

Hissing, Draco snagged the back of Harry's robe and dragged him towards
the line again. ``What did you think you were doing?'' he whispered in
his ear. ``You'll only get in trouble when Professor Snape sees you're
gone, and I'll have to take the blame. Besides, there's a troll
wandering around the castle, or did you forget that bit?''

Harry looked at him. Draco recoiled, dropping his hand. There was a
stranger in Harry's eyes, determined, implacable, full of intent
resolve. He didn't look like a first-year.

``Hermione's missing,'' said Harry softly. ``And Connor and Ron just
left the Gryffindor line. I think they've gone in search of her.''

Draco snored. ``That's a long chain of suppositions to hang your own
safety on,'' he said. ``Come \emph{on}.''

Harry shrugged. ``I might be wrong,'' he said, calmly. ``Maybe they
didn't go looking for Hermione. But, regardless, my brother's out there.
I \emph{am} going to protect him.'' He said the last words with all the
finality of a Runespoor's bite, and then turned and ran down the hall
before Draco could stop him. Hesitating one last time---merely to make
sure that the Slytherin prefects were too busy with everyone else to
watch them go, Draco assured himself---he tore after Harry.

``All this for a Mudblood,'' he muttered.

``Just like our mother,'' Harry said, mildly, without looking at him.

Draco winced. Harry was like that, sometimes, striking home with one
small and calm remark. ``I didn't mean it that way---''

``Draco,'' said Harry, in a tone of infinite patience, ``shut up.''

Draco shut up. He followed Harry, who seemed to know where he was going.
He nearly banged into him when Harry pulled up abruptly, and then peered
over Harry's shoulder and around the corner. The sight in front of him
was enough to take all the spit out of his mouth.

They'd found the troll.

It was huge, and gray, and lumbered like a sculpture come to life. It
hesitated for a long moment, then moved into the girls' loo at the end
of the hall. A moment later, two small figures pelted in after it.

``\emph{Connor},'' said Harry, with a tone in his voice that Draco
couldn't identify, and then ran. He was unfairly fast, and Draco fell
behind soon enough. He entered the loo in time to hear the screaming,
though, and then to see part of the problem. The troll had backed
Granger into a corner, and Potter and Weasley were trying to levitate
its club above its head.

It failed. Of course it did, Draco thought; it was a Gryffindor plan.
The club dropped, and the troll grabbed it and dealt a sideways blow
faster than Draco would have thought it could move. The club only grazed
Weasley, though it still dropped him unconscious, but caught Potter a
devastating sideways blow that sent him flying into the wall.

Harry moved a step forward. Draco caught a glimpse of his face, and
cowered. At the same moment, a ferocious, violent headache sent him to
the floor. His shield was no longer enough to keep out Harry's rising
power.

``You shouldn't have hurt my brother,'' Harry told the troll, which
turned towards him, blinking stupidly. ``You \emph{really} shouldn't have
hurt my brother.'' Draco felt all future plans to hurt Potter physically
wither and die in the flame of his stare. Harry thrust out a hand.
``\emph{Incendio}!''

The troll's club burst into flame. It howled and dropped the thing, but
Harry snapped, ``\emph{Wingardium Leviosa}!'' and the club hovered, then
flew back and smashed into the troll. The troll hopped around in a
circle, burning and screaming. Harry took another step forward and said,
in a voice that in and of itself carried enough power to make Draco's
temples throb, ``\emph{Finite Incantatem}.''

The fire went out, and the club fell on the troll's head with a very
final crash. It collapsed with a little whimper, and then lay still.
Draco shivered, both at the display of power and at the smell of burning
troll flesh.

And there was also the little fact that Harry hadn't used his wand for
any of those three spells.

Harry turned around, panting heavily, putting a hand out for support
that wasn't there. Draco hurried to provide it, but only managed to
catch Harry as he sagged to his knees. He didn't say anything. He didn't
know what to say.

Granger crept out of the corner and stared at them.

``Connor,'' Harry said, lifting his head. His eyes had come back to
almost normal, if glazed and panicked and wide was ``normal.'' ``Is he
alive?''

``I'll check,'' said Draco, since it meant so much to Harry, and went
over to Potter. He was breathing, and though there was a goose-egg on
the back of his head and a bruise along his ribs when Draco gingerly
peeked beneath his robes, he didn't seem seriously injured. Draco sighed
and nodded at Harry. ``He'll live.''

``I would heal him,'' Harry muttered, ``but I don't know any medical
magic yet.''

``What you do know is \emph{very} fucking impressive,'' Draco said dryly.
He felt the urge to giggle, and didn't give in, because once he did,
there would be no stopping it. He was half-high on the feeling of magic
that still ebbed and danced in the air, centering on Harry, and he had a
headache that would have been appropriate for a night of stiff drinking.
He dropped down to the floor again. ``I don't think I can move,'' he
said, pathetically, to no one in particular.

Footsteps invaded the room then, and Draco's head, making the pounding
worse. He winced, and looked up to see Professor McGonagall, the
Gryffindor Head of House, in the doorway, staring at the felled troll.

``What happened?'' she demanded, turning and squinting at Draco.

Draco opened his mouth to explain, but Harry got there first, all smooth
charm and utter believability. ``It was my brother, Professor,'' he
said. ``He hurled a spell at the troll I've never even \emph{seen}
before, a combination of---of the Levitation Charm we learned just today
and something that caused fire.'' He shook his head back and forth. The
wideness of his eyes made him look innocent, Draco thought, and butter
probably wouldn't melt in his mouth as he blinked at McGonagall. ``The
force of it knocked him out, and he's wounded, but he saved my life. He
saved all our lives.''

McGonagall's face softened, and she nodded once. Then she said, ``But
why were you here in the first place?''

Draco again attempted to assist the cause of truth, but Harry got in the
way again. ``I followed the troll, Professor. I thought I could defeat
it.'' He looked down bashfully. ``It just gets tiring, sometimes, living
in my brother's shadow.'' He added a perfect ingratiating whine that
Draco recognized as an imitation of himself. ``Do you know what I
mean?''

``That was extremely foolish of you, Mister Potter,'' said McGonagall,
the warmth in her face mostly gone. ``Ten points from Slytherin, for the
utter, utter \emph{foolishness} of your actions.''

Draco opened his mouth to protest the unfairness of everything, but the
other professors appeared then, clucking and exclaiming, and he got
swept away in the general tumult. He did see Hermione Granger watching
the entire scene with speculative eyes, her head cocked to one side. But
when Harry caught her eye and mouthed, ``They were coming after you,''
she appeared willing to let the matter lie.

Draco wasn't. While McGonagall levitated Weasley and Potter to the
infirmary, and Harry trotted beside them, breathless and exhausted and
happy, he fought his way to Professor Snape's side. The Slytherin Head
of House leaned on the wall, his eyes alternately on his colleagues and
the dead troll.

``Potter didn't do that,'' Draco insisted, when Snape deigned to pay
attention to him. ``Harry did. Wandless, even! And now the old cat's
taken points, and it's---it's just all so \emph{unfair.}'' He winced and
fell silent then, because his head really did hurt.

``I know, Draco,'' said Snape calmly. His voice had some tamped-down
emotion in it, but it was so repressed that Draco couldn't tell what it
was. He merely surveyed the scene, and his eyes gave nothing away,
either. ``But I must wait a few days before restoring Slytherin's
points. I have to account for why I gave them, after all.''

``I didn't mean that part!'' Draco wailed. ``Well, not just that part! I
meant---''

Snape nodded to him. ``I know,'' he said. ``But I have learned that the
best way to confront our Slytherin Potter is not directly. He can resist
that, and rather spectacularly well, it looks like,'' he added, with one
more glance around the room. ``We must wait, and be indirect. Now, come
with me. I have a potion that will soothe your headache.'' He swept out
of the room.

Draco winced and hesitated. On the one hand, he felt like he should be
with Harry in the infirmary.

On the other hand, his head pounded like a gong.

In the end, he followed Snape, and composed a letter in his head to his
father the whole way. \emph{Dear Father, Harry is being exasperating.
And stupid. And risking his life where he doesn't need to, and then
refusing to even take credit for it, which would be the only reason for
such a thing. And he gave me a} headache.

\chapter{Dares and Dives}\label{chapter-8-dares-and-dives}

Harry smiled as Draco cast a stone into the lake and yelled for the
Giant Squid to come up and attack him if it wasn't a coward. Draco would
run in the opposite direction if that ever happened, of course, but it
was funny to think about. And Harry was in a generally good mood this
morning, certainly enough to find Draco's jokes amusing.

Connor was well. He'd been released from the infirmary the yesterday,
along with a stern warning from Madam Pomfrey ``not to do whatever it
was that you did again, young man!'' Ron was up even before then. And
Connor, though he seemed dazed when asked about the troll, had accepted
the story of his defeating it without trouble. It probably helped, Harry
thought, that awed mutters and glances tended to follow him now, and
that the Gryffindor Head of House had been more than usually kind to
him.

Hermione seemed to know the truth, but though she watched Harry
constantly on Friday---he would look up from reading a book in the
library, and there she would be---she didn't bring it up. She had even
befriended Connor and Ron, to an extent, if her stiff efforts to include
them in a lecture on Friday were any indication. Harry was willing to
let it rest for now. He could urge them closer later.

And Draco hadn't brought up the truth, either, for which Harry was more
than grateful. He smirked when someone else talked about Connor and the
troll, and at every mention of ``wandless magic'' his elbow dug into
Harry's ribs, but he didn't talk. Harry thought he knew that McGonagall
and the rest wouldn't believe him. Even Snape probably did not. He had
his hands full hating Connor and Harry for being Potters, and thus James
through them.

Harry looked up as Draco said, ``I saw a shadow in the lake.'' He was
trying to be confident, but his voice rippled, like the water that had
probably been all he saw. ``I think we should head back to the castle
now.''

Harry checked the sun; it was still early morning, since Draco had
learned his trick of rising early on Saturdays and adjusted his sleeping
schedule to catch Harry then, too. But the Great Hall would probably be
open for breakfast by now, and Draco really had been agreeable,
following him around the lake and chattering nonstop about something
other than Harry being a Slytherin. ``All right,'' he agreed, and turned
back towards Hogwarts.

As they neared the castle, his eyes strayed to Gryffindor Tower, by
habit, and then he froze. A figure on a broomstick, shrunk by distance,
darted around the Tower, retrieving small objects that fell---or were
hurled, more likely, Harry thought---out of windows. The sound of
laughter was audible even from here. And Harry could recognize Connor on
a broomstick. He'd \emph{trained} in recognizing Connor on a broomstick,
in case they were ever in flight among enemies and he had to cast spells
without looking at someone's face first.

``Isn't that your brother?'' Draco said, at the same moment. ``Where did
he get a broom?''

``Probably sneaked out to the pitch and stole one,'' said Harry, his
eyes narrowing as Connor essayed a particularly daring swoop. He
spiraled once, wobbled as if he would bash into the side of the Tower,
and then soared up, laughing. Harry had no doubt that he'd caught
whatever it was he chased. He let his shoulders sag in relief. ``He's a
good flyer, though, don't you think?'' he added, turning to Draco.

Draco was watching him, and not Connor. Draco was disturbing that way,
Harry reflected. ``Not half as good as you are,'' he murmured.

``He's much better than me,'' Harry said. \emph{Not true, but he's much
better than Draco gives him credit for.} ``You ought to see us fly after
a practice Snitch together. Connor wins every time.''

``Because you let him,'' said Draco, in a soft, mocking voice.

``On his own merits!'' Harry hissed. He wondered if there was, after
all, something worse than Draco confronting him immediately after the
troll incident and demanding an explanation. Draco seemed to have
decided that the way Harry protected Connor from physical harm extended
into protecting him from any possible embarrassment, too.

\emph{Well, it does, but he has no right to} assume \emph{that it does.}

``\emph{Mister} Potter!''

Harry blinked and jerked his head up. It was Professor McGonagall who
spoke, though, and she was standing at the base of Gryffindor Tower, her
arms folded and her head tilted up. Connor didn't appear to see or hear
her. He swerved down, caught one more object too small for Harry to see,
and held it up to cheers and applause through the Tower windows.

``\emph{Mister} Potter,'' said McGonagall again, somehow managing to sound
equally forceful even though she'd raised her voice. ``Come down here
\emph{this instant.}''

Harry winced at her tone, especially as Connor heard her this time and
froze on the broomstick. Then he spiraled softly down. His head was
bowed, and Harry knew, though he couldn't see them, that his knuckles
would be white where they gripped the broom handle. Connor hated being
in trouble, or getting yelled at.

Harry hurried over. Draco, behind him, said nothing except for one quick
whisper of, ``You try to take the blame for this and I will give you
\emph{such} a thump.''

Harry didn't intend to take the blame. He just wanted to be there to
hear what the punishment was, so that he could commiserate with Connor
and agree whether or not it would be worth the crime.

McGonagall stood where she was for a long moment, lips pursed as she
stared at Connor. Harry's brother had hopped off the broomstick and
stood with his head bowed. It was a posture of genuine contrition, which
had often gotten him out of trouble at home. But McGonagall wasn't
James, and Harry braced himself as she opened her mouth.

``Mister Potter,'' she said. ``You know that you broke the rules by
flying without permission.''

``Yes, ma'am,'' Connor whispered. His voice sounded so small. Harry
would have gone forward and gotten in front of him, to deflect
McGonagall's attention, but he thought she would have gotten irritated
at him without dropping her irritation for Connor. Besides, Draco had a
death grip on his arm.

``And you know that you were hurt in your battle with the troll two days
ago and have \emph{no} reason to be up and flying,'' she continued.

``Yes, ma'am.''

``That said,'' McGonagall said, unfolding her arms, ``it will be to your
advantage to respect your position on the Gryffindor Quidditch team.''
Harry felt a warmth flooding his heart. Connor jerked his head up and
stared at McGonagall. ``We have desperate need of a Seeker,'' McGonagall
went on, ``which is the \emph{only} reason I am allowing this. But you
will not skip practices, Mr. Potter, nor will you abuse your teammates'
trust in you. Do you understand?''

Connor nodded, his eyes and his whole face shining with a light that
Harry knew well enough most people could not resist. Slytherins seemed
to be the exception, but Slytherins were the exceptions for lots of
things. ``Of course, ma'am! I promise! Thank you!''

McGonagall nodded at him. ``We had a practice this morning,'' she said
as she turned away, ``but you will need to report to Oliver Wood, the
team Captain, on your own time and have him instruct you in plays.''

Connor bounced up and down on his toes, grinning. ``I understand, ma'am.
Thank you!'' he added again, his voice exuberant.

Harry caught sight of McGonagall's faint smile as she passed. It seemed
even the stern Head of Gryffindor House was not immune to Connor's
charm.

``Congratulations, Connor,'' he said quietly. He was glad that he got to
be the first one to say that. There were confused, semi-cheerful sounds
coming from Gryffindor Tower, but none of them had had time to get out
of the Tower and down to the ground yet.

Connor nodded at him. Then his face firmed, and Harry blinked at the
change in his eyes and the set of his jaw.

He grabbed Harry's arm and dragged him towards the castle. Harry
stumbled before he managed to catch his balance and follow. He was much
more used to Draco pulling this kind of trick, and wondered what in the
world Connor could be thinking of doing.

``Where are we going?'' he asked, as they plowed through the doors and
in the direction of the Great Hall. But Connor turned before they got
there, leading him to the dungeons.

``I promised that you would get all the same chances that I get,'' was
Connor's only explanation, and soon enough they were hurrying along a
familiar hallway. Harry had a bad feeling when Connor paused and knocked
on the door of Snape's office.

There was a long, long silence, as though Snape were behind the door
asking himself incredulously who would dare disturb him this early in
the morning, and on a Saturday, no less. Harry shifted, and tried a new
tactic. ``Connor, thank you. You're wonderfully brave and generous. But
it's not necessary, really---''

The door opened then, and Snape, as ready to sneer as he was on days
when they had class, stood framed in it. ``The Brothers \emph{Potter},''
he said, making their last name sound like an obscenity. ``What do you
want?''

Connor lifted his chin. ``Professor Snape,'' he said formally, ``I've
just been made Seeker on the Gryffindor Quidditch team.''

Harry saw the professor's face grow tight with rage for a moment, but
his voice showed no change. ``I see,'' he replied, sarcasm dripping from
the words. ``And this would be your promotional tour, perhaps? Your way
of soliciting congratulations from all and sundry?''

``This has nothing to do with me,'' said Connor firmly, and thrust Harry
forward. ``My brother's as good a Seeker as I am. If Professor
McGonagall is going to break the rules and let me fly for Gryffindor,
even though I'm a first-year, then I think it's only fair that Harry
should get to fly for Slytherin.''

Harry winced and cowered. He could well imagine the force of the
invective Snape was about to unleash, and he didn't look forward to the
way that Connor's face would crumple and flush as he struggled not to
cry.

There was silence instead. And then Snape said, in the even tone that
was as close as he ever seemed to come to courtesy, ``Thank you, Mr.
Potter. That is indeed an excellent idea. I approve entirely. Come in,
Mr. Potter,'' he said, nodding at Harry, ``so that we can discuss this
further.'' He stepped out of the way and gestured into the office, as
though in invitation.

Harry would have rather entered a dragon's lair. ``My brother's
mistaken, Professor Snape,'' he blurted, chasing the first idea that
came to mind. ``I could never beat him in our practice matches. I
wouldn't want to give Slytherin an inferior Seeker---''

``Don't listen to him, Professor,'' Connor interrupted. ``He's nearly
taken the Snitch away from me more than once. And I'm \emph{really}
good,'' he added, with that artless self-adulation that Harry so often
encouraged and now wished would dry up for just a few minutes.

``I have no reason to doubt you,'' Snape assured him gravely, which made
Harry only more certain he was howling with laughter inside. ``But since
the first match is in a week, and it will be between Gryffindor and
Slytherin, then I wish to advise Mr. Potter of
the\ldots{}strategy\ldots{}he should adopt.'' His eyes came back to
Harry's face and lingered there. Then he smiled. It was not at all a
nice smile.

Harry said, ``Really, sir, you don't have to do this. I know how much
you hate bending the rules.''

``Harry.''

He glanced sideways at Connor, who was smiling at him with the gentle,
patient expression of a sibling pushed almost to the limits of his
tolerance.

``Do this,'' Connor whispered. ``Please. I want you to. I'd be miserable
if I were flying and you weren't. Please?''

Harry sighed and bowed his head. \emph{Why not? It's not as though I
have to win the game. Everyone has seen how good we are separately, but
no one's seen us in competition, and when they do, then they'll only
notice what Mum and Dad did whenever I played Connor.}

Those thoughts reassured him. This was a deception, but unlike the
desperate one he'd made up Halloween night to turn Connor into a hero,
it was an old and familiar one. Harry breathed a bit easier.

``If you really want me on the team, sir,'' he said to Professor Snape,
``I'll do it.''

``Indeed,'' said Snape. ``Now, step inside my office, Mr. Potter. We
really \emph{must} talk.''

Connor patted Harry's shoulder. Then he said, ``See you later, Harry.
Professor.'' A nod, and he was gone.

Harry stared at Snape for a long moment. His Head of House's eyes showed
no sign of yielding, so he bowed his head again and plodded into the
room.

The door shut with a soft sound. Harry hoped for some silence, but Snape
tore into him at once.

``You are a fool if you think that I will permit Gryffindor to beat
Slytherin,'' he said, circling around in front of Harry. Harry kept his
eyes on the floor. That didn't dim his consciousness of Snape's gaze on
him, or how triumphant it was. ``And I \emph{know} that you are not a
fool, Mr. Potter. You will kindly stop acting as if you are. You will
become Slytherin's Seeker. And you will win our matches, Mr. Potter.''

``Connor really is better than I am, sir,'' Harry tried.

``I don't believe you,'' Snape assured him, voice a purr. ``After the
incident with the troll, Mr. Potter, I wonder if I should believe you
ever again.''

Harry looked up in shock. He really, really had not thought that Snape
believed Draco's side of the story, even if Draco had told him. The
story Harry had made up sounded so much better, confirming as it would
for Snape the utter arrogance of both James Potter's sons and their
rule-breaking tendencies.

Snape smirked at him and cocked his head.

``I know what you are, Mr. Potter,'' he breathed. ``And do you know
why?'' Harry shook his head, heart like a drumbeat in his ears, almost
obscuring Snape's next whispered words. ``I am a Slytherin, too.
Maneuvering, lying, half-truths, concealment---they are second nature to
me. And your attempts are amateurish at best.'' He laughed when Harry
glared at him. ``Oh, yes, they are. They depend too heavily on the
listener being utterly besotted with our resident hero. As I am not, I
prefer to look for the true cause. The \emph{Slytherin} cause, Mr.
Potter.'' He hissed the last words, and Harry spoke before he thought.

``I'm not going to be a good Seeker, Professor. I'll just throw the
game. And Connor will still win anyway.''

Snape's smile vanished. He leaned close enough that Harry flinched, but
he couldn't seem to look away. Snape's eyes burned like black ice.

``If you do not win this game, Potter,'' Snape said softly, ``if you do
not make every effort to be what I know you are, then you will have
detention every night for the rest of the term. I will speak with
Headmaster Dumbledore and arrange it myself---the way that I intend to
arrange for you to become Seeker. And there will be \emph{nothing} you
can do about it. Is that clear?''

Harry growled, helpless. He didn't want to play Connor, he didn't want
to take even the chance of showing Connor up, and here the Professor
was, forcing him into it.

But he couldn't afford to give his nights up, either. Since Draco stuck
by him so closely from morning until night, Harry had finally gotten the
idea of following Professor Quirrell around after curfew. He couldn't do
that if he was in detention with Snape. Snape would probably take him
back to the common room himself.

``Yes, sir,'' Harry said at last, forcing the words out.

Someone knocked on the door just then, and Draco's worried voice called
out, ``Harry? Professor Snape? Are you in there?''

Snape chuckled darkly. ``He sounds as though he fears we have torn each
other apart,'' he murmured, and then leaned nearer to Harry. ``But I will
be the one tearing \emph{you} apart if you fail to live up to my
expectations, Mr. Potter.''

``Yes, sir,'' Harry said again, full of helpless hatred.

``Find Marcus Flint,'' Snape instructed him as he paced to open the door
on Draco. ``He is our Quidditch Captain. He will see about integrating
you into practices. And do strive your hardest, Mr. Potter. The match is
only a week away, after all.''

Harry, his good mood utterly ruined, bowed his head and left without a
word, despite all the questions that Draco asked on the way to the Great
Hall.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Snape smiled after Harry, careful to make it a predatory smile and not
one of sheerest exultation. This had been a good morning, far better
than he might have expected when he heard the hated Potter's voice
calling through the door.

\emph{I will set James Potter's sons against one another. How he will
writhe and squirm when he hears of that! And if I can encourage Harry
into acting against whatever his father taught him about yielding to his
brother, then I will have done the world a positive service, turning an
arrogant Potter spawn into a useful person.}

\emph{And more\ldots{}}

Snape shook his head slightly. It was too much to hope for, based on a
few sensations of power, some native Seeker talent, and one troll
defeat, that Harry would actually become a shining figure, someone the
other Houses and the wider wizarding world were \emph{forced} to take
notice of and respect. Snape was intensely practical. It was not
practical to gaze at the future with rose-glassed eyes.

\emph{But if I see the chance, I will take it. For too long, Gryffindor
has been beloved and Slytherin scorned. They look at us and see the Dark
Lord.}

\emph{If we could produce a hero of our own\ldots{}if we could make them
acknowledge, all against their wills, that heroism is more than just not
knowing when to stay out of a fight\ldots{}}

Snape carefully locked the thoughts up again. They were becoming too
ambitious, and this was a burning, nourished, long-held dream, something
he thought of anew each year when the first-year Slytherins entered his
House. He would find someone, someday, who had both the native quality
and the potential to be taught and molded. He would push that person
into the light, and see Slytherin take up its rightful position of glory
once again.

Harry had every chance of not being that person.

But, Snape acknowledged as he stepped back into his office and shut the
door, he was the best candidate Snape had seen yet.

\chapter{Sacrificial Unicorn}\label{chapter-9-sacrificial-unicorn}

It had taken forever for the other boys to fall asleep. Harry had slept
in the same room as Connor at home, and until now had never appreciated
what a luxury that was, sharing space with only one other person. And
Connor was a fairly heavy sleeper, too, unlikely to awaken if Harry
wanted to practice spells under his breath or read a book under the
covers with a \emph{Lumos} going.

But he could put up with the noise, he thought, if only he could trust
that the noise meant the other boys wouldn't be waking for the rest of
the night.

After the fourth mumble-mutter that might or might not have been a snore
from Blaise, Harry had had enough. He cast \emph{Consopio} on all four
boys, and listened as their breathing slid into a soft, relaxed rhythm.
Harry sighed and crept out of the room. He should be back before the
spell wore off; it was a gentle Charm that Lily had used on him and
Connor when they were children and had been awake for more than twelve
hours straight.

He had another \emph{Consopio} ready on his lips when he reached the
Slytherin common room, but for once no one had fallen asleep here. He
increased his pace as he reached the common room door. Professor
Quirrell might already have retired for the night. In fact, Harry
reflected as he slid the door open and glanced up and down the corridor,
that would be typical of the kind of luck he'd had today.

\emph{Could Marcus Flint be any more of a prat?} Harry thought
indignantly as he made his way down the empty hallway. \emph{Just
because I didn't catch the Snitch in the first ten minutes doesn't mean
I'm incompetent.} Normally, he would have been pleased enough that
someone else thought his performance below par, but not when Marcus
might whine to Professor Snape and get Harry detention.

The very thought of that made Harry want to hex Snape, though preferably
from a safe distance. What he was doing was \emph{important}. It might
mean lives, even more lives than Connor's, if Professor Quirrell was
doing something dangerous. He could be a Death Eater, and not one who
had reformed the way that Snape had. He could be a mere helper or ally
of Voldemort. But Harry's dreams suggested he was more ominous even than
that.

\emph{And that's another thing,} Harry thought, as he ghosted up the
dungeon stairs and towards the professor's office. \emph{Do I trust my
dreams? I don't know why I'm even having them. It's not as though my
scar is any kind of mark from Voldemort, the way that Connor's is.}

He and Lily had tried to develop his ability to dream prophetically,
despite Lily making loud and common comments about what a load of
bollocks Divination was, but had had no success. True Seer ability was
inborn, Lily had decided, like being a Metamorphmagus, and Harry simply
did not have it.

Harry felt like hexing somebody again as he considered that. It was
unfair that he not be able to develop any ability which could be the key
to protecting Connor, now or in the future.

\emph{But maybe I finally have. And I would be foolish to ignore these
dreams.}

Harry halted near Quirrell's office door and listened carefully. He
heard no sound. Of course, the professor had probably gone to bed
already. With a sigh, Harry sat down near the door.

\emph{I'll fall asleep,} he thought, pinching his arm to keep awake when
his eyelids began to droop. \emph{It's these damn classes. Why do they
give us so much homework? I have better things to do than write a
three-foot essay on why you should never Transfigure a doorknob into a
marble.}

He was so convinced that he would find nothing today that he nearly
didn't get out of the way in time when the door opened. Quirrell
shuffled out as Harry ducked around the corner, then turned and locked
his office door behind him. For a while, he stood there, trembling like
a leaf in the wind. Harry frowned. \emph{He doesn't look threatening
when he's like this.}

Then Quirrell turned and strode down the hall, his face set as he passed
Harry. Harry smiled as he followed. \emph{Here we go.}

It was a dangerously difficult dance, making sure that he kept Quirrell
in sight without letting himself be spotted. Hogwarts, with its
propensity to shift staircases and walls at a moment's notice, made it
harder. And there was still the disturbing pain in his scar, sometimes,
and an occasional mutter from Quirrell that it frustrated Harry he was
too far away to figure out.

Still, after the third staircase, Harry had to admit he was enjoying
himself. He thought about that as best he could while still watching out
for both Quirrell and the next good hiding place.

\emph{I'm finally putting my training to use,} he decided at last, as he
crouched behind a suit of armor when Quirrell glanced back. \emph{The
troll was different. It attacked too fast. I just reacted out of rage.
But this is the kind of thing that I trained for, hiding and spying and
concealing things so that Connor won't be tainted by them. I think I'm
allowed to be happy.}

There was a difference between ``happy'' and ``dangerously manic,'' of
course, and Harry concentrated to make sure that he wasn't the latter.
When he had to drop behind Quirrell on some tricky stretch of corridor
where the moonlight coming through the windows could have revealed him
even better than the shadowy light of torches, he let the professor get
far ahead before following. And even when he knew for certain that
Quirrell was heading out of the castle, he resisted the temptation to
dart ahead and take a shorter route. Quirrell might have some reason for
going this way. If so, Harry would find out.

It didn't seem that he did; perhaps he had taken the longest route on
purpose to have more of a chance of spotting stalkers, Harry thought.
Professor Quirrell stepped out of Hogwarts and waited for a long moment,
as though he liked the feel of the cool November breeze on his face.
Harry, crouched in the doorway, clenched his hands together and felt a
delicious cold tingle in his heart. Was the professor headed to a secret
meeting? Was he about to see it?

Instead, Quirrell turned and headed rapidly off across school grounds.
Harry eyed the stretch of barren earth between him and his prey, sighed,
waited, and then took a risk and cast the Disillusionment Charm on
himself.

He shuddered at the feeling that passed through him, as if someone had
broken an egg over his head, and then waited some more. Quirrell didn't
look back at him. It seemed he could use magic, as long as he wasn't
obvious about it.

Harry strolled carefully across the ground, letting the Charm reflect
whatever was behind him at the moment. Lily had told him that someone
who paid attention could make out the effects of the Charm by noticing a
ripple, like a heat shimmer, wherever the person under it was moving.
Unlikely as that might be in the moonlight and the open, Harry wasn't
about to take a chance.

Professor Quirrell aimed past the hut of Rubeus Hagrid, the gamekeeper,
and into the dark mass of the Forbidden Forest.

Harry hissed. He \emph{hated} forests for sneaking around in. He'd
always done horribly in the ones near Godric's Hollow. And it was fall
now, and with the amount of leaves on the ground and which could be
dislodged from the branches\ldots{}

Harry shook his head. He didn't know of any spells that would shield him
from making noise without also obscuring his ability to make any noise
out. And he definitely wanted to be able to hear, since he assumed that
Professor Quirrell was probably meeting someone interesting indeed in
the woods.

Resolving to ask his mother about teaching him noise-muffling spells as
well as medical magic, Harry sped up a little and followed the professor
into the Forest.

He hadn't expected it to be so \emph{dark}, he admitted to himself after
his first near-stumble on a sudden bump in the trail. True, it was
night, but the Forest seemed to eat light alive, and exhale darkness.
Life was around them, but it breathed, in turn, slowly and carefully,
and Harry felt the unnerving tingle on his skin that came from the
presence of powerful, nonhuman magical creatures.

\emph{Centaurs live here, at least,} he thought, as he forced himself
deeper and deeper, pausing to duck branches and figure out the best way
around large piles of drifted leaves. \emph{What else?}

The fact that he couldn't remember, exactly, annoyed him, and unnerved
him further. And then Professor Quirrell sped up, and Harry had to
follow him without making noise, and fast, and in the dark.

If Professor Quirrell hadn't been muttering to himself, apparently
intent on a private conversation of some kind, Harry didn't think he
could have managed it. As it was, he finally, \emph{finally} got close
enough to overhear what Quirrell was saying.

Unsurprisingly, it sounded like part of a Death Eater plot.

``---and they'll see then, the ones who laughed, the ones who turned
their backs, won't they? \emph{Won't} they?'' Quirrell demanded as if
someone had argued with him, using a force he had never displayed in
class with his students. ``The ones who pretended they were all under the
Imperius, or spies, or for Dumbledore all the time. We'll show them.
They'll \emph{know} the folly of abandoning us.''

Harry shook his head. The professor sounded barking, but he also hadn't
stuttered once. And the way he was speaking sounded as if he were
talking about the Death Eaters who had pleaded their own innocence,
usually with the handy excuse of the Imperius Curse, after Voldemort's
fall.

\emph{I don't understand. Dumbledore only hired Snape because he was a}
reformed \emph{Death Eater. How could Quirrell have hidden some kind of
Death Eater affiliation from him? Wouldn't Dumbledore check to see that
he'd reformed first?}

Deep in thought, Harry nearly catapulted himself over his own feet as
the path dipped. He winced, then saw Quirrell turning around. Harry took
a deep breath and dropped, rolling sideways, so that he was half-hidden
behind a large bush that swayed menacingly. Harry hoped it was only
swaying with the wind.

``Who's there?'' said Quirrell, and his hand went for his wand. Harry
laid his hand on his own, wondering if he was about to have his first
proper battle with a Death Eater.

``\emph{Animals.}''

Harry shuddered. That voice was definitely \emph{not} Quirrell's, high
and cold and shrill. And it made Quirrell cower and turn about, his head
in his hands. His turban bobbed and swayed as he uttered a cry.

``I'm sorry, my lord!''

``\emph{Animals},'' the voice repeated. ``\emph{Get what we came for and
get out. Someone will miss us soon.}''

``Yes, my lord,'' Quirrell whispered, and then took out his wand and
cast some kind of complicated charm Harry had never seen before,
involving at least seven separate wand movements. Harry frowned. What
good would that kind of charm be in battle? Someone would probably kill
you before you could cast it.

\emph{So it must not be a charm that has anything to do with battle.}

And it didn't, as Harry saw after a moment, when the first true light in
that dreadful darkness glimmered through the trees, and the unicorn
approached them.

Harry stared. He'd seen images of unicorns in history books, and thought
he was prepared; after all, wizards looked rather like their own
portraits, so unicorns should, too. But nothing had prepared him for the
pale coat, or the sheer shine of the horn, or the way the legs unfolded
and stepped, more like a deer's legs than a horse's.

The unicorn paused a few steps away from Professor Quirrell, and sniffed
the air. Harry wondered if it smelled the garlic that the professor used
to keep vampires away. But the professor performed the charm again,
which Harry thought was some variant of the summoning charm, and the
unicorn came on, walking tamely towards Quirrell, now and then flicking
its tail.

Harry swallowed. There was a thickness in his throat, and he did not
think that Quirrell could intend anything good with the unicorn, for
whatever reason he'd summoned it.

\emph{I could stop him from killing it, or hurting it, or whatever it is
that he wants to do.}

\emph{And then I'd reveal that I'm here, and Connor's life would be in
danger without me. I think he could kill me. I'm just supposed to
observe.}

Harry considered looking away as the unicorn halted in front of Quirrell
and the professor reached towards its neck. But he swallowed again and
kept watching. His mother had told him that only cowards looked away
from death, that many of the Death Eaters had killed people with their
eyes shut. He would witness, since he couldn't rescue.

The professor reached up and whispered a spell Harry could not make out,
and was not sure he wanted to. At once an immense, bloody gash sprouted
down the side of the unicorn's neck, wreaking havoc on the silver fur,
spreading blue-silver light and life that flared like the moon. The
unicorn reared, screaming, and Harry shuddered, driving his fingers so
hard into his own hands that for a moment he feared he'd snap his wand.
He made no sound himself, though, and was glad when the unicorn fell to
the ground, golden hooves thrashing like trailing meteors. It would have
seemed disrespectful to take away from the sound of its death.

Quirrell knelt down beside the unicorn, avoiding the hooves, and bowed
his head. His mouth went to the gash on the unicorn's neck, and he began
to suck.

Harry fought furiously not to be sick. His mother had told him about
people who drank unicorn blood. It was a heinous crime, and not just
under Ministry law. There was something rare, magical, and pure about
unicorns themselves. The blood made anyone who drank it immortal for a
time, but shut off from the world, hidden behind hideous gray spiderwebs
that concealed all emotions and humanity.

He couldn't watch, in the end. He turned away and crouched down, and
waited until the sound of sucking stopped. The unicorn was dead by
then---at least, he hoped so. He closed his eyes and listened.

``When?'' Quirrell was asking, apparently declaiming to his invisible
audience. ``When can we hope that the insult will be avenged, the
disloyal ones punished, and the Potter brat brought to heel?''

Harry's eyes snapped open again. \emph{Connor. They're talking about
Connor. Him and---and whoever's with him.}

The cold voice spoke, and at the same moment a burning pain came to life
in Harry's forehead. He held still as it grew worse, because what that
voice had to say seemed more important than any agony he might suffer.

``\emph{Not long now. Not long now. We will destroy their hope in the
sight of all of them, and we will use the loyal ones to do it. There is
one who can help us. He is trusted by the old fool. He will come.}''

Harry retained the presence of mind to scramble off to the side of the
path as Professor Quirrell walked back along it. He never looked to the
side. His voice had returned to its constant low muttering. Harry didn't
attempt to follow, just kneeling where he was until the pain in his scar
had passed.

And, all the while, he considered what he'd heard, and what he was going
to do about it.

It was the first time he'd seriously considered turning to the
professors for help. He didn't know if he could face a Death Eater---or
whoever else Professor Quirrell had been talking to---on his own. He was
beyond unsure what might happen if they attacked Connor, in whatever
fashion they planned. Maybe he wouldn't be in the right place, at the
right time. Thanks to Draco, he almost never was anymore.

And he really should tell someone about seeing the unicorn killed.

But two things stopped him. For one, he'd have to reveal that he'd been
out here, and that he'd been spying on Quirrell because of his dreams,
and that would draw attention to him that he didn't want, from the
professors and eventually from the Death Eaters. The whole point of
training as he had was to keep back, to discourage anyone from thinking
that he was in any way more than an ordinary, slightly sulking wizard
child awed by his brother's reputation. He would destroy every advantage
of that if he went to the professors now.

And the second thing\ldots{}

``\emph{There is one who can help us. He is trusted by the old fool. He
will come.}''

Who was that?

Harry was horribly afraid that the cold voice meant Dumbledore, and that
meant someone he trusted was a traitor, someone who would conspire to
hurt Connor. Dumbledore was not infallible, as his hiring of Quirrell
proved. And even if Harry went to him personally, rather than a
professor, Dumbledore could tell the news to the traitor under the
impression that he would help defend the Boy-Who-Lived.

\emph{I'm afraid it's Snape,} Harry admitted to himself, \emph{but I
don't have any other proof than my dislike. And Dumbledore trusts an
awful lot of people.}

No. He would have to rely on himself, as he had trained.

And the unicorn was a casualty of war.

Harry forced himself to leave his sheltered space behind the bush, and
forced himself to walk over to the dead unicorn instead of retreating up
the path at once. He looked down at it for a long moment, and wished
fiercely that it were still alive. He wanted to say something, but
couldn't think of any words that would stand up to what had happened.

``Goodbye,'' he said at last.

He turned and left, listening to the speech their mother had given him
the day before they left for Hogwarts playing over and over in his head.

``\emph{War requires sacrifices, Harry, sacrifices from all of us. It
requires time, and blood, and sweat, and lives. And, most of all, it
requires part of the souls of those who participate in it.}'' Lily had
closed her eyes, looking ill, and Harry knew she was remembering some of
the things that she had seen and done during the time of Voldemort's
first rise. Then she opened her eyes, and they burned into his, intense,
opaque green. These were the eyes that neither her husband nor her
younger son ever saw, the look she reserved for Harry alone.

``\emph{People around you are going to die, Harry,}'' she'd said quietly.
``\emph{People will be injured, and have their lives taken away, and have
bits of their souls snatched when friends are injured or die, or when
they kill. I think that last is the worst. It tainted Voldemort. It
could taint Connor.}''

She'd reached forward and clasped his hands, holding them firmly, his
new wand caught in between them. ``\emph{I'm asking you not to let that
happen to him, Harry. He has to grow up as normal as possible, even
though he's the Boy-Who-Lived. If he gets used to killing, to fighting
too young, then he won't retain the essential purity and love he needs
to defeat Voldemort. I know that I'm asking you to sacrifice your own
innocence, and I'm sorry for it. But this is war, Harry.}''

Harry had nodded then, and he nodded now, biting his lip. The unicorn
was a sacrifice. He'd been a sacrifice, in Lily's terms, even though he
didn't think of himself that way; he was just making sure that Connor
got to enjoy a chance in the sun that would otherwise be snatched away,
and unfairly.

And he loved his brother enough to lie for him, and to burn a troll for
him, and to let a unicorn die for him.

He loved him enough to play Quidditch against him---

Harry froze between one step and another, remembering what else that
cold voice had said.

``\emph{We will destroy their hope in the sight of all of them\ldots{}}''

They were going to attack Connor on the Quidditch pitch, during the
Gryffindor-Slytherin game, in front of the whole school.

Harry hurried frantically towards the castle now. He could see no sign
of Quirrell anywhere, and he had to get even better at wandless magic
than he was by the time Saturday rolled around.

\chapter{Connor's Big Day}\label{chapter-10-connors-big-day}

``Connor!''

``Dad!''

Harry smiled as he watched their father swing Connor up and around in a
circle, his red Quidditch robes trailing behind him like streaks of
flame.

\emph{Or the unicorn's hooves, kicking in the forest that night\ldots{}}

Harry shook the impression away, and moved carefully out of the doorway
of Hogwarts so that their parents could see him. They'd come up to greet
Connor just as he left, heading down to the pitch for one last-minute
drill or practice with the mad Gryffindor Captain, Oliver Wood. Lily
stood slightly behind James, smiling at both of them with a faintly
wistful cast around her eyes, as though she knew that moments like this
couldn't last for long. Sirius and Remus were here, Harry saw, but had
paused to stand by the lake, and appeared to be having an animated
argument that could have involved anything from the Giant Squid to the
last girl Sirius had dated.

``Harry.''

Harry smiled again when he saw that his mother had noticed him. He came
forward and stood in front of her, and she reached out a careful hand,
running her fingers through his hair. From her alone, Harry liked the
gesture. She knew how to actually \emph{arrange} his hair, so that it
looked less messed-up rather than more. He leaned against her, and she
put one arm around him.

``We heard how you defended your brother, Harry,'' she whispered. ``We
are proud.'' Her eyes glimmered with tears, briefly, as she squeezed his
shoulder.

Harry nodded. He and Connor had both sent letters to their parents after
the troll incident, and even though both of them had told the exact same
story, Lily would have known how to read between the lines. The look on
her face gave him a warm, contented feeling. He had had letters from her
in the past few months, of course, including one reassuring him firmly
that his parents were startled but not disgusted that he'd been Sorted
into Slytherin. Connor had written even before he could, even before
Harry came and talked to him, saying that there must have been a
mistake, and now all the Potters were united firmly behind his theory
that there \emph{had} been a mistake, probably on the Sorting Hat's
part.

James put Connor down and came over to Harry, embracing him and ruffling
his hair, destroying Lily's order. Harry caught their mother's glance,
and they exchanged an eye-roll, while Lily fussed over Connor and
admitted that his Quidditch robes did indeed make him look very
handsome.

``Harry! There you are.''

Harry turned to greet Sirius, who looked tired. Harry frowned. ``Haven't
you been sleeping well?'' he asked his godfather.

Remus snickered behind Sirius's shoulder, then ducked without even
looking when Sirius tried to punch him. ``You could say that,'' said
Remus. ``Of course, not sleeping \emph{at all} would have been more
accurate.''

``I like to have fun,'' Sirius defended himself, in a sulky mutter that
made him sound younger than Connor. He increased the impression by
rubbing one hand over his face, emphasizing the dark circles around his
gray eyes. ``I always did.''

``Yes, but you're not nineteen any more, Sirius,'' Remus said, facing
him with gentle humor in his amber eyes. It was just past the dark of
moon, and Remus looked healthier than he did most other times of the
month, Harry thought---definitely healthier than Sirius did just now.
``And you're not eleven, either, no matter how much you sometimes act
like it---''

Sirius tried to tackle Remus. Harry got hastily out of the way, and
watched in delight. He'd missed their frequent fights since he got to
Hogwarts, something he was used to at home. Sirius and Remus had never
really had to grow up, he thought sometimes, despite tragedies like
Peter's betrayal and near-tragedies like Voldemort's attack on Godric's
Hollow. They could still play like this, still have fun, as Sirius said.
Harry thought that, if Connor could reach their age and still act this
innocent, he himself would die content.

``Potter!''

Four heads turned, which Harry found amusing, but only until he saw
Snape standing in the doorway. His eyes were fixed on James, and there
was a hatred in his face that made Harry understand all the unkindness
he'd shown so far was only a shadow of the real thing.

James, for his part, froze, his hazel eyes fierce. Then he took one step
forward.

``Snivellus, is it?'' Sirius asked, letting Remus go from the headlock
he'd got him in. ``We can show him!'' He strode up eagerly to match
James.

Harry winced. He didn't like \emph{this} part of the Marauders'
innocence. It meant they held onto childhood grudges far too long.

Of course, Snape wasn't that much better, Harry thought, as he observed
his Head of House's narrow lips and poisoned stare, and he was, on the
outside at least, anything but innocent.

``Potter,'' Snape repeated, his voice almost caressing the name. His
gaze fastened on Harry then, and he motioned curtly to him. ``Get
yourself into the Quidditch robes you should already be wearing, and
then find Flint. You are to be on the patch at the proper time. You are
not to embarrass Slytherin House in front of anyone.'' His gaze shifted
back to James, and he sneered. ``Even those who would love to see you
fail.''

``I don't live for seeing either of my sons fail, Snape,'' James said,
and Harry had never heard a tone like that in his father's voice before,
scraped raw and cold. ``I \emph{do} know that Connor's going to win, but
that's just a matter of natural talent. And we all know it's a mistake,
anyway, that Harry's in Slytherin. He's not cold and slimy like the rest
of you.'' He half-lowered his head, reminding Harry of the stag he could
become at times. ``You're not going to convince me to hate my son,
Snape, however much you may want to.''

Snape's stare snapped back to Harry. Harry winced, but held his chin up
and endured it. He knew that at least part of its force was puzzlement;
Snape must not have realized that he concealed his talent at Quidditch
even from his parents. Of course, Snape could say that, and James and
Lily still wouldn't believe him. They wouldn't believe anything that a
Slytherin said.

Never in his life had Harry been so grateful for that.

``Potter,'' said Snape. ``Into your Quidditch robes.'' And he turned
around and left, his robes snapping behind him, oblivious to the insults
that James and Sirius tossed at his heels. Remus winced and hung back,
as he tended to do.

Harry shrugged at his family. ``Sorry,'' he said softly. ``I've got to.
But I'll see you at the game, right?''

``Of course,'' said James, and knelt down in front of him. Harry met his
father's eyes, and was a little stunned at the amount of love he saw in
them. He knew that his father felt it, of course; James just wasn't as
demonstrative with him as he was with Connor. ``Harry, don't worry about
anything he says. I'm going to speak to Headmaster Dumbledore after the
match and see about getting you Re-Sorted myself.''

A lump of emotion rose into Harry's throat, and he couldn't speak. He
just hugged James, who looked as startled by the suddenness of the
gesture as Harry was, and then hurried away to put on the green robes.

They were not the reason that he was going out on the pitch, of course.
That reason had to do with a conversation in the woods a week earlier
and the wandless magic that tingled and sang beneath his skin now,
lodged in a few specific Charms, just waiting to be used.

\emph{Try to hurt my brother,} Harry challenged Quirrell and this
unknown traitor and whoever else might come to the game. \emph{Try to
hurt him now. I dare you.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

The whistle blew. The balls flew out of the circle at the center of the
pitch.

Harry rose from the ground the moment he saw the others rise, so that he
was one of a crowd, not pulling out recklessly ahead and alone, the way
that Connor had. He smiled at his brother, but he would have found it
hard not to smile.

He was in the air again.

He circled the pitch as the Slytherin team spread out around him,
dipping and ducking, heading for the Quaffle and the Bludgers
respectively. The Gryffindor fliers were streaks of fire that clustered
around the Slytherin team like diving falcons. Harry could see, from one
glance, that the Gryffindor Keeper and Captain, Oliver Wood, was
obviously a dedicated player, and the Gryffindor Chasers and Beaters
didn't look bad, either.

In a different place, at a different time, it might have mattered. Now,
it didn't.

Harry circled, high and steady, keeping an eye on the sides of the pitch
as well as the stands of watchers. Briefly he caught sight of his
parents, Sirius, and Remus, all sitting together and waving a banner
that Sirius had enchanted to glow with the Gryffindor colors. Harry
smiled.

Then he rolled over his broom as he heard the warning whistle of air,
and the Bludger passed just above his head. There was another whistle as
the ball turned back, but Harry was ready, and dived in a twisting
spiral that made the ball, too heavy to turn as fast as he did, lose
track of him and veer off into the crowd of fliers. Harry spun out of
his dive and watched to make sure the Bludger didn't hurt Connor. Of
course, it didn't; Connor got out of the way with an ease that made
anybody's chances of hitting him look laughable.

\emph{But they can't be, or they wouldn't have arranged to kill him
here,} Harry thought, as he twirled upright again. \emph{Where are they
going to come from? Where are they going to strike?}

``And Johnson takes the Quaffle and scores ten points for Gryffindor!''
announced the commentator, whom Harry felt sure was a Gryffindor, given
the gleeful tone in his voice. ``Meanwhile, it seems as though the
Slytherin Keeper was too busy trying to find his own arse with both
hands to notice---''

``\emph{Jordan},'' came McGonagall's prim voice.

Connor cut beneath Harry, his eyes trained forward, his neck craned as
he searched for the Snitch. Harry made another turn, and briefly caught
Snape's glare from the Slytherin stands.

He'd \emph{have} to pretend to look for the Snitch, then. There was no
help for it. He shook his head in brief irritation, and swung around in
a carefully coordinated maneuver that just happened to lead to both
Bludgers avoiding him, and colliding with a ringing \emph{smack.} They
darted off again, wobbling slightly and appearing dazed.

Harry reoriented himself in time to hear the Gryffindors shouting
themselves hoarse, and presumed another goal had been scored. He would
have known, and been far more relieved, if Connor had caught the Snitch
already. He made another tour of the pitch, varying his height, which
allowed him to look for the Snitch and any incidental nasty little traps
that Quirrell had left lying around.

``And the Gryffindor team---''

Harry abruptly jerked. A moment later, he felt the conscious counterpart
of the strange sensation that had assaulted him: the anti-Apparition
wards around the pitch had fallen.

The next instant, two figures in dark cloaks and white masks burst out
onto the pitch, coming from the direction of the Forbidden Forest, wands
in upraised hands that were already spitting curses. A dark purple hex
headed straight for Connor.

Harry's heartbeat tripled in pace, and his vision narrowed. He had
practiced for this. He had trained for this. And the time for his first
real battle with Death Eaters had finally come.

``\emph{Stupefy,}'' he said, using all his will and the word only, as he
had when he fought the troll.

The spell hit Connor, whose broomstick promptly tumbled out of the path
of the nasty purple hex. Harry cast \emph{Wingardium Leviosa} at him,
not allowing himself to think about what would have happened if Connor
had hit the ground before he could perform that spell, and then cast
\emph{Fumo.} Everyone was screaming, feeling for wands, trying to storm
out of the stands, but they would notice if Harry started fighting
without his wand, or fighting at all for that matter, if the pitch
remained clear. The rest of the Quidditch team members had fled---except
for that mad fellow Wood, who was hovering in front of his goal as if he
could protect it from curses.

The smoke spread out around the pitch, obscuring sight for everyone
except those who might use a \emph{Specularis}, which was the spell
Harry cast next. He could feel the steady burn and pull of his magic
fighting him, not used to being called on like this. But he had
practiced nonstop for the past week. Three wandless spells had dropped
him after the troll fight. That was not going to happen this time.

A weight jolted him from beneath---Connor's broomstick, bearing the
unconscious Connor on it. Harry grabbed his brother's arm and towed him
towards the ground, holding the Levitation Charm and the
\emph{Specularis} both with all his mind. The first kept his brother
from dropping like a stone, the second was the only way he could see,
and both were necessary to keep his brother alive.

Harry dropped Connor gently in the grass before the Quidditch stands,
and then kicked off. His heart was beating fast again, and he nearly
choked on the mixture of terror, rage, and battle-joy filling him.

\emph{Here I come.}

He extended the \emph{Specularis} before him, from a small clear window
into a narrow tunnel that cut through the smoke and afforded him further
sight, and soon enough he made out two flashes of dark and white on the
ground. One of them was firing off hexes randomly and wildly into the
air, but the other had a \emph{Specularis} of his own in front of him,
and he looked up and saw Harry coming.

The Death Eater laughed. The laughter was shrill, high-pitched,
mad---and a woman's.

Harry swallowed once. \emph{This is Bellatrix Lestrange.}

``Attacking us alone, little baby?'' she crooned at him as he curved
above the pair---he thought the other was probably her husband,
Rodolphus Lestrange---and then stopped, hovering so that he could see
them. ``You have a high opinion of your bravery, don't you?'' Then she
swung her wand.

``\emph{Protego}!'' Harry intoned.

``\emph{Crucio}!'' she cried in the same instant.

The Shield Charm formed itself before the blast of the Cruciatus could
reach him, but then Harry had to hold it against the sheer force of the
curse, rolling waves that flowed around his defenses and set his
broomstick spinning in midair. Harry hissed and clasped the broomstick
with his knees, rolling back upright. He wasn't afraid of falling in the
air, he never was, but that curse made him the closest thing to it.

He dived the moment he thought of the plan, dropping towards the ground
and screaming as though Bellatrix's curse had managed to fell him.
Bellatrix laughed in delight and ran forward.

Harry did not dare drop the Shield Charm, so his options were limited,
but he managed to call a divot of grass from the ground with
\emph{Wingardium Leviosa} and smash it into her hip. Bellatrix winced
and limped for a moment, and that meant that a hex from her husband hit
her instead of Harry. Bellatrix shook it off, turned to scream and
berate Rodolphus while Harry lifted steeply back into the air.

The smoke was already thinning. He didn't have much chance to defeat the
pair of them, not if he was going to do it in the way he planned. Harry
spun in a brief circle, thinking, and then stopped both his broom and
his thoughts.

\emph{New plan. Always use what's around you. Mum told me that once. In
a forest, it's branches, and on the Quidditch pitch, it's grass. But not
only grass\ldots{}}

This had to work. His strength was flagging already. He had practiced
\emph{Protego}, because he thought he might need it, and held it longer
than this, but not against such powerful spells. And both of the Death
Eaters had their wands out and were advancing on him now, and he did not
think that he could bear it much longer.

He reached out with all his strength and all his will, and grabbed for
something he could feel floating in the mist. Now he had to wait for it
to get there.

Bellatrix intoned another spell he didn't know, and Harry winced as the
Shield Charm briefly threatened to crumble under it. The mad Death Eater
cackled cheerfully and tried another, and another, and another, and then
one that must have been non-verbal, since Harry heard nothing before the
burn of blue flame lit the air. That one got through to him, a little.
He winced and cradled a scorched hand.

He couldn't fight them, not the normal way. He wasn't strong enough yet.
But though that was a bitter pill to swallow, at least he knew his
weaknesses now. If he survived this---and he \emph{would}, because he
had to protect Connor---then he knew what to practice with. Defensive
wandless magic had just been added to medical magic and spells to
effectively muffle noise. With this kind, though, he could practice on
his own. There was that to be said for it.

He drifted closer to the Lestranges, not letting them see how much he
hurt. The Shield Charm was faltering, but he had only a few moments more
to endure. He had to have only a few moments more. He could feel it
getting closer.

``What are you doing, little baby?'' Bellatrix asked, swishing her wand
back and forth, trailing sparks. ``Have you given up?''

``Waiting,'' Harry said, as calmly as he could.

``For wh---''

The Bludger took her in the side of the head, snapping her neck sideways
at an angle and flinging her to the ground. She was still alive, Harry
thought, when he noticed her breathing, and so was Rodolphus after the
Bludger hit him and knocked him out beside his wife. Good. He wanted
that. Let them get questioned, or go back to Azkaban, or, preferably,
both.

He let his will relax, and dropped the Bludger beside the Lestranges.
There was only one more thing he had to do.

\emph{Well, perhaps two more.}

He flew back to the stands where he had laid his brother, casting
another \emph{Fumo} on the way, so that the smoke thickened just as it
had begun to dissipate. He knew he had to be quick about it. The
professors and the other adults in the stands had been concerned with
getting the students to safety and away from the Death Eaters so far,
which meant ``off the Quidditch pitch,'' but that wouldn't least much
longer, even if wand magic had to struggle against wandless magic.

He grabbed Connor in his arms and skimmed back to the Death Eaters,
laying him gently down beside them and putting his right hand on the
Bludger, as though Connor had hammered it into their heads. Then he
glanced around the Pitch. It was a slim chance, but just in case---

A gleam of gold flashed past above him, and Harry snatched the Snitch
out of the air. Holding it tightly enough to almost damage the wings, he
put it into Connor's left hand and clasped his fingers around it.

Then he flew randomly, almost to the Slytherin stands, and dropped to
the ground as if he had collapsed from inhaling smoke. And he let it all
go: \emph{Fumo}, and \emph{Specularis}, and the sheer effort of
producing wandless magic.

Exhaustion came down on him like a waterfall. But he was awake long
enough to hear the shouts, and then the silence, and then the cheers.

They had found Connor. And he looked like an absolute hero.

Harry smiled, closed his eyes, and let his weariness take him.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Snape stepped carefully away from all the festivity, lowering his wand.
It appeared that the majority of the students were fine, and, in fact,
had been more injured in the stampede from the stands than by anything
that the Death Eaters had done. And, of course, now the crowd was
chattering about the Boy-Who-Lived as the hero of the hour---he'd not
only defeated two trained Dark wizards more than twice his age, he'd won
the Quidditch game while doing it!

Harry's lies depended on everyone being besotted by the resident hero,
Snape had told him. They were tissue-thin with the troll, really, and
tissue-thin here.

But because everyone \emph{wanted} to believe them, they were going to
believe them.

Snape smiled tightly. He had seen. He had looked. When everyone else was
screaming at the appearance of Death Eaters, his gaze had gone at once
to the two smallest figures on the pitch, one in scarlet robes, one in
green.

He knew Connor had been unconscious when the Smoke Charm spread its
obscuring arms over the pitch.

Snape had had enough of this. He knew the truth, now, and was not in a
mind to let a Potter brat hide behind lies. It was time to find
Dumbledore, and have a talk with the Headmaster about getting some
credit for a certain stubborn Slytherin who, apparently, \emph{still}
refused to believe that he belonged in Snape's House.

\emph{When, really,} Snape thought as he saw Albus's star-covered robes
and quickened his steps, \emph{he fits in} so \emph{remarkably well.
Will that not half-kill his father? Oh, I think it will.}

\chapter{Power United With Love}\label{chapter-11-power-united-with-love}

``You're quite sure that you don't want a sweet, Severus?''

``Yes, Headmaster.'' Snape had to fight to keep a scowl away. Even when
he heard what Snape wanted to talk to him about, Dumbledore had still
nodded and chuckled and never let the damn smile on his face fade for an
instant. He'd brought Snape straight to his office, which was something,
but now he was petting Fawkes, his phoenix, and not sitting down behind
the desk, where Snape thought he ought to be for a discussion of this
magnitude.

At last, moving without hurry, Dumbledore turned and dropped into his
seat. The first thing he did was pop a sweet into his mouth, and then
try to offer one to Snape, \emph{again.} At that point, Snape had had
enough.

``I know that the Potter brat in my House is the Boy-Who-Lived, Albus,''
he said.

Dumbledore blinked---Snape had only told him that he wanted to talk
about Harry---but said, ``I am astonished that you think so, Severus, in
the face of all available evidence. Will you tell me why you think so?''

``It is \emph{obvious},'' said Snape, becoming truly annoyed. ``He is far
too powerful for a wizard that young. He saved his brother from the
troll, and again today, from the Death Eaters. He performs
\emph{wandless magic}, Albus, including, I'm quite sure, wandless Shield
Charms. I believe that he may well be the strongest wizard to enter this
school since---the Dark Lord.'' Habit, superstition, old changed
loyalties, all kept him from calling the Dark Lord by name that often.

``Yes, I know all about young Harry,'' said Dumbledore, and gave him an
infuriating smile as he tapped a kettle set on a table behind him, which
promptly began to whistle. ``I know that he is doing precisely what he
is meant to do. Tea, Severus?''

For a long moment, Snape couldn't speak---first because of his
astonishment, and then because he had to remind himself that reformed
Death Eaters did \emph{not} stand up and attempt to kill the Headmasters
who'd saved them from Azkaban.

\emph{Attempt to kill,} one of his thoughts hissed at him, probably
originating in his Slytherin survival instinct. \emph{The spell wouldn't
land, and you know it. This is Dumbledore.}

Snape nodded at nothing, calmed down, and managed to say in a voice with
only a thin veneer of ice rather than outrage, ``You knew?''

Dumbledore glanced up at him, eyes mild. ``Of course, Severus. From the
moment young Harry walked into the Great Hall, I've had to strengthen
the shields that protect me against seeing other wizards' magic. It
grows worse when he is angry, which so far has always coincided with
something that he believes puts his brother in danger. He blazed today,
and I know that he was the one, not his brother, who defeated the Death
Eaters.'' He shook his head, while pouring tea from the kettle into two
small cups. ``I know what their presence means here, and I am shocked
and saddened. I had not realized that matters had gone this far.''

For a moment, Snape let himself be distracted enough to think of asking
after that, but he pulled his thoughts back to the reason he'd come
here. The Headmaster had been a Gryffindor, not a Slytherin, but he
manipulated as well as one. And Snape was determined that this time,
\emph{this} time, if no other, he would not be manipulating the Head of
Slytherin House away from what was truly important.

``How can you know this,'' he demanded, ``and yet claim that Connor
Potter is the Boy-Who-Lived? I have felt the boy's ability. He could do
well with training---'' \emph{those} words stung him to say ``---but I
could say that about any of the first-year imbeciles who come through
our doors. What \emph{about} Harry? Why isn't he being celebrated,
hailed as the hero of the wizarding world, the boy who defeated
Voldemort?'' He was glad that he managed to say the name this time. He
had calmed. He would do this, would stand aloof from the lashing anger
that wanted to fill him whenever he thought of the name \emph{Potter} or
the stubborn way that Harry stuck to the shadows. ``I am quite sure that
he is.''

``He isn't, Severus,'' said Dumbledore cheerfully, and then handed him a
cup of tea that it was either take or look ridiculous refusing. Snape
took it, but held it in such a manner that he hoped conveyed his deep
disapproval of the whole notion. Dumbledore went on drinking his own tea
with every sign of enjoyment, not speaking again until he finished the
cup. Then he smiled. ``It is true that Harry is a powerful wizard, but
that does not make him the Boy-Who-Lived.''

``Why \emph{not}?'' Snape said, and so much for not getting angry. He was
fighting not to crack the cup in two.

``Because,'' said Dumbledore, ``of factors that the Order of the Phoenix
has been aware of since before Harry and Connor were born. We are lucky
enough to have a careful, clear set of signs to guide us. We have read
them all with great precision, and reasoned out what they must mean. We
are convinced that Connor is the Boy-Who-Lived, and we would not have
announced him to be so after Voldemort's attack if we were not so
convinced.'' He politely ignored Snape's flinch. ``Rest assured, we know
what we are doing.''

``What are these `signs?'\,'' Snape snapped, putting the teacup down on
the Headmaster's desk. ``I want to know what they are.''

Dumbledore looked uneasy for the first time---uneasy and slightly sad.
``Severus---''

Snape stood. ``If you do not trust me, Albus, then you ought to have
said so,'' he said, feeling his voice fall into the quiet registers it
did when he was truly angry. ``Of course, a Death Eater can never be
fully trusted, can he? Even one who turned his back on the Dark Lord and
all he stood for. Even one who risked his life for you as a spy, for a
year and more. Even one who is now Head of the House into which one of
these precious Potter children has been Sorted.'' He turned towards the
door. ``Well, you need not be troubled with my presence any longer.
Goodbye, Albus. You'll have my resignation on your desk in the
morning.''

``It was not entirely my decision, Severus,'' Dumbledore told his back.
Snape halted, and didn't turn around. It remained to be seen if his ploy
would win more out of the Headmaster than this. ``Not every member of
the Order was aware of it, either. I was, and so were James and Lily
Potter, and a few of their friends. It was James and Lily who asked that
the news not be spread further. They wished to keep it a secret because
of the danger that it might mean to their sons.''

``I am Harry Potter's Head of House,'' Snape said, and turned around
again. ``I am the one responsible for training him, protecting him,
guiding him through the wizarding world during his time at Hogwarts.''

``Minerva does not know,'' Dumbledore said, frowning at him.

Once, Snape would have quailed at that frown. He did not now. He
\emph{knew} he was right, knew it as surely as wandless magic exhausted
wizards five times Harry's age. He folded his arms across his chest.

``I also owe a Life Debt to James Bloody Potter,'' he snarled at
Dumbledore, ``and will be protecting Connor Potter. \emph{If}, that is, I
know why I should be defending him at all costs, and not his brother,
instead.''

Dumbledore let out a long, slow sigh, as if he were feeling his age at
last. ``Sit down, then, Severus,'' he said, standing. ``I suppose I
should have known this day would come. So long as the boys remained at
Godric's Hollow, no one else needed to know. But in Hogwarts, as you so
amply point out, there are others who will, perhaps, pause and wonder
about what seems a strange state of affairs.'' He glanced pointedly at
Snape. ``Perhaps someone else has already.''

Snape felt his face change briefly, and sighed when Dumbledore looked at
him and waited. ``Draco Malfoy,'' he said unwillingly. ``He has not made
the connection with Harry being the Boy-Who-Lived, I am certain of it,
but he can feel the boy's power.'' He tensed his shoulders, ready to
dive forward and defend one of his charges. ``But he is
also---\emph{interested} in Harry, perhaps fascinated, and would be
extremely hard to get rid of.''

Dumbledore nodded. ``I suppose I should have realized something like
this would happen when Harry was Sorted into Slytherin,'' he murmured,
and Snape had to conceal his shock at the Headmaster admitting two
mistakes in two minutes. ``That was the one thing we did not foresee,
when we made the decisions that we did. We were sure he would go to
Gryffindor.''

Snape watched as Dumbledore walked over to a small chest that occupied
the back of his office, under an array of tilting, spinning silver
instruments and several dozing portraits of Headmasters past. He
thought, but did not say, \emph{You are a fool, Albus. The boy is a
Slytherin. What else have you missed? Should I be inclined to distrust
you even more than I already do?}

But it was not true to say that he distrusted Dumbledore. He had faith
in him to do what he thought was best for Hogwarts, and there was
always, always the debt of gratitude, that Dumbledore had listened to
him and believed him when Snape turned his back on the Death Eaters. But
he was wary of him, too. The Headmaster favored his Gryffindors, loved
his Gryffindors. He was likely to make mistakes in their favor and
against Slytherins.

And, too, there was the tiny seed of anger, long-buried but not
forgotten, that asked: \emph{Why didn't you expel James Bloody Potter
and his friends for endangering my life? When I could have become a
werewolf or died, why were their chances to stay in school more
important?}

He said nothing about that, though, as he watched Dumbledore straighten
up with a small Pensieve filled to the brim with silvery liquid.
Dumbledore carried it to the desk and nodded Snape to it with a
strangely solemn air.

Snape bent over the Pensieve, dipped his head below the surface of
Dumbledore's collected thoughts, and vanished into the memory.

Dumbledore waited in a small, comfortable room, whistling tunelessly to
himself and studying the walls as though he admired the dreadful artwork
hung on them. Now and then he lifted his wand and cast a ring of colored
smoke into the air, watching and chuckling as it changed through several
shapes. When one faded, he would whistle, study the walls, and then cast
another.

Snape entertained himself, if one could call it that, by trying to guess
where the room was. The walls were wooden, which made him think it was
not part of Hogwarts, but it had no windows to let him make sure.

At last, a knock sounded, and Dumbledore turned and called, ``Enter.''

A woman stepped through the door, blinking at the light of the torches
that gripped the walls. Snape felt his mouth curl in a sneer. The woman
was Sybill Trelawney, Hogwarts's useless excuse for a Divination
teacher. She had her shawl wrapped around her like a snail's shell, and
she didn't make much faster progress than a snail would towards
Dumbledore, either.

``Headmaster?'' she asked hesitantly. ``I don't understand. I thought
you had offered me the Divination job, that I was now secured as
Professor?'' She spoke in a meek and humble voice Snape had never heard
before. He thought he rather preferred it over her usual manner.

``You are, Sybill, never fear,'' Dumbledore said, smiling at her.
``However, I called you here because I did not hear the whole of the
prophecy that you recited to me that night in the Hog's Head. There was
a---bit of a commotion, and I am afraid that I missed the rest. Will you
please say it again?''

Snape stiffened. \emph{He} had been the commotion, since he had
overheard the first part of the so-called prophecy that Trelawney had
recited. Then someone had seen his Dark Mark, screamed, and gotten him
thrown out. He had scurried away to the Dark Lord and reported all he
could, which was a measly few lines. It was a surprise that Dumbledore
had not heard the rest, either.

Trelawney blinked at him. ``What proph---''

Then her eyes rolled back in her head, and she began to speak in a far
more powerful voice than Snape had ever heard from her, even on that
night when she had begun to speak the prophecy.

``\emph{The one with the power to vanquish the Dark Lord
approaches\ldots{} Born to those who have thrice defied him, born as the
seventh month dies\ldots{}}''

That was all Snape himself had heard. And Dumbledore was nodding along
in encouragement, though Trelawney could see nothing of it. Snape leaned
forward to hear the rest.

``\emph{He is the younger of two, and he shall have the power the Dark
Lord knows not\ldots{}For the elder is power, but the younger is power
united with love\ldots{}O guard him, O shield him, for the darkness
through which he passes otherwise is vicious and hideous, and love has
but a scant chance of surviving\ldots{}The elder will stand at his right
shoulder, loving him, but the younger will love the whole of the
wizarding world\ldots{}The Dark Lord will mark him as his equal, and in
so doing mark his heart\ldots{} The one with the power to vanquish the
Dark Lord approaches, born as the seventh month dies\ldots{}}''

The prophecy ended. Snape didn't wait to hear the stammering sounds
Trelawney would no doubt make; most true Seers did not remember their
own prophecies afterwards. He pulled his head out of the memory.

He was shaking, both from the roused memories and from the power intoned
in the words. He sat down in his chair, and said nothing as Dumbledore
covered the Pensieve and carefully put it back in its chest. Fawkes,
watching with his head on one side, suddenly let out a rich trill.
Dumbledore paused to stroke the bird. Snape noticed that his hands were
trembling.

Snape whispered, ``And so that prophecy fits the Potter twins?'' He had
never known, never \emph{suspected}. The Dark Lord normally had as much
use for Divination as he had for kindness. And he had arranged matters
almost alone, with the help of Peter Pettigrew, the Potters'
Secret-Keeper now rotting in Azkaban, and Bellatrix Lestrange, who had
tortured the Longbottoms into insanity. Snape had thought he had
attacked the Potters for their expeditions against him in the past, not
because he truly believed an infant could be a threat to him.

``It does,'' said Dumbledore, moving forward and sitting down behind his
desk again. ``They were born at the end of July---as was Neville
Longbottom, incidentally, but they were the only wizarding twins born
`to parents who had thrice defied him' then. Harry is the elder
twin---''

``You know that for certain?''

``Of course,'' said a cool voice behind him. ``I should know it. I was
there.''

Snape turned sharply. Lily Potter stood in the doorway, glaring at him
with eyes deeper and sharper than her son's. Snape wondered what to say,
until he saw James Potter behind her, face red with fury.

\emph{Take refuge in hatred, always,} Snape advised himself, and
smirked. ``Come to hear the unexpected news of your sons, Potter?'' he
taunted. ``Come to hear that the Slytherin is the one who shall save the
wizarding world?''

``\emph{Severus.}''

Snape flinched and glanced over his shoulder. Dumbledore had stood and
was scowling at him. Snape slunk back into his seat, and watched in
sullen resentment as the Potters took two more chairs beside him.

``Our apologies, Headmaster,'' Lily said, ignoring Snape entirely and
not sounding sorry at all. ``We came to see you about something else
concerning our boys, but when we heard what was being discussed, we felt
we had to enter.''

``Quite all right, my dear.'' Dumbledore beamed at her, and held out an
Acid Pop, which she accepted. ``I think that Severus does deserve to
know, since he's Harry's Head of House now.''

``Not for much longer,'' James Potter muttered.

Snape looked sideways to meet a glare of equal intensity. He sneered at
it, and turned back to the Headmaster.

``So Harry is the elder twin, Connor the younger,'' he said.

``By almost fifteen minutes,'' Lily added.

Dumbledore nodded. ``And Harry is more powerful, there is no doubt about
that. \emph{The elder is power\ldots{}} When we came to Godric's Hollow
that Halloween night, to find Voldemort defeated and Peter fled, we
could feel Harry's magic raging about him like a windstorm. We believe
that the presence of so much other power in the room---Voldemort's
magic, Connor's essential innocence and purity---set Harry's free,
earlier than it should have been loosed.'' Dumbledore's eyes darkened.
``So much power is unnatural in a child, Severus.''

He did not have to say that Voldemort had been the same. Snape could
\emph{feel} him thinking it.

He wanted to shake the Headmaster. He wanted to shout, \emph{Not every
Slytherin is the Dark Lord. Stop reflecting us with a mirror of your own
creation!}

Instead, he raised one eyebrow and said, ``It seems clear to \emph{me}
that that makes him the Boy-Who-Lived.''

``Not so,'' Dumbledore said. ``Recall what else the prophecy speaks of,
Severus. \emph{The power the Dark Lord knows not.} Voldemort knows all
about magical power. He is versed in the darkest of the Dark Arts, and
much other knowledge that no child of eleven could have hoped to
acquire, much less a baby. But love---ah, that he does not know. And
Connor will be power, well-trained power by the end, united with love.
He loves effortlessly, easily.''

Snape ground his teeth. ``And how can you be so sure that love is this
unknown power?''

``You forget,'' Dumbledore said gently. ``You are talking to the man who
defeated the last Dark Lord, Severus.''

Snape opened his mouth, then snapped it shut. It was true; he had
forgotten. He had known Dumbledore as Headmaster for so long that it
sometimes made him forget that he had done other things, such as
defeating Grindelwald.

``True,'' he murmured. ``My apologies, Headmaster. Continue.''

``It was my love of the wizarding world that let me defeat
Grindelwald,'' said Dumbledore, and closed his eyes with a sigh.
``Seeing him standing there, knowing he would poison everything we are
if I did not destroy him---that was what made my hand move as it did.
But I was an adult, Severus, and had had long years to gain in
experience, wisdom, and love. Connor and Harry are only children. We
cannot trust to sheer power, however great. We must trust to the one who
loves more. And that is Connor. Harry loves and cares only for his
brother.''

Snape watched Lily flush a bit from the corner of his eye, and wondered,
\emph{How much of that was your doing?} But he said aloud, ``And the
part about marking as his equal?''

``Connor's scar,'' said Dumbledore. ``\emph{And in so doing mark his
heart.} Connor's scar is in the shape of a heart.''

``Harry bears a lightning bolt,'' said Snape, determined to pry as far
as he could, because he could not believe that everything was really
this neat.

``Caused by a bit of falling roof the night of the attack,'' said
Dumbledore, shaking his head.

``You cannot be \emph{certain} of that,'' said Snape. He would press this
until it dried, he decided. He had squeezed blood from harder stones.
And the chance at a Slytherin hero who could do what the boy had done
today, in defense of someone else, was closer than it had ever been.

``No,'' Dumbledore admitted. ``But the wording of the prophecy, and the
presence of fallen roof close by Harry's crib, makes it near-certain.
Alas, only two people could tell us the truth about that night, and one
of them was lying dead of a reflected \emph{Avada Kedavra}.'' He smiled,
as if the mere mention of the Potter brat's triumph was a matter for
wonder.

``Who is the second?'' Snape said, leaning forward.

``Peter,'' said James, with an even deeper loathing in his voice than he
reserved for Snape.

``Peter,'' Dumbledore agreed, with a long sigh, and shadows in his eyes.
``The Aurors caught him the next day. There was no need for a trial, or
Veritaserum. When they asked him if he had betrayed the Potters'
location to Voldemort and created the rumor that their sons had already
been taken, he admitted that he had. He went to Azkaban laughing, as if
he were already mad. I have visited him several times since then,
attempting to confirm what we know already about the attack, but he
grows progressively more insane. I fear that we will get nothing useful
out of him.''

Snape sat back in his chair, stymied. He could not think of any other
target to focus his questions on. He turned his memory of the prophecy
over and over in his mind, but could think of nothing there. If nothing
else, the fact that Connor had been born after Harry seemed to seal
their respective fates.

``Now,'' said James Potter, leaning forward in his chair, ``we came to
speak to you about Harry, too, Headmaster.'' He sent Snape a distrustful
glance. ``I am doubly glad that we did, now that I hear about
\emph{Severus's} worrying obsession with him. We would like him
Re-Sorted into Gryffindor.''

\emph{And there is a new target for my questions.}

``You will permit this farce, Headmaster?'' Snape drawled, turning his
eyes on Dumbledore. ``Then I might know well and for all what House you
really favor, and which you do not.''

He watched in amusement as Dumbledore's face struggled between several
expressions. In the end, Dumbledore shook his head. ``We must trust the
Sorting Hat,'' he explained to a visibly sagging James. ``It put Harry
in Slytherin for a reason, I am sure. Perhaps it is to enable him to
learn even stricter control of his magic, which in the end he will put
to use protecting Connor.''

\emph{This again,} Snape thought, seething behind his outward mask.
\emph{I am sure that Harry could kill the Dark Lord in front of you,
Dumbledore, and still you would insist that his brother had done it with
this mysterious power of `love.' I despise your romanticism. It is not
the way to win a war.}

``But the Hat may have made a mistake---'' James began.

Lily took his arm, and he hushed. That disappointed Snape. He would have
looked forward to more bluster that he could attack and refute. But Lily
turned towards the Headmaster and said, ``Why was our son in danger
today, Headmaster? Who were those Death Eaters?''

``The Lestranges,'' said Dumbledore quietly, his face dropping at once
into grave, worried lines. ``The Minister has spoken with me. Someone
claiming to be acting with my authority---and with impeccable
credentials, apparently---told him that the Lestranges were to be
removed from Azkaban and put in a more secure location. They were
released, and then they traveled here. The same person, likely, dropped
the anti-Apparition wards around the Quidditch pitch. There seems little
reason to doubt that the Lestranges planned to Apparate away when they
were done.'' He closed his eyes. ``We have a traitor in the Order of the
Phoenix.''

Lily sagged back in her seat, looking ashen. James Potter, for once, had
no words to say.

Snape found himself astonished, and then frightened, briefly, as the
sense of the Headmaster's words came home, and then angrier than ever.
The anger was combined with a fierce pride, which was a most peculiar
mix.

\emph{The Lestranges! Top Aurors fell before Bellatrix's wand. They
tortured the Longbottoms into insanity. I cannot count how many
atrocities they were responsible for during my time in the Dark Lord's
Inner Circle. And the boy defeated them with a few wandless Charms and a
Bludger!}

Snape changed his mind in that moment. He could not insist that Harry
was the Boy-Who-Lived. Dumbledore would not believe him, and neither
would the Potters. They had already made up their minds. For all Snape
knew, they might even have sought to ``tame'' Harry's power by insisting
that he focus on protecting his brother. It seemed likely.

That did not mean that he need sit idle and do nothing.

The Order---with a traitor in the middle of it, how wonderful for
everyone involved---could have their Boy-Who-Lived. He would work with
Harry. He would insure that the bloody stubborn boy learned to look
beyond his brother's skin, and out for his own, and then for other
Slytherins'. And then, if they had the time for it, he might urge Harry
to think of the rest of the wizarding world, including the father who
would be torn apart by Snape having such control of one of his sons.

And if he chose to expunge his debt to James Potter in guarding Harry,
who was to gainsay him?

He sat through their discussion of the traitor, uninterested; as he had
suspected, no one had any idea who it was. Dumbledore trusted too many
people, and Lily and James had been too isolated from the world in
Godric's Hollow to have any idea of current political realities.

Snape stood when he could safely excuse himself, and made his way back
to the dungeons, glad that he ran into no one to whom he would have to
explain the pleased smirk curling his mouth.

There was no point pushing for credit right now, not with the Headmaster
dead-set against granting the boy any notice at all, even half-thinking
that he might turn into another Voldemort if he were praised for his
power. Snape would work in secret, and then push Harry into the light
when matters were already so far along that no one else could stop them.

First, of course, he needed to have a little talk with Harry. Snape did
not anticipate that being easy. But since he had the perfect weapon in
mind, he did not worry overmuch about it.

Halfway to the dungeons, he was horrified to realize that he was almost
humming under his breath, and made himself stop it.

\chapter{Interlude: Correspondence}\label{chapter-12-interlude-correspondence}

\emph{September 1st, 1991}

\noindent Dear Father:

I am safely at Hogwarts, and have been Sorted into Slytherin. As if
there were any doubt! You and Mother raised me beautifully, and I have
every expectation of being able to fulfill the role the Malfoys have
always held in Slytherin---that of its leaders---with exceptional
elegance and grace.

But, Father, there is something unusual: a Potter in Slytherin! No, not
the Boy-Who-Lived; I met him, and he's a stuck-up Gryffindor. He has a
twin brother, though, did you know? Harry. I think he's older, but
that's just because he {looks} older. He has green eyes, and a lightning
bolt scar, and an odd aura of power. I knew he would be in Slytherin
from the first time I saw him on the train, because his magic made my
head ache. I shielded like you taught me, though, and soon all was well
again. The expression on Harry's face when the Hat put him in Slytherin
was funny, though. It was as if he didn't expect it!

Slytherin is everything that you said it would be. I feel comfortable
here already, Father, about to assume my natural destiny of triumphing
over the commoners who might think to lead in my place, or to doubt me.

Your loving son,

\emph{Draco Malfoy.}

\emph{}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\emph{September 2nd, 1991}

\noindent Dear Father:

I am using a school owl to send this to you, but only because you
haven't sent Imperius back yet. I promise you that in no way do I think
a common Hogwarts school owl is worthy of a Malfoy.

Classes were wonderful today. I know that I'm going to enjoy
Transfiguration, and I'm going to enjoy it in spite of McGonagall, who
is an old bat just like you said. At least she doesn't dare be unfair to
me, because she knows who I am, and none of her precious Gryffindors are
in the class for her to be unfair about. Blaise Zabini said something
most amusing about her as we were leaving class, however, and got
assigned extra homework as a result. I shall endeavor to guard my tongue
around her.

Charms class is going to be easy, I know it. Professor Flitwick looks so
funny. Is it true that he has goblin blood, dear Father?

Harry Potter sat next to me in every class. He is quiet and brooding and
looks everywhere when we're in the halls for that twin of his. I think
he might believe the Boy-Who-Lived can't hold off a simple speck of
dust, the way he acts. At least I stopped his nonsense of wanting to go
over and speak to his brother at lunch by pointing out that his brother
had come in late and we needed to hurry to get to Charms.

That reminds me, Father: Harry seems to be unaware of his own power. Do
you know of any rumors that the Potters have a son that powerful? And
could Connor Potter, the Gryffindor prat, really be so powerful that I
simply can't feel him? {He} doesn't make my head ache.

I have to hurry through the last of this letter, as we have Astronomy
class in a few moments. I love you, Father, and hope both you and Mother
are well.

Your obedient son,

\emph{Draco Malfoy.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{September 6th, 1991}

\noindent Dear Father:

Yes, of course, I'm sorry. I won't use such language about a Hogwarts
professor again, even in a private letter. You're right that it wouldn't
look very good if anyone took it into his head to read our mail, or even
if Imperius was carrying it and got intercepted. Are those Aurors still
watching the Manor?

The old {cat} McGonagall disapproves of me. I heard her talking about me
in the corridors earlier. She was saying something about ``that Malfoy
boy,'' and stopped and frowned when she saw me. She was talking to
Professor Sprout. I have no idea why. I haven't even hexed a Hufflepuff
yet. I put my head up and walked past them like the paragon of good
breeding that I am. You would have been proud of me, Father. I remember
all the lessons you taught me about courtesy, and all Mother's lessons
about proper posture.

Potions was---two classes, really. Professor Snape really is a brilliant
teacher, just as you said. And he takes points away from Gryffindor when
they show just why they're the House of Idiots, and he made a particular
point of humiliating the Boy-Who-Lived.

And then Harry was tiresome. He's acted {all week} as if his skin was
crawling because he couldn't see his twin, and then he actually
interfered with our boil cure potion just to keep his brother from
getting in trouble. Snape assigned him detention, of course, since he
wouldn't take points from Slytherin. And I kept asking him why he did
it, and he refused to answer me.

Can you believe that, Father? A Potter {refusing} to answer a Malfoy?

I like Harry, but he makes my head ache and my teeth ache from grinding
them. Not that I let him catch me grinding them, of course. Such an
action would not be as you have trained me to do. I only wish he were
not so tiresome.

Your elegant son,

\emph{Draco Malfoy.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{September 12th, 1991}

\noindent Dearest Father:

Harry Potter is the most tiresome wizard {in Hogwarts}!

Harry has been consistently refusing to admit that he belongs in
Slytherin, instead of in pompous, self-absorbed, lying Gryffindor. With
my usual cleverness, which of course is entirely a product of your
training, I had thought of a plan to make him admit he \emph{was}
Slytherin, and better than his brother in some way.

We had flying lessons today, and Neville Longbottom---how the mighty
pureblood lines have fallen!---humiliated himself, causing Madam Hooch
to briefly leave us alone. I took up Longbottom's Remembrall, a gift
from his grandmother, that evil woman with a vulture on her head, and
then challenged Harry to catch it from several dozen feet in the air. He
succeeded brilliantly, as I knew he would. He's a Slytherin! That should
be all the proof of his House that anyone needs.

Then I took him to Snape's office, and told him what had happened, and
he agreed that Harry should be Slytherin Seeker.

And Harry {refused}.

No one {refuses} Professor Snape, except maybe Dumbledore, and I suppose
the Dark Lord. {But he refused!}

And no one {refuses} a Malfoy, but he did that, too!

I spoke with Professor Snape, and we both agreed that Harry needs to be
made to acknowledge that he's a Slytherin. We will come up with a
cunning plan, and he won't have any choice but to listen to us. But it
is so tiresome, having to do this in the first place. Were it not for
the fact that Professor Snape and a Malfoy together could not be wrong,
I would be inclined to think that Harry is right, that he does in fact
belong in Gryffindor with his prat of a brother.

Your graceful son,

\emph{Draco Malfoy.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{October 1st, 1991}

\noindent Dearest Father:

How hard is wandless magic? Could I learn to do it? Only Harry knows how
to do it, I'm certain of it, and loads of other powerful spells. I've
tried to get him to show me, but he does so with great reluctance. And
he sneaks out of the House at night to go practice spells somewhere.

Harry Potter is very tiresome.

Your grateful son,

\emph{Draco Malfoy.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{October 7th, 1991}

\noindent Dear Father:

Ah, of course. I suspected that wandless magic would be difficult, but
not impossible for a Malfoy. I am glad and pleased that you wish to
instruct me, and will wait until the Christmas holidays at home to
practice, with your supervision.

Classes proceed apace. I'm top of my class in Charms, and also very good
at Transfiguration. In History of Magic, the main difficulty is keeping
awake, but I have done several very good essays on the goblin
rebellions. It is difficult to learn from Professor Quirrell, since he
is so weak that my every instinct screams at me to despise him, but of
course I grit my teeth (silently) and do so, keeping in mind your
dictum: {No knowledge is ever a waste}

Our Astronomy classes leave me tired the next morning, but of course I
make sure not to yawn where anyone can see. I'm a natural at flying, but
then, your instruction and Mother's have seen to that; thank you.

Herbology seems the most useless class to me, but then, that may be only
because it's such a Hufflepuff subject, and Neville Longbottom has the
nerve to be {good} at it. Still, perhaps I will learn enough to tend the
gardens in the Manor over the holidays.

Potions is my most frustrating class, though I am making top marks.
Harry Potter is the reason for that frustration. There was never a
wizard more determined to let others take the credit for his actions, or
to appear ordinary while he was causing headaches for wizards who were
minding their own business, thank you. He never answers a question with
anything more than the absolute basic, required information. He always
makes it seem as if I have done all our combined Potions work. I've read
his essays, and they are not dreadful, or brilliant; they are absolutely
average. He sometimes gets detention, and luckily he hasn't actually
tried to spare his twin that much of Snape's attention since the first
day of class, but that's normal, too.

He has the nerve to walk about pretending to be {normal}

Tell me, Father, have you known any powerful wizards who have done so?

At least he can't spend that much time with his brother or those other
Gryffindor prats now. I've seen to that.

Your refined son,

\emph{Draco Malfoy.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{October 12th, 1991}

\noindent Dear Father:

It has been a month since I first suggested the Quidditch team to Harry.
I tried it again tonight.

He gave me a flat stare. I persisted, because of course no Malfoy would
give up after the first try.

Then he intoned a {Silencio} at me and left me that way for the rest of
the evening. Gregory and Vince both tried the counterspell and could not
lift it. Have you ever heard of such an outrage?

He released me at nightfall, and we had a shouting match. At least, I
tried to have a shouting match. Harry had a shower and went to bed.

He is {most} {tiresome}.

Your calm son,

\emph{Draco Malfoy.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{November 1st, 1991}

\noindent Dear Father:

Harry is being exasperating. And stupid. And risking his life where he
doesn't need to, and then refusing to even take credit for it, which
would be the only reason for such a thing. And he gave me a {headache}.

A troll broke into the school, and the Professors quite sensibly decided
to take everyone back to the common rooms. However, Harry, because he is
stupid, noticed his brother running off to find a Mudblood girl he'd
insulted earlier in the day---because the Boy-Who-Lived is stupid like
that, too---and followed him. And, well, I had to follow him, because
what in Merlin's name did he think he was doing?

We found the troll in a girls' loo. It had cornered the Mudblood girl,
and Harry's brother and the horrible Weasley who is the same age as he
is were trying to fell the troll by using {Wingardium Leviosa }on its
club. It failed, of course, because they are Gryffindors, and therefore
idiots. Then the troll injured them.

Father, Harry used {wandless} {magic} to fell the troll. Three spells,
all right in a row: {Incendio}, {Wingardium Leviosa}, and {Finite
Incantatem}. He did it as if it were no great effort at all, though he
was sick with spell exhaustion afterwards.

I do not want to get in Harry's way when he's angry. He frightens me. I
think he would die to protect his brother.

And then Harry lied when that old cat McGonagall came on the scene, and
claimed that he had followed the troll looking for glory, and Connor
Potter, the Brat-Who-Lived, the bloody Prince of Gryffindor, was the one
who'd done the magic. Unconscious, no less!

I had a fierce headache by that time, and followed Professor Snape to
the dungeons for a headache potion. He has said, and I agree, that it's
no use trying to force Harry to act with direct intervention. We must
try to coax him subtly.

But I have never been so angry with him. Doesn't he know that he could
have been {killed}?

Your angry, but rightfully so, son,

\emph{Draco Malfoy.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{November 2nd, 1991}

\noindent Dear Father:

Ha-ha! Harry is on the Slytherin Quidditch team now! We saw his brother
flying, and, of course, McGonagall didn't give him detention, but put
him on the Gryffindor team. That bloody Potter gets everything he wants
just handed to him.

And then Potter grabbed Harry's arm and took him to Professor Snape, and
told him that Harry should get to fly because he did. Sometimes a
Gryffindor sense of fair play comes in handy.

Harry will fly on Saturday, and I am sure that he will win. Can you come
to the game? I would like it if you could watch him play.

Your excited son,

\emph{Draco Malfoy.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{November 10th, 1991}

\noindent Father:

I am so angry that I am shaking. There was a Death Eater attack at the
Quidditch game. Rumors in Slytherin say it was the Lestranges. And Harry
defeated them with his wandless spells and a Bludger. I think I know now
why he's been creeping back into our rooms so late at night, though
really, he hasn't disturbed me that much; I sleep so remarkably deeply
that I never hear him go.

And then he let his brother take the credit for it! {Again}! He even put
the Snitch in his brother's hand, which I think is unfair. At the very
least, he could have insured that Slytherin won. No one would have cared
if he had carried the Quaffle home a few times, and then carried off the
Snitch. Instead, Harry is in the hospital wing with spell exhaustion,
and Connor Potter's name is feted all over the school.

I am beginning to think that Harry needs a good talking-to, from someone
who isn't me (whom he disregards) or Professor Snape (whom he distrusts
because Professor Snape hates his father). I have thought of a
remarkable solution, which I present to you with cautious hope. Will you
permit me to bring Harry home with me to the Manor over the Christmas
holidays, so that he may see what true Slytherins should behave like?

Your expectant son,

\emph{Draco Malfoy.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{November 11th, 1991}

\noindent Dear my son:

Yes, indeed, if you can convince this boy whom you are so fascinated
with to come to the Manor with you over Christmas, do so. I should like
to see what he is capable of.

Yours in Merlin's name,

\emph{Lucius Malfoy.}


\chapter{Three Uncomfortable Conversations}\label{chapter-13-three-uncomfortable-conversations}

Harry put a hand to his head and sagged against the wall. He'd thought
it was ridiculous for Madam Pomfrey to insist that he stay in the
hospital wing for a full \emph{week} because of spell exhaustion (which
she thought was an unusual and persistent case of smoke inhalation), but
now he wondered if he really should have left so early. His head pounded
in regular time with his heartbeat, and a dizzy, eddying light clouded
his eyes.

He blinked when he realized that at least some of that light came from
spells shining along the corridors, spells to calm tempers and damp
fires and make the torchlight just the right color. Had he been able to
see them before the Quidditch match? He didn't think so, but of course,
he hadn't been down the corridor to the hospital wing that often.

``Harry! If you'd waited, I would have walked you back to the
dungeons.''

Harry glanced up. Connor was striding towards him, with no one
accompanying him for once. Harry smiled, then wondered how his brother
had managed to get away from all those people who would surely want to
exclaim over him and shake his hand for saving the day and grabbing the
game for Gryffindor while he was at it.

Then he took in his brother's narrowed eyes and slightly tilted head,
and felt a queasiness that had nothing to do with performing too many
wandless charms.

Connor stopped in front of him, and squinted at him. Harry chose to say
nothing, hoping that looking pathetic would be enough to make his twin
forget whatever was on his mind.

It didn't work, of course. Connor rarely got his teeth into anything
long enough to distract himself from Quidditch, but when he did, he
didn't let \emph{go}, either. Sometimes Harry thought that Sirius should
have been his godfather, instead of Remus Lupin. Sirius was the exact
same way with a problem, worrying and picking away at it until he'd
worried either himself or the problem to death.

``Look, Harry,'' Connor began at last. He chewed his lip then, as if his
courage failed him when it came to the big moment. Harry, his stomach
definitely churning now, cast a glance down the corridor, longing for
Draco to appear and call Connor a blood traitor, or Ron to appear and
call him a Slytherin.

Neither happened, and his glance seemed to make up Connor's mind for
him. Connor drew a deep breath and leaned in closer.

``I'm not stupid, Harry,'' he said. ``I know that you won that game and
defeated the Lestranges. I don't remember anything past the point when
they came onto the field, and then I woke up and people were
congratulating me for two victories I hadn't earned. And I'm starting to
wonder about the troll, too. Awfully convenient, wasn't it, that I just
happened to collapse unconscious before the spell blast that supposedly
felled the troll?''

\emph{Shit. Shit shit shit.}

Harry sighed slowly. Their mother would be so disappointed in him. The
first two times he'd really had to protect Connor, without the help of
the ready and willing adults who were always around at home, and he'd
done it in such a way as to make Connor suspect it was him.

\emph{I can't go back and change his mind,} he thought, as he stared
into his twin's determined face. \emph{The best I can do is plunge ahead
and hope to get away with half-truths.} He was glad that no one else was
there now. The last thing he wanted was for anyone to witness his
humiliation or Connor's aggressive truth-grabbing.

``Yes,'' he admitted. ``I dropped the troll, and I gathered in the
Lestranges and the Snitch.''

``Why?'' Connor leaned nearer and nearer. ``Did you think that I couldn't
do it myself? I \emph{am} the Boy-Who-Lived.'' His hand went to the scar
that he normally never paid that much attention to.

Harry sighed. ``No, Connor, I didn't think you could do it yourself,''
he said, being completely honest for this part. ``The troll knocked you
unconscious. And do you think you could have beaten the Lestranges on
your own?''

``Well, no,'' said Connor, shifting from one foot to the other. ``But
that's what the professors are there for. They would have dealt with
them. You didn't have to, Harry. Why did you try?''

``Because you were hurt, with the troll, and you would have been hurt,
on the pitch,'' Harry said. ``I got so \emph{angry}, Connor. I didn't
want anything more than to hurt the people who'd caused you pain. I know
the Lestranges were there to kill you. Why else would they \emph{dare}
come to Hogwarts but to attack the Boy-Who-Lived, the richest target
they could aim for? If they killed you in front of all of Hogwarts, it
would spread despair across the wizarding world.''

Connor's eyes were wide. He hadn't thought about the political
realities, Harry knew, and a wash of affection swamped him. He was there
to make sure that nothing forced those realities onto Connor too soon.
He should have at least one year of normal schooling, one year where he
was a child and a boy and could play like a child, without having to
weigh his every move. Their mother had already told Harry, when she
visited him in the hospital wing before they left, that she planned to
start guiding him into some politics and history this summer. \emph{Let
me hold on until this summer,} Harry thought. \emph{Just this summer.
That's all I ask.}

``And you attacked them because you were angry?'' Connor asked.

Harry nodded.

Connor exhaled. ``Harry,'' he said, ``I don't think that you should be
that angry.''

Harry frowned at him. ``I don't know what you mean.''

Connor spent a long moment musing over whatever it was he was thinking
about, then shook his head. ``Harry, rage like that\ldots{}rage like that
is \emph{Slytherin},'' he said, earnest as summer morning. ``Just getting
upset because of little things. I could have taken the troll. It was
just a little bump. I would have got up in a minute. And the professors
would have taken the Lestranges. You know how fast I am on a broom. I
could have flown away from their hexes.''

``And, Harry,'' he said, now picking his words with obvious care, ``it
makes it sound as though you want to do things with magic all the time.
That's the way that You-Know-Who works. I've heard stories. Sirius told
them to me. You-Know-Who used his magic when he didn't have to, to
terrorize and impress people and do things that someone else could have
done.'' He recited that line as if he'd memorized it verbatim from a
story. ``I don't want you becoming like that.'' He reached out and
squeezed Harry's shoulder. ``Please? I love you, Harry. I don't want a
brother who's like---'' He paused a long moment, then forced out,
``Voldemort.''

Harry felt a moment of shock hammer into him, and then he tucked that
moment away in the secret box of his thoughts and made himself
understand. Connor didn't know about any of the secret spells Harry had
learned, or just how dangerous Hogwarts might be for him, among adults
who had dark pasts and possible reasons to wish him ill. He didn't know
that Harry had trained himself for the Lestrange attack and hadn't been
in any real danger. And of course he would think he could have handled
the attacks himself. He was a Gryffindor.

Harry had not the least ability to make Connor understand his
point-of-view, not without revealing everything that Lily had promised
to guide Connor into more gently, and breaking his sacred trust. But,
luckily, he didn't have to come up with a story. Connor had done it for
him. All he had to do was accept it.

``You're right,'' Harry whispered. ``Sometimes I feel this enormous
\emph{anger} rearing up, Connor, and I don't know what to do to control
it. I lie in my bed in the dungeons and stare at the ceiling and want to
do something, anything, to release my magic.''

Connor gripped both his shoulders. ``Then come up to the Gryffindor
Tower when you feel that way, Harry,'' he said. ``I don't care what time
of the night it is. The password this week is \emph{lionheart}, and I'll
tell you what the new one is every time it changes. Please? I want to
surround you with Gryffindor goodness and warmth of heart. I want my
brother back.''

Harry smiled at him. ``I'll try.''

Connor smiled, too, and then bounced ahead of him all the way to the
dungeons, talking about the aftermath of the Quidditch game and where
Gryffindor stood in the contest of House points. He did give Harry a few
searing glances, promising in silence that he wouldn't tell Harry's dark
secret.

Harry smiled, and smiled, and came up with plans to conceal his actions
better the next time he had to save Connor. His deceptions so far truly
had been weak. He would have to practice more.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``I know that you threw that game.''

``Yes, Draco, of course I did,'' said Harry, lowering his
Transfiguration textbook and frowning at the boy who was looming over
his bed. Trying to catch up on all the homework he'd missed sleeping off
his exhaustion wasn't easy, not when Draco insisted on saying one inane
thing after another. ``I arranged for the Lestranges to show up and
threaten my brother \emph{just} so I could get the Snitch into Connor's
hand.''

Draco rolled his eyes, snorted, and plopped on his bed in a graceless
sprawl. He couldn't have been further from the stiffly poised boy who
sat straight up at every meal and followed every rule of pureblood
etiquette. Normally, the contrast amused Harry, but normally Draco
wasn't cutting at his nerves like a \emph{Diffindo} charm. He wanted
Draco to shut up and go away.

``I wasn't talking about that,'' the amazing annoying Malfoy
sing-songed. ``I was talking about the fact that you really stopped the
Lestranges and put the Snitch in Connor's hand.''

Harry turned his attention back to his book. ``Yes, I did.''

Utter silence. Harry raised his eyebrows and started counting to ten,
while trying to devour as much of the big paragraph in front of him as
he could. \emph{When Transfiguration approaches the normal curve of
normal shape\ldots{}}

Draco clawed the book down from in front of him and demanded,
``\emph{What} did you say?''

``I said that I did do what you said I did,'' said Harry, and then
paused to think about the structure of that sentence.

Deciding it was fine, he went on, ``I know that I ended the battle and
the game, and then let everyone think Connor did it.'' He shrugged.
``And yes, you could threaten to tell Connor, but it wouldn't make much
difference. Connor already knows.''

``You---'' said Draco, and then apparently couldn't think of anything
else to say.

``Yes?'' Harry lifted the Transfiguration book again.

Draco was silent for a long time. Harry could feel his mind racing,
exploring possibilities. He could threaten to tell the whole school, but
then people would pay attention to Harry, and Draco didn't want that; he
would want to be in the spotlight, too, or he would want to keep Harry,
whom he seemed to regard as some kind of fascinating magical beast, to
himself. He could threaten to tell Professor Snape, but Professor Snape
almost assuredly knew, and Harry didn't think he cared, or he would have
stormed up to the hospital wing to yell at him about it. He could
threaten to tell the other Slytherins, but that would just make them
dislike Harry, and Draco wanted Harry to fit in to Slytherin House.

Draco uttered a frustrated sigh and flopped back on the bedcovers.

Harry hid his smile, then froze. \emph{That was a smile, right? Not a
smirk? Just because I'm good at predicting Slytherins doesn't mean I
want to turn into one.}

He blamed his preoccupation for not being able to predict that the next
words out of Draco's mouth were, ``Do you want to come to Malfoy Manor
for Christmas?''

It was Harry's turn to put down the book and stare incredulously at
Draco. He ducked his head meekly, and let Malfoy good breeding and
pureblood manners try to speak for him. They didn't do a very good job
of it.

``No,'' said Harry. ``Are you out of your mind?''

``It'll be fun,'' Draco said.

``No,'' Harry said.

``My father is teaching me wandless magic,'' Draco tried.

``I already know it.''

``He really wants to meet you.''

``Draco, your father was a \emph{Death Eater,} and I'm the brother of the
\emph{Boy-Who-Lived}.''

``He was under the Imperius Curse.''

``No, he bloody wasn't, and my parents and my godfather would scream the
roof down if I tried to go to the Manor.''

``But my mother is your godfather's cousin.''

``That does not \emph{help},'' Harry pointed out, and then went back to
reading, ignoring any and all attempts that Draco made to sway him.

That evening, at least. It soon became obvious that Draco was not going
to give up, even when hit with a wand. Harry tried a reinforced
\emph{Silencio}, and Draco continued in increasingly obscene sign
language that Harry was slightly shocked the son of a pureblood
wizarding family knew.

\emph{No help for it,} Harry thought, as he finally rolled over and went
to bed for the night. \emph{Just ignore him.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``Detention, Mister Potter,'' Snape said almost absently, gliding past
the cauldron where Harry was laboring to skin shrivelfigs.

Harry almost opened his mouth to protest, but remembered himself in
time. Snape needed no especial reason to give detention, as he had shown
with the Gryffindors, and he had no reason to be pleased with Harry
right now. \emph{Perhaps he's going to yell at me about the Quidditch
game after all,} Harry thought, and ground and stirred and mixed and
chopped and tried to forget.

He still kept an eye on Connor, but luckily, his brother got along
without too many obvious mishaps. Hermione Granger had worked out a
system wherein she would lean over and whisper the proper instructions
to Ron and Connor just when Snape had reached the point in his circuit
where he was least likely to hear her. Snape delighted in humiliating
Hermione and had no reason to look kindly on students talking in his
class, which made Harry sure that he hadn't found out yet.

As if reading Harry's mind, Draco whispered, ``We could tell him about
the Mudblood---'' He cringed at the look Harry shot him, and amended,
``The Muggleborn, and her little cheating techniques.''

``It's not cheating if she gives correct information,'' Harry whispered
back, emptying the shrivelfig skins into the cauldron. ``Besides, if you
do that, I won't go to the Manor for Christmas with you.''

Draco cheered up in an instant. ``You're thinking about it, then?''

``Maybe,'' said Harry, and gave him a smile he hoped was mysterious. It
was sufficiently mysterious that Draco hummed happily throughout the
rest of Potions and seemed to have forgotten that Hermione existed.

Class ended, and Harry was cleaning out his cauldron when Snape advanced
on him and said, ``I have decided that your detention shall be served
immediately.''

Harry swallowed the protest he wanted to make. He wanted to go eat
dinner, but saying so would only incense the professor further, and he
would make some remark about thankless brats thinking their bellies were
more important than Potions. Besides, it kept attention off Connor.
``Yes, sir,'' he said instead, and waited in the room while the others
filed out.

Draco looked as if he would stay with him, but Snape stood there and
gave him a pointed look until Draco figured out that the rules of
Snape's classroom applied even to Malfoys. He stalked away, back
straight in that posture that made it seem as if he weren't sulking.

Snape shut the classroom door and gestured once with his wand. The
written instructions for a potion Harry had never heard of---and it
didn't have a name above it, either---appeared on the board. ``There,
\emph{Mister} Potter,'' he said, hissing that part of the name rather
than Harry's surname, which struck Harry as counterproductive. ``Get to
work. Your detention is to make this potion, correctly.''

Harry squinted at the potion's steps. They looked easy enough, to his
vast relief. He had taken care not to display any signs of unusual
talent or ability in Snape's class, keeping his marks exactly even with
Connor's, or even a little under. He actually wasn't that unusually
talented, the way that he was with spells, but he knew far more than he
let on.

\emph{This seems like a remarkably easy detention,} Harry thought, as he
went to fetch the unicorn horn, rose petals, demiguise hair, and fairy
wings he would need for the potion. \emph{Unusual list of ingredients,
and they don't make any potion I recognize, but maybe Snape figures I'll
get frustrated with making something useless and ask, and then he can
taunt me about my lack of knowledge.}

Because of that, he determined to say nothing at all, and set up his
cauldron, boiled the water, and made the potion---the most difficult
part of which was slowly scattering in the rose petals, one at a time,
while he stirred---in utter silence. Snape stalked back and forth, and
watched him. Harry didn't let that unnerve him, either. He finally
measured in the last pinch of demiguise hair, and his potion sparkled
once and then turned into a clear liquid with a sweet, enchanting smell.
Harry stood away from the table and put his hands behind his back,
waiting for Snape to come and check on it.

Snape did, sniffing the potion and studying it from all sides. Harry
braced himself for Snape to knock over the cauldron or Vanish the potion
and demand he start over again. At least Harry had used all the
ingredients, so he couldn't ruin it with a sudden addition from the
table.

\emph{Unless he added something from his robes\ldots{}} Harry fixed his
eyes on Snape's hands, and kept them there with such strict attention
that he almost didn't notice it when Snape spoke. His voice was not
mocking, not sneering. He simply asked a question.

``What do you believe the effect of this potion would be, Mister
Potter?''

Harry blinked, but shrugged and answered. He was probably wrong, since
he had not the slightest idea what it would do, but then, that was the
kind of challenge Snape would assign a student he was exasperated with.
``I believe it would work to purify, sir, given that the unicorn horn
and the rose petals are symbols of purity and love. The demiguise hair
could have something to do with invisibility, but demiguises are also
gentle, so it probably adds to the potion's overall calming effect. And
fairy wings are also from gentle creatures.''

Snape bent down. Harry looked up at him as calmly as he could; he
couldn't help but tense up a little when someone got this close, since a
Death Eater or other enemy might try to hold him at his mercy like this.

``I knew it,'' said Snape.

Harry wrinkled his brow. ``Sir?'' Snape knew what? Harry expected a
tirade against his intelligence to start any moment, since he had
probably got all the effects of the ingredients completely wrong. But
then, they were just guesses.

Snape stood back, and smirked. He looked extraordinarily ugly, doing
that, Harry thought.

``I knew that you were more talented at Potions than you appeared,''
Snape said, his voice soft but gathering in power. ``One can, of course,
have theoretical knowledge without practical skill, but I have
\emph{watched} you, Potter. I noticed, for example, that in some essays
you knew material that you claimed not to know in other essays. And you
sometimes committed common Potions mistakes, but they did not fit a
pattern. If you could not remember to stir counterclockwise on a memory
potion, you should certainly not have been able to remember it on this
potion.'' He nodded at the sparkling clear liquid in Harry's cauldron.

Harry couldn't swallow. He settled for clenching his hands into fists at
his sides and glaring at Snape. He hadn't been careful enough, he
thought, just as with the troll and the Lestranges. He had thought only
of keeping abreast of Connor, or just a bit behind, and hadn't checked
to make sure that his mistakes were consistent. Of course, he didn't
think he could have done that even if he'd thought of it. He just didn't
know enough about Potions to know what mistakes he \emph{should} make.

``Now,'' said Snape, his voice soft and sweetly poisonous, ``I did tell
you once that I did not thank any of my Slytherins to work at less than
their full potential. You have been doing so, and I have the proof
now.'' He tapped the cauldron with his wand, and the potion swirled,
flew out of the cauldron, and flowed over to a bottle waiting on Snape's
desk, in which it sealed itself. ``This is one of the preliminary steps
in brewing the Wolfsbane Potion, which I am laboring to perfect, so that
your \emph{beloved} werewolf can be around normal wizards who do not
become flesh-eating monsters once every month.'' He turned his sneer on
Harry again. ``This part of the potion calms the werewolf's mind,
gentles its murderous impulses. It is not impossible to make. It is one
that a fourth-year student could have made without hesitation.'' He
halted, holding Harry's eyes.

``But it wasn't that hard!'' Harry protested, and then cursed himself to
death and back again as Snape laughed at him.

``Precisely,'' Snape said. ``So. You have some talent at Potions, neglect
it though you will. And I will \emph{not} see you neglect it. You will
work to your full skill level in every Potions class from now on.''

``No, sir,'' Harry said, and set himself. He saw Snape wince, and
wondered for the first time if the older wizard could feel his magic
when he got angry. He grimaced. He would have to study specialized
Shield Charms, too.

``Why not?'' Snape taunted him. ``You fear everyone knowing that you are
\emph{not} hopeless in my class after all?''

``I won't show up Connor, sir,'' Harry said, feeling he might as well
admit it. Hiding was no good with Snape anyway, no more than it was with
Draco. In a way, Harry had to admit, it was freeing to be able to speak
like this in front of someone else.

``I thought so,'' said Snape. ``And that is easily solved.''

``You can give me detention for the rest of the year, sir,'' Harry told
him flatly. ``I am not going to budge on this.''

``I don't need to do that,'' said Snape. ``I only need to give your
\emph{brother} detention for the rest of the year. Particularly at, say,
the times of Gryffindor Quidditch practices.'' He put his head on one
side and watched Harry.

Harry shut his eyes. He could imagine Connor's cry of anguish from here.
His brother would die if he couldn't play Quidditch. And the thought of
the rest of the school not getting to see Connor play, not coming to
admire him for something he honestly did quite well\ldots{}

Harry opened his eyes and told Snape, ``I'll do as you say, Professor.
But I hate you for it.''

``I rather thought you might,'' Snape said.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Snape rubbed his head as Harry left the classroom. He had a
freshly-brewed headache potion waiting in his office, since he had
rather expected that this detention would make Harry stare at him like a
basilisk.

But it didn't matter. Pure triumph roared through his veins as he
stepped into his office, toasted an invisible companion, and drank the
potion.

\emph{This is one over on Harry Potter, one over on the Brat-Who-Lived,
one over on James Potter, and one over on Gryffindor,} he thought, as
his pain eased and then left him. That only made the triumph all the
keener. \emph{The boy is more talented than I ever dared to hope, and he
shall have no choice but to admit it in at least one place.}

\emph{And perhaps his brother will notice the difference\ldots{}wonder
about it\ldots{}speak to him\ldots{}}

\emph{The sooner I can separate him from his brother, the better.}

Snape strode over to the hearth, that he might firecall the kitchens and
order a private, complicated dinner from the house elves. He was in a
mood to celebrate in the privacy of his quarters.

And if part of that mood came from the desire to avoid Dumbledore's
piercing gaze and the proximity of a powerful, angry boy wizard\ldots{}.

Well, that was no one's business but his own.

\chapter{Discoveries}\label{chapter-14-discoveries}

\emph{You'd think,} Harry thought, as he struggled to keep flat to the
wall and not peer around the corner to see what Quirrell was doing too
soon, \emph{that he would manage to use some bloody spell to get past
that bloody dog.}

This was the fifth time in as many nights that he'd trailed Quirrell to
this door, and Harry was getting bored. Quirrell hadn't caused pain in
his scar again, and neither had he sneaked out to the Forbidden Forest
and drunk unicorn blood, or performed some unspeakable rite on a
hippogriff. He just came to this door and talked or shouted to the dog
behind it, until the dog exploded into barking---which should be
happening any moment now---and he rushed out.

Harry was starting to think that Quirrell wasn't as much of a threat to
Connor as he had seemed. After all, he hadn't been the one who had
brought the Lestranges, and he hadn't been the one who had dropped the
wards around the Quidditch pitch; if he were capable of that, Harry
thought, then he would have been in a position to cause much more
trouble. And if he had drunk unicorn blood\ldots{}that might be a sign
that the professor was mad, certainly, but no one had ever said that
Voldemort's followers had the monopoly on madness.

There was the cold voice that had spoken in the Forest, though, and that
was the reason that Harry kept following. His dreams insisted something
was wrong, but Harry didn't trust them. He'd never had the talent---

Footsteps sounded up the corridor, heading towards him. Harry hastily
cast the Disillusionment Charm on himself. Argus Filch had never caught
him, though he'd nosed around a time or two.

Harry watched in curiosity and anticipation as this dark-clad figure
strode nearer. Perhaps Quirrell's mysterious traitor had finally showed
up, and was going to help him. That would make Harry's observations more
interesting.

It was Professor Snape.

Harry ground his teeth. The insufferable Potions Professor didn't seem
to notice that he was being teeth-ground at, and settled against the
opposite wall not far from Harry.

Harry glared at him, and wondered if he would get away with a hex if he
cast one now. He didn't think so. But Merlin knew Snape deserved it, for
the way he had made Harry work like a house elf in the Potions class the
last few days.

He was trying to think of hexes he could cast without sound---even
though Lily hadn't started him studying nonverbal magic yet---and
without an immediate effect when the door banged open, as expected.
Quirrell came tottering around the corner, his hands fumbling at his
turban.

Snape unfolded himself like a rising bat. Quirrell turned around, saw
him, and gaped at him.

``S-Severus,'' he gabbled, sounding the way he always did.

``Quirrell,'' said Snape, not stuttering, Harry thought, on purpose, to
make himself sound more threatening. He came a step nearer, and his hand
went into a pocket of his robe and emerged with his wand. ``And what are
you doing here, hmmm? I never imagined that I would find you so
\emph{interested} in this one part of the school. You know what is down
there.''

\emph{Down there?} Harry wondered. He supposed it was possible that the
dog was guarding some kind of underground chamber, but if that was the
case, why not put it on the ground floor, or in the dungeons, where it
would have been easier to dive straight into the earth?

Quirrell laughed, and even that sounded false. Harry concentrated, but
could feel no sense of dangerous magic about him. The most noticeable
thing, besides his annoying laugh, was the constant smell of garlic that
hung about him. ``Only p-professional interest, S-Severus,'' he said.
``You know th-that I l-like to study o-other fields that have some
b-bearing on m-my own. That is a-all.''

``What bearing could Hagrid's pet have on your own field?'' Snape asked,
coming another step nearer. Harry shivered. He had never seen Snape wear
this face, holding a faint hint of amusement but hard and cold as a
sheet of steel. He supposed it was the face that Snape had worn during
his Death Eater days.

``Oh,'' Quirrell said, ``s-such a w-wondrous creature. I w-wonder who
b-bred it, that is a-all.''

``Is it?'' Snape said, and his voice had become so quiet that Harry had
to strain to hear. ``I think, Quirrell, that we would all be best served
if you stayed away from the Stone. You know where it is. You know that
it is well-protected. And you know what can be done with it. Unless you
were planning to brew some Elixir yourself---and why would you want
to?---then you have no reason to want to see it, or study it.'' His wand
was rotating in his fingers now, spinning fast enough that Harry could
see only the tip, moving like a dark star.

\emph{Stone? Elixir?} Harry stuck the words in his mind for later, while
Quirrell made what could be called an attempt at a sneer, if one was
being kind.

``And wh-what do \emph{you} w-want with the St-Stone, S-Severus?'' he
demanded. ``Do you w-want to know wh-where and h-how it is h-hidden so
th-that you can m-make the E-Elixir y-yourself?''

Professor Quirrell's stuttering got worse when he was truly nervous,
Harry noted, making most of his attempts at intimidation useless. Of
course, there was the cold voice in the Forest, and the steady voice
that the professor had spoken with when he thought himself alone. This
might be all an act, then.

Harry didn't think Quirrell's squeak when Snape lunged at him and pushed
him up against the wall was an act, though. Snape held his wand to
Quirrell's throat, and his face had gone completely calm, without a hint
of the dark laughter that seemed so natural to him.

Harry recognized the expression. He'd seen it in the mirror often
enough, just after Lily had given him a speech about what war might
mean. It was the expression of a man preparing to kill.

``Now, Quirrell,'' asked Snape, ``will you force me to this? I do not
want to. If nothing else, it would be hard to explain to Albus. But I
will, if you push me. You know what I was.'' He made a gesture towards
his left forearm, invisible unless one was looking for it.

Quirrell couldn't even speak, just gasp and cry incoherently. Snape
watched him for a long moment, then let him go with a violent shove.
Quirrell stumbled and half-fell, catching himself against the stone and
staring hard at Snape.

``You will leave now,'' said Snape quietly. ``If I find that you have
come here again, then I will speak to Dumbledore.''

``D-do it n-now, if you w-want,'' said Quirrell, and straightened
himself with a dignity that struck Harry as ridiculous more than
anything else. ``I d-don't care.''

Snape laughed, and the sneer was back around the corners of his mouth.
``No,'' he said. ``I would rather know that I have you under my thumb,
Quirrell, ready to destroy whenever I wish.'' He gestured negligently
down the corridor. ``Go.''

Quirrell left, stumbling all the while. Snape watched him out of sight,
and then turned and aimed his wand towards Harry.

``\emph{Finite Incantatem},'' he snapped.

\emph{Shit, he noticed the Disillusionment Charm,} Harry thought, but
didn't attempt to run as it melted. He stared up into Snape's eyes,
which, for a moment, flashed genuine surprise---\emph{who did he expect
to see?} Harry thought---and then shuttered. He moved forward and
grasped Harry's arm.

``How much did you hear, Mister Potter?'' he hissed.

``The whole of it.'' Harry didn't call him sir. He didn't see that he
should have to. They were outside the boundaries of classroom and
Slytherin House, in the middle of something more important, something
that encompassed them both---the war against Voldemort, the war that
Harry intended to see Connor survive.

Snape said something quiet and obscene under his breath, and darted a
glance down the hall. Then, quite shockingly, he sank to one knee before
Harry and stared into his eyes. Harry stared back, feeling the slight
twinge in his head that he sometimes felt when Snape did this. Whatever
he was looking for, the Potions Professor seemed to find it. He closed
his eyes and pinched his nose for a moment.

Then he said, ``Potter, I will tell you what this means, so that you
won't go sniffing about for trouble. I expect you to go back to your
common room after this and not wander about after curfew again. Do you
understand?''

Harry nodded. He did not say that he intended to wander anyway, to find
disused corners of the castle where he could practice his wandless
spells. It was not as though Snape had made him promise with an
Unbreakable Vow.

``Dumbledore has a Philosopher's Stone, well-protected, in the castle,''
Snape said quietly. ``He is keeping it safe from the Dark Lord. I might
almost think that Quirrell is a minion of the Dark Lord's, but I know
that he was not Marked when I served among the Death Eaters. You,
however, will stay \emph{far} away. This is a matter for adults. Do you
understand?''

``Perfectly, sir,'' Harry said. There was no need to come back here
again, then. He knew what he was going to do with his own information.
He didn't even blame Snape for not telling Dumbledore his suspicions
about Quirrell. He was going to put his own information to even better
use.

\emph{The troll was clumsy, the Lestranges clumsier. But there I had to
worry about immediate danger to Connor's life. Now I don't, and I can
plan.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``Are you coming with me to the Manor for Christmas yet?''

``No, not yet.''

Draco paused. ``Now?''

``Still not yet.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``Harry?''

Harry hastily stood up and shoved the book he was reading underneath the
table. Not quick enough to escape Hermione's eyes, of course. She stared
at him, then whirled her bag over her shoulder and set it down heavily
on the table. No dust rose. She'd been coming here, her own private
study corner of the library, for long enough that she'd cleared all the
dust off. Harry had noticed it a few weeks ago, and kept the knowledge
to himself, because he hadn't thought of a way to use it yet.

Now he had.

He smiled weakly at Hermione. ``Hi, Hermione. Sorry. I just wanted a
quiet corner to read in, and this one looked nice and clean. I didn't
realize it was yours. Sorry,'' he added again, and tried to stuff the
large book he was carrying into his bag.

``What's that?'' Hermione asked, and then gasped as she caught sight of
the title. Harry bit his lip and looked down at the ground as if
ashamed, while silently congratulating himself. Sharp as Hermione was,
this plan was already going much better than the other ones to give
Connor some sheen of heroism had.

``Harry!'' she said, her voice rising distressingly. ``\emph{Darkest
Alchemies?} Where did you get that? Isn't it supposed to be in the
Restricted Section of the library?'' Her voice turned accusing. ``And why
are you reading it?''

``It's not a Dark book, Hermione, really,'' Harry said desperately. He
studied her face. Her lips were set, and her eyes as well as her mouth
managed to frown at him. He had counted on that. ``It's a sort of
history book.''

``But why were you reading it?''

``Because I was interested, that's all,'' Harry said, shrugging.
``Something that Snape said in class the other day.''

For a moment, Hermione looked as if she'd let herself be distracted by
that. Harry's sudden gifts in Potions had astounded and irritated her,
and she'd been working hard herself to catch up. The books peeking out
of her bag had the look of Potions texts, in fact, Harry thought.

Harry had a plan to get her back on the trail if he needed to, but she
wound up clinging to the original idea. ``Professor Snape didn't say
anything about alchemists,'' she said, eyes narrowing.

``Uh\ldots{}'' said Harry, as if she had caught him flat-footed.

He shifted his weight, glanced around, and then said, ``Well, see you
later, Hermione. Bye.'' He carried the book around the corner of the
shelves and waited for a moment. Sure enough, Hermione's head poked
around the corner behind him.

He looked towards her, giving her enough time to duck out of the way,
and then shoved the book awkwardly among the others, patting the spine.
That looked like enough to hide it---or to make a pathetic attempt at
hiding it. He hurried out of the library, bag banging on his shoulder.

He had no doubt that Hermione would look at \emph{Darkest Alchemies} the
moment he was far enough away. And she would find the well-worn page
about the Philosopher's Stone and its last inventor, Nicholas Flamel.
She would wonder about that. She would carry the questions to Connor.
Connor's own suspicions of Harry possibly going Dark, fed by Ron's
prejudice against Slytherins, would drive them to investigate. And then
they stood a good chance of finding out that one was hidden in the
school, or at least coming to Harry and drilling him for answers. He
could drop subtle hints that would lead them in the right direction.
Connor would find out about Quirrell---Harry could make it seem as
though he were simply too blind to notice what the professor's constant
visits to the third floor meant---and then Connor would tell Dumbledore
about him. There would be plenty of glory for Connor, and all of it
produced from good old Gryffindor honesty, hard work, courage, and
suspicion of sneaky Slytherins.

Harry was rather proud of himself for thinking of such an ingenious
plan. Of course, it helped that he would be in the shadows behind
Connor, ready to aid him with a nudge in the right direction, or a
carefully timed spell if things looked to be getting out of hand.

The most important part was that Connor survive, after all. But if Harry
could lead his brother to his own victory while not being too obvious
about it\ldots{}

Harry thought it a good deal all around.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``Harry.''

Harry glanced up, blinking. He'd been deep enough in his Charms textbook
that he hadn't heard Draco ordering the other Slytherin boys out, or the
room door opening and closing. But now they were alone, and Draco sat on
his bed and stared at Harry with one of those serious expressions that
promised a conversation Harry wouldn't like. He put down his book,
stared back, and waited.

The first words out of Draco's mouth, though, were, ``Why won't you come
to the Manor with me for Christmas?''

Harry sighed. ``Draco, we've been over this---''

Draco held up a hand. ``I know that you think my father's a danger to
you. But really, Harry's, he's not.'' His voice was so painfully earnest
that Harry didn't have the heart to correct him just then, though he
realized he should have when Draco went on. ``I've talked to him about
the Dark Lord's first rise. Poor Father was under Imperius from almost
the first moment that the Dark Lord gained power. After all, he knew
that he couldn't leave the Malfoys alive behind him, but enslaving them
was better than killing them. And Grandfather Abraxas had just died.
Father was reeling, uncertain, just trying to find his place in the
world. I think that that was it. He served the Dark Lord only as long as
he couldn't fight the curse, and then broke free and gave testimony to
the Ministry that helped to convict other Death Eaters.''

Harry looked at him for a long moment. Draco stared back at him, posed,
shining, happy. Innocent, in much the same way that Connor was, Harry
thought. The idea made him weary.

He could lie to Draco, perhaps, and come up with another reason to
escape the Manor---that Connor wouldn't let him be apart from him at
Christmas. But he didn't want to lie. Shameful as it was, Harry thought,
he was growing used to honesty with Draco and Snape. They wouldn't let
him lie, so why should he? About anything?

And Draco was \emph{wrong}, and at some point, his wrongness might
endanger Connor. Or, more within the realm of immediate possibility, his
ignorance might endanger Harry, and if Harry died, he wouldn't be there
to protect and defend Connor throughout the coming war.

``Draco,'' he said quietly, ``my mother's told me the stories of the
first war with Voldemort.'' Draco flinched and scooted backward on the
bed, away from him. Harry didn't stop. Draco had wanted privacy. He had
wanted a serious discussion. Well, he was going to get both. ``I know
that he wasn't above using the Imperius, but he only used it on some of
the Death Eaters. He didn't use it on the ones who believed in his
ideals and willingly joined him.'' He paused, and waited for Draco to
grasp the truth of what he was saying.

Draco blinked, puzzled, for a long moment, then paled. ``My father is
\emph{not} a willing Death Eater,'' he said. ``He never was.''

``He trained you to hate Muggleborns, Draco,'' said Harry. ``You say
\emph{Mudblood} more naturally than you say \emph{I'm sorry.}''

``Malfoys never need to apologize,'' said Draco, but his attempt to
lighten the mood fell utterly flat, and both of them knew it. He shook
his head. ``You're wrong about this, Harry. You must be.''

``Why?'' Harry asked, and heard his voice deepen and turn flat.
``Because you want me to be? Because you don't want to believe me? I
thought that Malfoys at least needed to face reality.''

``No,'' Draco whispered.

Harry held up three fingers on his right hand. ``There might be others,
but these are the ones I know about,'' he said. ``My mother told me that
Lucius Malfoy helped kill the Prewett brothers. They were the brothers
of Molly Weasley, Ron's mum. Did you know that?''

``No,'' Draco whispered.

Harry suspected that he was both denying knowledge and denying what
Harry was saying. That didn't matter. He folded one finger down. That
left two. ``And he was responsible for attacking a Muggleborn family,''
he said. ``Muggle parents, three children with magic who attended
Hogwarts. The Nascents. He tortured them to death. Bellatrix Lestrange
was there, too, but they recognized Lucius Malfoy's style.''

``My father doesn't have a \emph{style} of torture,'' Draco said, his
voice very small. ``You take that back.''

Harry folded his second finger down. ``And then there was the Bones
family,'' he said, very quietly. ``Edgar Bones, and his wife and
children. One was a baby, Malfoy. A \emph{baby}, not as old as Connor
and I were when Voldemort came for him. He only---\emph{only}---murdered
them, because he didn't trust his wandwork against Edgar's. And Edgar
Bones was Susan Bones's uncle. She's walking around the school right
now, missing her uncle and aunt and cousins. Oh, and her grandparents,
because---''

``\emph{Shut up}!'' Draco yelled.

Harry folded down his last finger, and sat watching. Draco was breathing
hard, his cheeks flushed, his hair falling around his face. He took a
breath that sounded to Harry like a great, gasping sob, though he wasn't
letting any of his tears actually fall.

``He's my father,'' said Draco. ``He's my \emph{father}. I love him. He
wouldn't do anything like that. Or he'd tell me if he did.''

Harry leaned forward. ``It's all a matter of historical record,'' he
said. ``You can go into the Ministry and look it up in the records. The
Pensieve and the trial transcripts are there. He claimed to be under
Imperius, and he bought his way out. But he killed them, Draco. He
killed them and he \emph{laughed} when he walked away free---''

He hushed. Draco had reached out and struck him, awkwardly, across the
face, not quite a punch and not quite a slap. Harry had taken worse from
Connor in their mock-fights, but he watched in silence as Draco ran from
the bedroom, slamming the door behind him like a giant's tread.

Harry sighed and picked up his Charms book again. He felt a faint
sadness for the loss of his friendship with Draco, but it had been
coming. He could only ignore the past for so long.

\emph{Besides, my first and primary loyalty will always be Connor's.
What} would \emph{happen if I became friends with a Slytherin? Would I
feel compelled to choose between them?}

Harry shuddered. He could imagine little more distressing than that.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Harry woke, blinking. He'd fallen asleep studying, which was unusual for
him. He stood up and made his way to the loo carefully, since he could
hear breathing around him and knew the other boys had returned.

He paused, though, when the faint \emph{Lumos} spell on his wand showed
him that Draco's bed was still empty.

Harry hesitated, then put his wand on his palm and murmured,
``\emph{Point Me} Draco Malfoy.''

The wand turned, pointing definitively out of Slytherin House. Harry
groaned to himself. He wanted nothing so much as to shower and go to
bed. And Draco was probably wandering around the castle in a sulk, or in
Snape's quarters complaining about what a prat Harry was.

Still, though, Harry did feel responsible. He probably could have found
a gentler way to break the news to Draco. And he really \emph{had}
thought Draco was more politically aware than that. What son of a
pureblood family wouldn't be?

He followed the wand in silence, casting another Disillusionment Charm
on himself as soon as he left the common room. The wand tugged him up
the dungeon stairs, surprising Harry, who hadn't thought Draco would
have gone that far. And then it pointed to the doors to the outside, the
same doors Harry had followed Quirrell out earlier that month.

Wary, Harry stepped outside. The wand aimed steadily towards the
Forbidden Forest.

``Oh, \emph{shit.}''

\chapter{Draco In Danger}\label{chapter-15-draco-in-danger}

Harry pushed aside a thickly clinging vine and ducked beneath it, drawn
along the path by his pointing wand. At least he didn't have to be as
quiet as he had when he followed Quirrell, he thought, and he could use
the \emph{Lumos} spell to light his way without worrying if anyone saw
him.

\emph{Unless Quirrell is in the woods tonight.}

\emph{Or unless a magical creature sees it and comes towards me, ready
to devour me.}

Harry forcibly reminded himself that Draco might see the light and be
drawn to it, too. It was unlikely, but most helpful things were in the
Forbidden Forest. That did not mean it would not happen.

Harry sighed. \emph{Speaking of that, I suppose I'll have to turn and
confront them sooner or later.}

He had been hearing faint sounds from behind and beside him almost from
the moment he had entered the Forest. When they didn't attack, he
ignored them, intent on getting to Draco before something could happen
to him. But the sounds were louder and more insistent now, and he knew
that he would have to confront them.

He turned and called, ``Who's there? I can hear you.'' He braced
himself, just in case the creatures tracking him weren't intelligent
after all and came at him all in a rush. The \emph{Protego} incantation
waited on the tip of his tongue.

There was a long pause. Then the noises came again, closer this time and
louder. Harry hadn't been able to tell what they were as muffled thumps,
but now he clearly made out the sound of hooves.

A centaur trotted out from between the trees on the right side of the
path and stood facing him. Harry's wand-light made his face shadowed and
half-demonic. He had striking blue eyes, hair as pale as Draco's, and a
faintly golden body, which shifted color towards a deep gold on his
flanks.

``Harry Potter,'' whispered the centaur. ``The stars are watching you.''

Harry half-glanced up, but he couldn't see the stars through the thick
cover of trees overhead. ``And so are you,'' he said, bringing his
attention back to the centaur. ``Why?''

``We know that you came here in pursuit of a boy who walked into the
Forest a short time ago,'' whispered the centaur. ``We know many things
from watching the stars. Your fate is written there, Harry Potter.
Sealed there.''

Not for the first time in his life---the first had been when he'd read
about them in a book on magical creatures---Harry decided that centaurs
were creepy. He simply nodded. ``Thanks,'' he said. ``It's always
pleasant to know that. However, I have to find Draco.'' He turned to go
down the path again.

The trees to his left gave way, and a chestnut centaur galloped onto the
path in front of him. He was bigger than the palomino one, and had dark
eyes and hair that looked the color of blackberries in the light. He
folded his arms and looked steadily at Harry.

``You must come with us, Harry Potter,'' said the palomino centaur.
``The stars are bright tonight. Mars is in his glory. Because of that,
we are willing to give thanks, and to listen to the one who comes
beneath Mars's aegis.''

Harry concealed his annoyance. He had hoped to get on and find Draco,
but he did not think that he could take two centaurs at once, and he had
no wish to show that he had been here, which dead or injured centaurs
would surely reveal. He forced a smile.

``All right,'' he said. ``Where are we going?''

``This way,'' said the palomino centaur, and cantered off down the path.
The chestnut centaur stepped out of Harry's way and flicked his tail as
if in permission. Harry shook his head and fell in behind the palomino,
hearing the clop of hooves as the chestnut walked behind him.

The \emph{Point Me} spell continued to show that Harry was on the same
trail as Draco, which somewhat lessened his agitation. He was beginning
to hope that Draco hadn't fled in a raging sulk after all, but had had
the sense to stay on the path and seek some place to be alone. He might
even go back to the castle before Harry did, depending on how long the
centaurs decided to entertain him.

``I am Firenze,'' the palomino announced suddenly.

``And I am Coran,'' the chestnut said.

Harry blinked. He had read once that centaurs gave their names on the
second meeting, not the first. But they also watched the stars and spoke
incomprehensible nonsense about them. So they might consider this the
second meeting, since they were some way down the path now. Who knew?

``You know my name already,'' he said, struggling to remember the
courtesies he'd heard. Lily had tutored him in greeting customs for
magical beings other than pureblood wizards, just in case Connor ever
needed allies someday and Harry had to serve as ambassador, but it was
far down on the list of important training, and he wasn't surprised that
he couldn't remember more of it. One phrase seemed safe enough, though.
``I am glad that you greet me in the name of the stars.''

Firenze stopped walking and glanced back at Coran. Harry stopped too,
perforce, backing away from the palomino's switching tail. The centaurs
locked each other in a long gaze.

Harry waited. The \emph{Point Me} spell still indicated, faithfully,
that Draco was straight ahead. He wanted to push Firenze out of the way
and run, but he couldn't do that, so he made peace with his impatience
and waited some more.

``He knows the courtesies,'' Firenze said at last.

``And he came beneath Mars's light,'' said Coran.

``That is significant,'' they both said at once, and then Firenze turned
around and resumed his trot forward, this time forcing Harry to follow.

The Forbidden Forest changed when you were traveling through it with
powerful magical creatures, Harry found. The shadows seemed less
menacing. The trees drew back more often, and let a paler, colder
starlight through. Harry checked once or twice, but he couldn't make out
Mars. Perhaps the angle was bad.

\emph{Or perhaps the centaurs are barking,} Harry thought, shivering
slightly as a chill breeze cut past him and he nearly stumbled over a
root he hadn't seen until too late. \emph{Guess which one I choose.}

The path finally widened out and then broke in two. One branch curved
around the base of a small hill, while the other led to its top. Firenze
solemnly mounted the hill, and then glanced back as Harry followed.

``It is possible that you shall be angry,'' he said in a distant voice,
not sounding as if he really cared. ``But you must understand that all
fates serve the balance, and all things are written in the stars.''

Harry narrowed his eyes. They had arrived at a place that seemed
significant, and the \emph{Point Me} spell still indicated straight
ahead\ldots{}

``You took Draco, didn't you?'' he asked, not bothering to keep the
accusation from his voice.

``It was written,'' said Firenze, and then walked over to something
Harry couldn't see. Harry hurriedly climbed the last few steps he had to
go.

He found a group of stones assembled at the top that looked for all the
world like an imitation gallows. Draco stood on the platform, shivering,
his head bowed. A vine was looped around his neck and around the stone
serving as crossbar. There was no trapdoor that Harry could see, but
there wouldn't have to be, he knew. One kick from a centaur's powerful
hooves could make the vine sway and send Draco flying sideways, where
his neck would snap or he would choke to death. Or perhaps he would just
smash his skull on the stones.

\emph{Any way, not an easy death,} Harry thought, as he stared and
desperately struggled to recall what he knew about centaurs. They were
polite, they observed the stars, they stayed out of wars for the most
part---though they had fought against the Dark Lord Grindelwald, who had
threatened them with extinction---and they didn't generally go around
kidnapping schoolboys in forests and hanging them from stone gallows.

Draco stirred then, and decided to make everything more complicated.
``Harry!'' he shouted, starting to run across the platform.

Firenze caught him by the vine around his neck and held him still. Draco
swayed to a stop, gagging. Harry took a tense step forward, but Draco
finally remembered the noose and stepped back. His breathing returned to
normal in a moment. He glared at Firenze, then turned the glare outward
to include Coran, who had come up beside Harry.

``This is a test,'' Firenze told Harry, his voice deep and somber as
echoes in a bottomless pit. ``You will pass it, or Draco Malfoy will
die. He will not use magic in any way, including to aid you, or he will
die.''

``Why?'' Harry asked.

``This is the test of the one who comes under Mars,'' said Coran, and
his voice was sterner than Firenze's. ``You may not question. You must
do.''

Harry choked his impulse to scream in frustration, and even managed to
smile. ``Then tell me what I must do, honored centaurs.''

Coran moved in front of him, feeling briefly on the ground for
something. He came up with an egg-shaped stone, which in the light of
\emph{Lumos} looked some shade between deep purple and black.

``You must crack this---''

Harry nodded, and raised his wand.

``Using wandless magic,'' Coran continued. If he had been a human, he
would have sounded smug, but he only sounded remorseless. He held the
stone out to Harry.

Harry stared for a long moment. He could perform a Blasting Curse with
his wand, but he hadn't studied it wandless. He hesitated and glanced
once at Draco. Draco had settled for glaring at the centaurs, at the
vine around his neck, and at Harry---though, to be absolutely truthful,
the looks he sent Harry had a lot of pleading in them, too.

\emph{Could I sever the vine, take Draco, and run?} Harry knew the
answer almost as soon as he had the thought, though. The vine shifted
and settled itself possessively around Draco's throat in a motion that
no wind would allow. It was alive, and perhaps intelligent. He supposed
it would have to be; Draco would have freed himself already if it were
that simple.

Which left his only option as passing the test.

Harry turned back to the stone and frowned at it. He had learned
wandless magic before out of grim duty and driving necessity; he had
imagined Connor dying, and each time, it gave him the strength to press
on. And when he had thought that Connor might die in a week, in six
days, in five days, in four days, nothing had stood in his way. He
hadn't even felt the loss of sleep until the spell exhaustion hit him.

Could he summon the same emotion for Draco?

\emph{No}, he realized, after a moment of trying. He did feel worried
that Draco might die, and he would certainly experience guilt if that
happened, but there was no love there yet, nothing to send the magic
down well-worn channels in the center of his being. He would have to use
something else.

What?

``You have until the stars set, Harry Potter,'' Firenze intoned calmly
just then, jolting him.

Harry glared at him. ``You didn't say that I had a time limit.''

``The one who comes beneath Mars's light always has until the stars set
to pass his test,'' said Coran, as if Harry should have known that. He
continued to hold the stone out, straight and steady. His arm hadn't
wavered yet.

Harry ground his teeth. The anger came surging up in him, and he focused
it on the stone, hoping that might work. Crack, \emph{you stupid thing!
Draco and I have to get back inside and away from these loonies before
we're missed!}

The stone did nothing. If stones could be smug, Harry was sure that it
would have been.

Harry poured the rage out, and it was fruitless. Nothing happened, not
even a faint line seaming the stone's surface, while he had sweat
running down his brow from the force of his concentration.

``It is an hour until the stars set,'' said Firenze's voice, regular as
the chiming of a clock.

Harry closed his eyes and banished his anger. So love would not do it,
and neither would anger. What would?

But those were the forces that had always driven his wandless magic.
Harry could possibly learn new ways, but they would take longer than he
had. And then Draco would die.

Harry did not think he could bear that. He had caused the argument. It
was his fault that Draco was out here in the first place.

\emph{Worry?}

\emph{No, that's a niggling little emotion. I need something else.}

Well, was there anything that his love and his anger had in common? Did
they spring from some shared seed that he could use to free Draco?

Perhaps it wasn't an emotion.

And then Harry could have laughed aloud in relief. Of course. It was the
same thing that Snape was always cursing him for, the same thing that
had made Connor impatient with him, the same thing that had caused him
to continue the argument with Draco instead of simply giving in and
saying that Connor wouldn't let him come to Malfoy Manor for Christmas.

\emph{Will. Stubbornness. Sheer bloody-mindedness.}

Harry focused his will on the stone. He imagined it cracking. He willed
it to crack. He created a careful image of the stone cracking, so
intense that dark spots swam in the air before his eyes and his ears
rang, and he overlaid it on the stone. He could still see the whole dark
purple surface under the shattered one, but only just. The ringing in
his ears became a roar.

\emph{Crack. You} will \emph{crack.}

It was nothing like anger, nothing like love, but the root and
wellspring of them both. Harry called patience and determination and
unbending, unflinching uncooperativeness to his aid. He focused, and he
pushed, and he began to feel the outer edges of the stone's solidity as
an irritating buzz off to the side, just barely audible under the
torrent of his magic.

\emph{Crack. You} will \emph{crack.}

The stone pushed back at him. It had no will of its own---the smugness
Harry had imagined was not real---but it had the same resistance that it
would if he were trying to shatter it against the edge of a table by
simple pounding. It existed, and it was hard, and it did not want to
crack.

Harry carefully formed his will down into a sharpened point, a chisel,
and then put all his magic behind it at once.

\emph{Crack.} His being resonated with the word, and he trusted that he
had the will and the magic, both, to carry it out. \emph{You will crack
because I say you will. And now, you will---}

\emph{Crack!}

Harry blinked, then staggered forward as his will shoved through
something that was no longer there anymore, like the dissipating smoke
of \emph{Fumo.} He caught himself on his hands and looked up.

Coran held shattered bits of stone in his hand, but only a few
fragments, themselves no bigger than shards of eggshell. More had
apparently scored his face and shoulders in their whipping passage, but
Coran didn't seem to care about the blood. He looked at his palm, as
though wondering where the stone had gone, and then nodded gravely,
solemnly, to Harry.

Harry glanced over at Firenze. The blond centaur was untying Draco, his
movements swift and efficient. Draco made a gasping noise when the vine
came free that Harry was sure was exaggerated, or he would have had
difficulty breathing when it actually gripped him.

Harry got slowly back to his feet. He ought to have felt tired; he
usually did, after wandless magic. Instead, he felt oddly braced, as if
he had gone through a swift walk through cold air. And the ringing,
roaring sound his magic had made hadn't quite faded yet. Harry tasted
the air around him, still rich and alive with playful, gamboling power,
and found himself smiling.

``The one who comes under Mars has passed the test,'' Firenze said,
looking as if he spoke to the stars.

``When the time comes,'' Coran intoned, ``we follow.''

Firenze cantered over to Coran, and then both of them, to Harry's utter
astonishment, stretched out a foreleg in his direction and bent over it.
Harry clumsily returned the bow, struggling to remember the phrase that
closed out a cordial conversation between centaur and wizard. He ought
to remember it, if only because it had been so odd---one of the least
complicated phrases that any magical creature used in formal
communication.

\emph{Oh, yes.}

``Under star and over stone may your way lead you,'' he said. ``Under
darkness and over water.''

Firenze nodded to him. Coran said, ``Under the light of Mars may you be
led,'' which was not in the book that Harry remembered, and then both
centaurs turned and galloped into the darkness.

Harry let out a little breath, blinked, and then turned back to Draco.
``We'll need to cover up those bruises on your neck, unless you want
everyone to know we were out past curfew---'' he began.

He stopped. Draco was staring at him.

Harry winced. In the struggle to save Draco and the excitement of
actually succeeding, he'd forgotten what drove Draco out here in the
first place.

``Yeah, I know,'' he said. ``I acted like a git. I didn't have any right
to say those things in that tone of voice. Once I realized you didn't
know, I should have been gentler. Sorry.'' He held his breath and
waited, hoping that the next words out of Draco's mouth would be
forgiveness. He could make Harry's life much harder than he had already
if they weren't.

Not to mention that he \emph{would} miss Draco's conversation, even if
he had turned out to be so self-absorbed that he told Harry almost
nothing about Lucius or his movements. Draco was one of the few people
in his life who wasn't part of the elaborate deception at play around
Connor. Unlike Snape, he wasn't hostile, and unlike Lily, he was close
to Harry's age. Draco just---existed in Harry's life, and though that
would almost certainly change later, when Voldemort returned and Draco
chose pureblood loyalties, for right now he could chatter, and Harry
would listen.

Draco closed his eyes and shook his head. ``Harry\ldots{}'' he began,
and stopped.

``What?'' Harry swallowed. Maybe he \emph{had} foregone his chance at
Draco's forgiveness. He would just have to live with it if he had, but
he wished Draco would \emph{say} something and show him why.

Draco opened his eyes. ``Harry,'' he said, ``you saved my life. I owe
you a life debt.''

Harry stared at him in turn.

Then he shook his head and backed away, making sure to keep his voice
soothing. ``Draco, you've had a hard night. An argument, running away
into the Forbidden Forest, and nearly dying. You don't know---''

Draco drew his wand from his sleeve and held it out over his palm.
``\emph{Diffindo}!'' he said clearly, and a cut appeared on his hand. He
turned towards Harry, his face alien and too solemn under the
\emph{Lumos} light.

\emph{This is the son of the pureblood wizarding family,} Harry thought.
\emph{He might not know about his father's past, but he knows the
rituals.}

``I do so pledge my debt to Harry James Potter,'' Draco said, still in
that same clear voice that would have made most of his teachers
astounded to hear, ``willingly performing whatever service he asks of
me, until I save his life in turn or the debt be expunged.'' He swept
his wand over the cut, and the line turned silver where it passed,
looking first like frost and then like a very old scar. ``This I do,''
Draco added softly, ``in the name of Merlin, and in thanks for my
life.''

He stood looking expectantly at Harry.

Harry sighed. He knew of no way to refuse to accept a life debt without
killing the wizard who offered it, but he could at least leave the
payment of the debt up to Draco.

``I, Harry James Potter,'' he said, ``do so accept the offered debt, in
Merlin's name, and in gladness that the one who offered it still
lives.''

The air between them flashed silver for a brief moment. Then the light
turned to the cold air that Harry saw when he breathed out in winter,
and floated away towards the stars.

``Name my service,'' Draco said, still impossibly clear.

``Draco---''

``Do it, Harry.''

Harry shook his head. ``I leave it up to you to name it,'' he said. ``I
\emph{can} do that, and I choose to. Serve me in whatever way would
please you most.'' He carefully cast a Concealment Charm at the bruises
on Draco's neck, and was relieved when they disappeared. He hadn't been
sure that his magic high after shattering the stone would last. ``Now,
come on, Draco, we have to get back.''

Draco fell into step beside him, but he seemed to be thinking. They
hadn't reached the halfway point on the path before he said, ``I've
thought of something, Harry. I \emph{can} choose the form my payment
takes, right?'' He looked at Harry carefully, as though he thought Harry
was tricking him.

Harry nodded.

``And guarding you in a dangerous place would be an acceptable form of
it?''

``Of course, Draco, but what place---''

``Then,'' said Draco, ``I choose to repay my debt by guarding you in
Malfoy Manor. Where you are going to come visit me. At Christmas.'' His
smile was blinding.

``No,'' said Harry flatly.

``You left it up to me to choose the payment,'' Draco reminded him,
bouncing a little.

``I didn't say that you could---'' said Harry, and then stopped. He
\emph{had}, actually, and the moment when he could have reclaimed the
debt was past. He had offered it to Draco, and Draco had chosen the form
his payment would take. He'd even used the correct phrasing to seal it.
And just as there was no choice about accepting a life debt in the first
place, so there was no choice about accepting the form the payment took
if it was turned back on the giver.

Unless he killed Draco, and that was still not an option, though Harry
had to admit it was looking a bit more tempting than before.

``I promise, Harry.''

Harry turned to Draco, who had caught his hand and stopped on the path.
His face was hard, his eyes gleaming, near a fanatic's. It disturbed
Harry, who imagined it was the way his Death Eaters would look at
Voldemort.

``I think you're wrong about my father,'' Draco said, firming his clasp
on Harry's wrist. ``But I \emph{promise}, I \emph{promise} you, that I
won't let any harm come to you in the Manor, from my father or anyone
else. I \emph{promise}. They'll have to kill me first.''

Harry sighed. He really had no choice anymore, and he would have to live
with the consequences of this, too.

``You realize that my parents and my godfather are still going to scream
the roof down,'' he said, as they started walking back to Hogwarts.
``And my brother.''

``I don't know your parents,'' said Draco, with a sniff. ``And my mother
told me your godfather is a prat. And I \emph{know} your brother's a
prat. So that's all settled.'' He gave Harry another beatific smile.

Harry, helpless, forced to remember that at least Draco was \emph{here}
to smile instead of choked or kicked to death, smiled back.

\chapter{A Very Malfoyish Christmas}\label{chapter-16-a-very-malfoyish-christmas}

``But you \emph{can't},'' said Connor, for the twentieth time, as if he
hoped to wear Harry down by simple repetition.

Harry had to admit he was close to that. He tossed the last of his
clothes in the trunk and turned towards Connor with a sigh. ``I have
to,'' he said. ``Draco called a life debt on me. I don't have any
choice.'' He had told his twin what had happened in the forest---for the
most part. Having Connor know the extent of his magic was dangerous.
Having Connor know that he'd had an argument with Draco, chased him into
the Forest, and rescued him from centaurs was not. Of course, it would
have meant more if Connor had paid the least attention to anything his
father or Sirius said about pureblooded wizarding rituals. ``I promise
that I'll come back safe from Malfoy Manor, Connor. I can't do anything
else.''

``But you'll miss Christmas with me,'' Connor whispered. ``We've never
missed a Christmas together.''

Harry felt his mouth curve in a genuine smile. ``I know,'' he said
quietly. ``But I promise we'll spend next Christmas, and all the rest of
them, together. All right?''

His twin looked at him for a long moment, and then nodded. That will and
iron determination that Harry usually saw focused on the Snitch shone in
his hazel eyes as he said, ``But if you don't come back from the Manor
alive, then I'll hunt down and kill the Malfoys myself.''

Harry let his brother hug him, and then leave the bedroom. He ignored
the stares of all the Slytherins on the way, masterfully---better, Harry
thought, than he himself ignored the Gryffindor stares when he visited
the Tower. Of course, he'd been to the Tower many times, and this was
Connor's first trip to the dungeons. Perhaps he was just less
self-conscious.

``Finally! The prat is gone.''

Harry rolled his eyes as Draco came out; he'd been hiding in the loo,
refusing to be in the same room as Connor without insulting him. ``He's
not a prat, Draco,'' Harry snapped, tossing his last jumper in his trunk
and then looking around. He couldn't see anything else that needed to
come with him. There was the large pile of letters by his bed, the ones
that had arrived from his parents, his godfather, and Remus almost
immediately after he wrote them that he was going to Malfoy Manor. Harry
hadn't opened any except the Howlers, which he had no choice about
opening. As long as his parents didn't actually come to school and force
him to go to Godric's Hollow---and they couldn't, not when a life debt
was involved---then he was safe, and he'd deal with the letters after
Christmas.

``Yes, he's a prat,'' Draco insisted, drawing Harry's attention back to
him. ``The first thing he did when he entered the common room was insult
our color scheme. He's a plebian.''

``Draco,'' Harry said with great restraint, as he charmed his trunk to
levitate behind him, ``if you went to Gryffindor Tower, you would insult
\emph{their} color scheme.''

``Yes, but their color scheme deserves to be insulted.''

Conscious that Draco would see absolutely nothing hypocritical about
what he was saying, Harry gave up. ``Come on,'' he said, curling his
scarf around his throat. ``We'll have to hurry if we want to catch the
carriages to Hogsmeade.''

Draco, of course, discovered that he was only half-packed, and flew
around the room getting things ready. Harry leaned on the wall and
watched. Draco hummed under his breath as he packed clothes, books,
pictures, and small items that Harry could see no use bringing. He
folded all the clothes neatly, and wrapped the more breakable things in
cloth. He would have been every inch the Malfoy heir---

If it weren't for the humming.

Harry closed his eyes. \emph{Draco hums. If he can do that, I can
survive a few weeks at Malfoy Manor.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``Come on, Harry!''

Harry winced as Draco's shout drifted back to him. The other boy darted
ahead like a child, laughing and kicking up the snow behind him. Harry
walked after him much more decorously, his trunk so tuned to his
movements that it bobbed and floated up in the air when he raised his
foot to step over a snowdrift that was higher than it appeared. Harry
had learned that was a good method for making himself walk more slowly,
and for making himself learn patience.

He had assumed they would take the Express to King's Cross Station,
where Draco's parents would meet them, but Draco had laughed at the
thought of going to London for a holiday. No, he'd told Harry loftily,
they would walk to the outskirts of Hogsmeade, beyond Hogwarts's
anti-Apparition wards, and his mother would come to Portkey them back to
the Manor.

Harry had asked Draco why he rode the Express to get to school, then.
Draco had gone off into a long spiel about tradition that Harry paid
absolutely no attention to. He would either already know the pureblood
traditions that Draco referred to, or Draco would have made them up.

This wasn't bad weather for a walk, Harry thought. It was cold enough to
make his breath plume in front of him, but not so cold that he could
feel the winter digging through his clothes and making his marrow
freeze. Draco's laughter wasn't as loud from a distance. The wizards and
witches that passed them bore Christmas colors on their scarves and
robes, and the Hogsmeade houses themselves had decorations, mostly
snowflakes charmed into not melting and pinecones enchanted to glow
different colors, hanging from their eaves and windows.

``Harry!''

Harry snapped his head forward, blinking. For a moment, he couldn't see
where the cry was coming from, but then Draco put his head around a
house and motioned frantically to him. Harry sped up, and rounded the
house to find Draco tightly holding the hand of an incredibly beautiful
witch.

``Harry Potter,'' said Draco proudly, ``this is my mother, Narcissa
Malfoy. Mother, may I present Harry Potter?''

``You may,'' said Narcissa, and took a step forward, one hand held out.
It was white, Harry saw, nearly as pale as the tumble of thick hair that
she wore loose around her neck. The glow of warmth charms from the
silver necklace clasping her throat explained her lack of a scarf or
hat. Her face was fine-boned, the features elegant, in a way that
reminded Harry of Sirius, or at least would have if Sirius ever looked
like an adult. Her eyes were blue, very clear, and did not blink as she
met his gaze. ``I am very pleased to meet you, Mr. Potter.''

Harry bowed from the neck instead of taking her hand, using the delay to
scan her hand for signs of a hidden Portkey, poisoned ring, or amulet. A
silver bracelet on her left wrist radiated power, but had the pink glow
of latent defensive magic; he would have to worry about it only if he
was attacking her. He saw no signs of anything else threatening, and
willingly pressed his lips to the center of her palm.

``Mrs. Malfoy,'' he murmured. ``It is a pleasure to meet you. I come as
a guest, willing to become a friend, and to abide by the laws of
hospitality.''

He stepped back. Draco's face was blank. Harry wasn't sure what that
meant, but thought Draco probably hadn't recognized the courtesies he
used.

Narcissa Malfoy's face was a different matter entirely---alive, her blue
eyes holding the fierce, intent gaze of a predator. She had a faint
smile on her lips, one that Harry was almost sure meant appreciation and
admiration. ``No one has used those words to me in a very long time, Mr.
Potter,'' she said. ``I believe the last one was my great-uncle Black,
and he died when I was a child.''

``I prefer the old ways, Mrs. Malfoy,'' said Harry. His adrenaline was
up, thundering in his veins. He forced his hands to spread in front of
him, intent and relaxed, fingers loose to show that he couldn't be
gripping a wand. Of course, he didn't need a wand, but he doubted that
he would have to protect himself if this gambit worked. ``I understand
that you are going to take us to Malfoy Manor with a Portkey. Do I have
your word that this Portkey will land us outside the threshold of the
Manor, so that I may accept your personal invitation inside?''

``Harry,'' Draco scolded. ``You're being nonsensical.''

``Hush, Draco,'' said Narcissa. She didn't say it loudly, or warningly,
or with much of a tone in her voice at all, but Draco was instantly
quiet. Narcissa didn't look away from Harry as she pulled a pebble out
of her sleeve. ``I swear to you that this Portkey shall deposit us
outside the threshold, Mr. Potter. When we land, I shall invite you in.
I swear that no harm shall come to you during the journey, or on
arriving if you do not trust my promise of hospitality.''

``Thank you,'' Harry said, and waited until both Draco and Narcissa
gripped the Portkey before putting his own hand on it. Narcissa smiled
at him in the moments before the world whirred, someone grabbed Harry
around the waist, and they leaped forward through the twisting
nothingness that a Portkey generated.

They arrived in a field of snow, unprinted and unmarked in three
directions. Harry could feel the hum of enormous magic at his back, and
was not surprised when he turned around and saw the Manor.

The house did not sprawl, for all that it was big enough to do so. Every
part of this building had been carefully planned, Harry had learned when
studying the Malfoys, and it looked like it. The windows pointed in all
directions, but the ones looking in the same direction were always of
the same size. The gray stone that made it up varied in careful,
beautiful patterns, washing from a dark shadowy color near the
foundations to one that was almost silver at the eaves, making it look
as though the Manor were caught in a cresting wave. The manor's door was
painted a faint color that Harry knew mimicked the most ancient Malfoy
crest, which had simply been a silver serpent on a field of blue-gray.

And the wards were everywhere, massive and linked to blood and intent
and power of magic and half a dozen other safeguards that Harry could
not untangle in the moment before Narcissa spoke.

``By blood shed on the earth,'' she said, and Harry turned back in time
to see her spilling three drops of blood on the snow with a tiny silver
dagger, ``I welcome you to our home. You shall have free use of the
stone of our floors, the cloth of our beds, the fire that burns in our
hearths. You may eat freely of our bread and our meat. And if any harm
comes to you under our roof, then I will ask that the earth itself feel
the treachery in my blood and rise up to destroy me.''

Harry swallowed. It had not been the oath he would have asked for from
her, being the most formal instead of the second most formal, but
evidently he had impressed her enough to warrant it.

Of course, if he broke one of the guest-laws, or attacked a Malfoy, then
he was fair game.

``In the name of Merlin,'' he replied, ``I accept your claim. I promise
in turn to leave the stones as clean of blood as I found them, the cloth
as unstained with any foulness, the fire undamped by any mistake. I
honor the bread and the meat, and the hands that made them. And I will
ask that the earth reach through my own blood and congeal it to rock in
my veins, do I break my word on this.''

Narcissa's wound sealed with a white light, and she inclined her head.
``In the name of Merlin,'' she said, ``I accept your claim.''

``Good,'' said Draco, stamping a foot. ``Now, can we go inside? It's
bloody \emph{freezing} out here.''

``Draco, language,'' said Narcissa in the same mild tone she'd used
before, and Draco murmured an apology before scampering ahead to the
door. Harry followed. He didn't think he was ready to be alone with
Draco's mother right now.

He could feel the wards closing in around him, accepting and evaluating
him. Most of them gave way at once; they were the ones designed to keep
Muggles or Squibs away, or to search for hostile intent towards the
family. Others lingered on his shoulders like suspicious snakes, at
least until they realized the strength of his magic and the
blood-promise which guarded him. Then they relaxed and melted away, and
left Harry, blinking, to follow Draco.

The door opened before they reached it. A tall, slender man stood framed
in it, staring out at them.

``Father!'' Draco shouted gleefully, and raced towards him, arms spread
wide.

Harry set his shoulders and tilted his head back. He was about to have
his first formal introduction to a Death Eater. Of course, he had met
Bellatrix Lestrange in far more intimate circumstances, but he hadn't
been introduced.

He should have been laughing. He was not. The formality mattered. The
purebloods had used games like this---or dances, as Sirius had once told
him they thought of them---for centuries to cut out the less
intelligent, the boorish, the less magically talented, and the
rebellious, and to keep peace between and within families. This tune of
strict manners had to be heard, had to be moved to, or the other dancers
would turn vicious.

Draco turned and presented Lucius to Harry just as he had his mother.
Harry barely listened. He was too busy meeting Lucius Malfoy's eyes.

Lucius looked like his son would look if Draco had first grown older and
then frozen. Pale hair and gray eyes, yes, but Harry thought that he
must have put on a mask of ice during the first war with Voldemort and
never taken it off. Or perhaps this was his special mask for unwanted
guests.

Harry frowned slightly when his eyes went to Lucius's left arm and a
corresponding twinge traveled through his scar. \emph{Yes, I know that
he was a Death Eater. There's no need for me to have prophetic dreams
about that.}

Lucius, however, surprised him. After that cold stare, he bowed and
said, ``I am glad that my son suggested a way we might meet, Mr. Potter.
I have heard so much about you from him, and look forward to a
beneficial exchange.''

Harry breathed in deeply. There were traps in those words. He knew how
to dodge them. ``Your wife has been kind enough to grant me guest-right
with a blood-promise, Mr. Malfoy.'' \emph{I'm safe here.} ``And I assume
that your son has told you of the reason I agreed to come in the first
place.'' \emph{Draco's life debt protects me.} ``With those in place, I
see no reason why we should not speak in cheerful amicability.'' \emph{I
know that you might try anything, and I am prepared for it.}

With a slight smile on his lips, Lucius moved out of the way and used
his cane to gesture into the house. ``Welcome to Malfoy Manor, Mr.
Potter.''

``Thank you, sir,'' Harry responded, and stepped inside, his trunk
bouncing behind him. Draco had already darted ahead, yelling glorious,
incomprehensible nonsense about what room Harry would have. Harry made
his way after him, beneath the gaze of disapproving portraits.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

It wasn't actually the size of the house, Harry thought the next
evening, nor even the presence of ancient and powerful artifacts, that
made this place so different from Godric's Hollow. It was the
dance---that unheard formal music playing in the background, except when
Draco and Harry were alone, that guided everyone's movements and made
him or her hyper-aware of every little gesture, every glance, every
word.

Harry had expected to find it wearying. Much to his surprise, he was
enjoying it.

He'd slept in a beautiful room without portraits, clearly kept for
guests, with windows that faced east for sunrise-watching and a small
panel of enchanted ceiling that showed any constellations he asked it
to. A house elf had awakened him with pumpkin juice that morning, and he
and Draco, after a breakfast so solid that Harry was amazed Draco wasn't
as heavy as Vince or Greg, had raced out to have a snowball fight, sled,
fly on the now-buried Quidditch Pitch, and argue constantly about small
things that they forgot five minutes later. Draco had laughed and
laughed, hard enough to crack his lips and turn his face red with
exertion, and Harry had found himself smiling back, unable to miss
Connor or his parents that much with someone who so clearly enjoyed his
company.

Lunch had been much the same as breakfast, and then they'd sat and
listened to Narcissa play the piano and sing old history songs while
wind and snow flew around the Manor. Harry had read the songs, the
ancient method of keeping wizarding history alive before the common
spread of literacy, but had never heard them, and he sat shivering
harder than he had outside while Narcissa sang, beginning to end, the
tale of Hogwarts' Four Founders---their childhood, and how they decided,
together, to create a center and heart of wizarding education. The song
ended on a triumphant but lonely note, with Salazar Slytherin standing
outside the school after the creation of a mighty spell, just before his
legendary quarrel with Godric Gryffindor. Harry closed his eyes and
immersed himself in the last lingering notes of the music long after it
had ended.

Harry had bowed his head when the song was done, and chosen his
compliments from the long list of formal ones approved by pureblood
wizards down the generations, and the Black family in particular.
Narcissa had accepted them with an enjoyment keener, Harry suspected,
than if he had made up his own original words to praise her in. Narcissa
appeared, in her own way, to appreciate his presence here as much as
Draco did.

Lucius was---more of an enigma.

Harry lifted his head. They were sitting in the Malfoys' gathering room,
the place the family would use for meetings specifically with invited
guests or trusted relatives whom they didn't wish to bring into their
most private counsels. The portraits on the walls were all refined
enough not to stare at Harry, and the walls were crowded with books.
Draco was sitting in the chair on the left side of the hearth with a
book on the theory of wandless magic, Harry in a chair on the right side
with a book on the history of Slytherin House that Draco had shoved into
his hands with a glare that promised death if he objected. Narcissa sat
opposite Draco on a divan, waving her wand and casting nonverbal spells
that Harry didn't recognize into a silver necklace.

Lucius sat in a chair opposite Harry, heavy enough to be a throne, and
stared at Harry the entire time.

Harry met his gaze for a moment. Lucius took a sip of his wine. He
nodded to Harry, as though some point had been scored or some matter
resolved, but he didn't stop staring.

Harry shrugged and turned back to his book. He knew the confrontation
between them would not be long in coming, but for right now, he was
going to read, and accept, even thrill to, in a strange way, the feeling
of cool, appraising eyes on him.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``Harry, wake up!''

Harry blinked his eyes, groggily, and lifted his head. It was dark
beyond his window, but someone was pounding on his door and calling his
name.

``Wake up, Harry!'' came Draco's muffled voice. ``It's \emph{Christmas
morning!} Come on, Harry!''

Harry cast \emph{Lumos} wandlessly, so that he could see where his wand
was, and then used that to catch up his glasses. The room became a
little less blurry after that, but it was still dark, still around five
in the morning, and still early enough that the portraits grumbled and
shifted in their frames.

Harry opened the door, and Draco promptly grabbed his hand and dragged
him down the stairs.

``Draco,'' Harry tried to protest, as Draco tugged him towards the room
they hadn't been permitted to visit yesterday, ``shouldn't we wait for
your parents? I don't think it's proper to go in at this hour---''

``Merry Christmas, Mr. Potter,'' Narcissa's voice said softly. Harry
looked up and saw her leaning out of the door ahead of them, wearing a
smile that would have done credit to a dragon.

``They're already here,'' said Draco, and shoved Harry ahead of him.
``We do Christmas early at the Manor.''

Harry shrugged helplessly, and then caught sight of the tree in the
center of the room. All the breath left his lungs at once.

The only light came from the Yule log roaring in the hearth, and the
tree itself. Captured snowflakes hung on its branches, charmed, as in
Hogsmeade, not to melt, but also glowing with a dazzle of silver and
golden sparks that traced the outer edges of their patterns, shining and
then vanishing again. Others, or perhaps other spells, twinkled from
beneath the needles. Harry saw garlands of pure light dodging and
ducking around the snowflakes, changing their positions from moment to
moment. On top stood a star, a snowflake made up of many smaller ones,
the middle a dizzying maze, the outside fed with silver fire that seemed
to coalesce from beyond the star, making it shine like the moon.

``It's like Slytherin come again,'' Harry whispered, the only compliment
he could come up with at the moment, and the one most in his mind as he
recalled the equally cold, beautiful song from yesterday.

``Thank you, Mr. Potter,'' said Narcissa, and then nodded to the
enormous pile of presents beneath the tree. ``The three near the outer
edge are from us.''

Harry blinked. ``Mrs. Malfoy, you didn't have to---'' He had brought
gifts for them, as was a guest's duty, but they were absolutely
traditional ones: silver rings that would glow when someone hostile was
near. He had given them the first evening he arrived, and the Malfoys
had accepted them with grave thanks. He had received his gifts from
Connor and his parents before coming, and had given Draco his gift, as
well, a jumper that would warm him up or cool him down on command. He
had not expected anything from the Malfoys, simply to observe and be in
the same room with them.

Narcissa bent near him. ``And we would not have,'' she said softly, ``if
you had not impressed us so much.''

Harry nodded hesitantly, and then joined Draco, who was already ripping
heedlessly at the paper of his first gift. He let out a cheerful yell
when he uncovered it. ``A book on wandless magic! Thank you, Father!''

Lucius, sitting on the other side of the tree, nodded his response.
Harry, looking back and forth between his cold face and Draco's beaming
one, finally made out the answer to something that had been puzzling
him---how Draco could come from a home where the music of the
purebloods' formal dance played so strongly and yet act like he did
around his parents. He could do it because he knew, with perfect
confidence, exactly where he stood. He was enthusiastic about things he
was allowed to be enthusiastic about, and otherwise proper. When he
strayed over a boundary, as he had with Narcissa two days ago, she would
correct him at once, and Draco obeyed at once.

It was nothing like the relationship Harry and Connor had with their
parents, but Harry suspected it might work just as well.

``Well, Mr. Potter,'' said Narcissa, ``please open your gifts.''

Harry turned his attention to the first gift, which, when he opened it,
proved to be from Draco. He held it up and caught his breath. It was a
glass ball, and inside the ball floated a miniature model of the solar
system, the sun a dazzling speck too bright to look at it in the center,
while around it surged the nine planets and their moons. Harry gently
touched the glass, and the rotation sped. He took his hand away, and it
dropped back to the same stately dance it had been before, for every
planet except tiny Mercury, which went on zipping around the sun like a
Seeker after the Snitch.

``Thank you, Draco,'' he whispered. He had no special interest in
Astronomy, but it was the beauty of the gift that counted, and it was
very beautiful. Draco, in the middle of opening yet another gift,
grinned at him.

``Now mine, Harry,'' said Narcissa, and Harry registered the change in
name, the slightly greater warmth in her voice. She knew how impressed
he was with her son's gift, and that had earned him points in her eyes.

Harry, filled with an eerie contentment, unwrapped the gift with the
neatest silver paper. He smiled as he found a copy of the book he had
been reading yesterday, on the history of Slytherin House.

``Draco told me that you had almost no prior knowledge of Slytherin,
since you'd expected to be Sorted into Gryffindor,'' Narcissa explained.
``I thought you might like this book.''

``It's very thoughtful of you, Mrs. Malfoy,'' Harry said. ``Thank you.''
He turned to the final gift, aware of Lucius's eyes on him.

He unwrapped what seemed a blank piece of glass at first; he thought it
was a mirror, but when he moved his hand in front of it, nothing
happened. Then he made out a shadow in it, located towards the side
nearest the tree, and far more distant and shadowy figures located in
what seemed to be the back of the mirror.

Harry blinked, and then shivered a bit as he recognized it. It was a
Foe-Glass, a mirror that would show him his enemies. As they came
nearer, it would show their faces.

``Thank you, Mr. Malfoy,'' he said slowly, and lifted his eyes to meet
Lucius's. ``I am sure that I will find it useful.''

Lucius inclined his head, and said nothing.

``Oh, Mother!'' Draco exclaimed, starting up suddenly. ``I forgot! The
sun is almost up.''

Narcissa blinked, then stood. ``Excuse us, Harry, please,'' she said,
with a nod. ``Draco and I always watch the sunrise on Christmas morning.
It's a family tradition.'' She cast the Summoning Charm, and a pair of
jackets, one large and one small, streaked into the room. She bundled
Draco up, and then herself, and they left the room, hand in hand. Draco
half-leaned towards his mother as he walked.

Harry watched them go, imagining what they must look like as they
watched the sunrise together, and then turned as he heard a faint sound
behind him. Lucius had risen to his feet.

``I find myself in need of some more light,'' he said. ``My study has
candles that light themselves. Will you not come with me, Mr. Potter? We
have not yet had any private time to talk, and I would appreciate it.''

Harry nodded slowly. He was alone with Lucius Malfoy, and he could guess
some of the things that would happen in this conversation. Lucius had so
far kept his claws sheathed, for the sake of his son and his wife. He
was about to extend them now.

Harry noticed, with a sort of distant amusement almost hidden behind all
the memories of pureblood customs he was marshaling, that the shadow in
the left side of the Foe-Glass acquired a face as Lucius swept past him
and towards the door.

\chapter{The Dance}\label{chapter-17-the-dance}
Harry walked into the study directly behind Lucius, not wanting to give
him time to set up traps or firecall an ally. The room was wide and,
Harry thought, five-sided, though enough bookcases crowded the walls
that it was hard to be sure of that. More wards coiled and hissed around
him as he entered, letting him pass only because of whom he walked in
with. The walls were the blue-gray color of the front door, of the old
Malfoy crest, and bore no decoration save one portrait above the
fireplace.

Harry turned back to face Lucius's wand, drawn and pointing directly at
him. He grabbed for his own, trained reflexes springing into action.

He moved only a second behind Lucius, but that was enough.

``\emph{Probo Memoriter,}'' Lucius intoned, and a jet of faint blue light
sprang from his wand and struck Harry.

Harry closed his eyes and waited for the spell to take effect. He
reminded himself forcefully that the spell could not be offensive, or it
would dishonor both Lucius's son and his wife. Of course, the Death
Eater he'd heard stories of might be ruthless enough not to care about
that.

He felt his mind bulge and ripple oddly, and then he was remembering a
day when he and Connor had been five, and Lily had had them playing on
the lawn outside the house at Godric's Hollow. Connor had been playing
with a toy broom, catching it out of the air like a Snitch when it flew
past him. Harry had been reading a simple spellbook that described the
charms he would be practicing that night when Connor slept, things like
\emph{Wingardium Leviosa} and \emph{Alohomora.} The sun had shone, the
sky had been a brushed, cloudless blue, and their mother had sat not far
from both of them and watched them with wide eyes from which, for once,
all shadows had fled.

The remembered scene flowed to that night, when Harry had practiced the
charms and managed to levitate his pillow on his third try. Lily had
come in during the middle of that and held him tightly for a few
minutes. So vivid was the memory that Harry could feel her arms clasping
him around the waist and shoulders.

The scene flowed to one of himself, seven years old, and mentally
repeating the long list of pureblood courtesies he had learned that day
as he lay on his back in the grass and watched the stars with Connor.
Remus was telling Connor a story about the day a young wizard and a
young Muggle had become friends. Harry had already had his story from
Sirius, who, if he thought it odd that his young godson wanted to hear
about formal dinners in the House of Black, never failed to indulge him.

Now Harry was nine and managing his first bits of wandless magic, after
which he would always collapse immediately. But he persisted, and
between May and August, he improved by leaps and bounds. Once he had
looked up and seen their mother watching him from the doorway, her face
bearing a faint smile both proud and worried.

And now Harry was ten---

Harry, struggling beneath the surface of the memories, managed to open
his eyes. He realized that they were creating images that hovered in the
air between him and Lucius, playing out in dazzling color and sound.
Lucius had his eyes locked on them, a faint frown on his face.

Harry had never heard of this spell, but he had a fair idea of its
effect by now. He gritted his teeth and called up the will that had
served him so well in the forest. He shoved at the faint blue light that
crackled about him, seeking out and displaying more memories.

\emph{Leave me.}

The web of light bent and flexed around him, stubborn at first, but
Harry was more stubborn. He clenched a hand in front of him, and the web
abruptly snapped.

Harry staggered back one step, then managed to recover his balance and
look up at Lucius. The older wizard stood with his wand extended still,
watching Harry as if he were a particularly interesting species of fish.

Harry spent a few moments getting his breath back. It was impossible to
hide that he was somewhat disconcerted, but he wanted to look as
composed as possible. A weakness was a \emph{faux pas} in the dance,
worse than a mere wrong glance or gesture. A wrong glance or gesture
might be a mistake. A weakness was far more likely to be a truth,
something the weak wizard should have hidden.

``Mr. Malfoy,'' he said at last, ``you have used a spell on me without
warning and without my consent, and in response to no slight that I can
see. You extended an invitation to come to your study with you, and I
accepted it. For you to treat me as if I had broken the guest-laws is
unacceptable. I'll wait for Draco and Mrs. Malfoy to return, so I may
bid them farewell. I ask that you have a Portkey waiting so that I may
return to Hogwarts when that is done. I bid you good day.'' He turned
and walked towards the door of the study.

Lucius locked it with a nonverbal spell before Harry reached it. He
turned around, this time with his magic poised about him. He could not
remember being this coldly furious before. He had done everything
correctly. Lucius had \emph{no right} to act as he had been acting. To
be a Death Eater was one thing, but Lucius was breaking the ancient laws
left and right. It offended Harry on a level he hadn't even known
existed in himself.

``Mr. Potter,'' said Lucius quietly, ``please accept my apology. I
thought that you would attack me when the spell was lifted. Instead, you
have abided by the laws, and would even depart before I could tender an
apology.'' He dipped his head, his eyes never leaving Harry's. ``That
spell was a test, as was the gift of the Foe-Glass and my impolite
staring last night and everything else I have done since you came here.
Each time, you have responded as though you were the son of two
pureblooded wizards, and, moreover, one trained in the most ancient
courtesies. I assumed that you would act as the son of a Mudblood.
Forgive me for so assuming.''

Harry held himself rigid for a moment, waiting, but that seemed to be
the end of Lucius's little speech. \emph{He} was waiting now, and Harry
had to respond.

Of course, there was a test happening even now. If Harry reacted to the
word \emph{Mudblood}, he would confirm Lucius's assumptions, and that he
did not deserve the apology. If he attacked Lucius, he would break the
guest-laws, which, technically, had not been broken. Testing was
permitted under the dance, was in fact the biggest part of the dance,
and the spell had not been offensive or harmful.

\emph{He was digging out information from my memories to see what
Connor's strengths and weaknesses are,} Harry thought. \emph{Of course
it was harmful.}

But Connor was not actually here, and the spell had inflicted no harm,
physical, emotional, magical, spiritual, or mental, on Harry himself.
That was the set of steps Lucius was using, as proven by the fact that
he hadn't apologized for any specific effect of the spell. Harry had to
respond in the same kind of dance, or give up the protection of the
guest-laws.

\emph{So do what you have to. Survive. Make it through the holidays so
that you can make it back to Hogwarts, and Godric's Hollow, and Connor.
And forgive yourself for what you have to do in the meantime.}

Harry met Lucius's eyes again and said, ``Mr. Malfoy, I accept your
apology. I insist, however, that you ask me before performing any spell
on me in the future. I consider myself to be the son of a Mudblood and a
pureblooded wizard who has been fortunate enough to receive a nearly
complete pureblood education from his father and Sirius Black.'' He
registered the spasm of distaste that crossed Lucius's face at Sirius's
name, but he didn't allow it to dissuade him. ``I am also the brother of
the Boy-Who-Lived, and only immense guarantees of safety have allowed me
to feel comfortable in Malfoy Manor. Any deviation from those guarantees
makes me nervous. I am sure that, as a pureblooded wizard yourself, you
understand.''

Lucius studied him for a long moment. Harry waited. He hadn't missed
either the spasm of distaste, nor the flicker of shock in those chill
gray eyes when Harry had called his own mother a Mudblood. Of course,
Lucius would have understood---Harry was acting the pureblood part he
must---but he still must not have thought Harry would do it.

Harry sighed to himself. \emph{Connor would not have. He would stick to
family pride and honor, and claim Mum proudly. I wish I could do that.
And perhaps I could, if I wanted to endanger my life.}

\emph{I can't. My life doesn't belong to me. It's Connor's. And this is
what will let me get out of here and return to his side.}

Lucius at last nodded, once, and then relaxed, his mask of ice seeming
to melt for the first time. ``Please, sit down,'' he said, gesturing to
a chair in front of the hearth. ``I promise that the only spells on this
chair are ones to make it more comfortable.''

Harry nodded, murmured his thanks, and walked over to it. The chair was
narrow, hard, high-backed, and high. His feet didn't reach the ground.
Harry ignored that. If he complained about it, the advantage would go to
Lucius.

``Since it is Christmas, I believe that mulled cider may be in order,''
said Lucius, and waved his wand. Two mugs of a steaming drink appeared.
He carried one over to Harry, then took a seat in an identical chair
across from him and inclined his head. ``You may make the toast, Mr.
Potter.''

Harry didn't hesitate. Too long a pause would also convey weakness. ``To
being alive,'' he said, and drank. The cider tickled the inside of his
mouth unpleasantly, and he couldn't escape the thought that it might be
poisoned---except that Lucius would be beyond stupid to poison him now,
while Harry was still inside the protection of the guest-laws. Harry had
as much confidence in his enemy's intelligence as in his willingness to
poison him, so he drank three mouthfuls and then put the cup down on his
lap. It made his hands tingle with greater warmth than the fire could
convey.

Lucius sipped at his own. His eyes never left Harry's. A moment later,
he settled against the back of his chair and said, ``I see that you have
trained long and hard. Unusual to see such mastery of wandless magic in
one so young, never mind such a repertoire of difficult and valuable
spells. Tell me, Mr. Potter, why have you trained so? You are the
brother of the Boy-Who-Lived. The Dark Lord is vanquished. You have your
parents and your teachers to watch over you. Even my son, though I drive
him hard in other ways, has more time to learn his magic.''

Harry kept his face still. If Lucius wasn't going to refer to how he
gained those memories, neither was he. ``I do not believe in resting on
laurels, Mr. Malfoy,'' he said, and sipped at his cider again. ``I
believe the Dark Lord will come again. And we must all be ready to meet
him when he does.''

``Ah,'' said Lucius softly. ``Then your brother, the Boy-Who-Lived, also
undergoes the same intense training program?''

Every time Lucius spoke of Connor, Harry felt as though his insides were
being scraped over with a dull knife. But he ignored that as well. He
was still the weaker partner in this dance. He had to guard himself,
which in turn would guard Connor. And, he told himself, Lucius could not
know for certain that Connor did not have the same training. He had not
seen enough memories to be sure of that. ``His training is complementary
to mine,'' Harry chose to say.

Lucius's eyes flickered again, though Harry could not be sure which
emotion they held. He sipped. Harry sipped.

``My son has spoken of you a great deal,'' Lucius said. ``When I first
read his letters, I was surprised. A Potter in Slytherin? A Potter
willingly becoming friends with a Malfoy?'' He smiled, but this time
only his mouth moved; his eyes had gone cold again. ``Tell me, Mr.
Potter, why have you befriended my son?''

\emph{This is the protective father,} Harry thought, and felt
instinctively more comfortable. Lucius was not the perfect frozen
pureblooded wizard on this ground. He would be easier to shove and push
off-balance if Harry had to, and Harry thought he could do that best by
telling the absolute truth.

``Draco has befriended me, more than the other way around,'' Harry said.
``I would not wish to reject him. And I am certain that he wrote to you
about his life debt to me and how he chose to fulfill it.''

``Yes,'' said Lucius. ``Of course, he did not explain the circumstances
of the debt to me---how it came about or how you saved his life.''

``Life debts are such private things,'' Harry murmured. ``And such
ancient ones. I think it is an honor done to tradition if we invest them
with mystery.''

Lucius smiled, genuinely, and lifted his cider mug in a brief toast to
Harry. Harry checked his own emotions, and found himself caught in the
same odd pleasure he had experienced since coming to the Manor. Lucius
was a murderous Death Eater who would no doubt stop at nothing to insure
that Connor died or was given to the Dark Lord. But he could also be
counted on to stay inside certain boundaries, borders, cages, when not
actually in battle. Such boundaries permitted certain moments of mutual
respect and admiration. Harry knew his relationship with Lucius would
ever be strained, but it worked beautifully.

``Enough about my son,'' Lucius said. ``How \emph{is} it that the son of
a Mudblood received a pureblood wizarding education?''

``I wished to have it,'' Harry said. ``My family had no reason to deny
it to me.''

``Interesting,'' said Lucius, raising his eyebrows. ``I would have
thought that any son of James Potter would be encouraged to follow the
Muggle-lovers' traditions. To worship Dumbledore, for example. To avoid
the word \emph{Mudblood} as if it were a curse. To not know any
pureblood traditions as a matter of pride.''

Harry kept his face blank. That was a perfect description of Connor,
who, while he had bits of pureblood tradition in his head, didn't know
what they were, and had certainly never been taught them separate from
the rest of his general wizarding education.

``My family had no reason to deny that to me, either,'' he said.

Lucius leaned a bit back in his chair. Harry was certain he was
accepting that, processing it, evaluating it, and concluding that Harry
knew both worlds. It happened to be true. It might also make Lucius
hesitate when going after Connor, if he thought that Connor had a
similar education.

\emph{Connor will need it,} Harry thought, with an aching in his heart.
\emph{I know he'll resist it, but we} must \emph{start this summer. We
may already have left it too long in our desire to protect his
innocence.}

``Then why are you in Slytherin House?'' Lucius asked, abandoning
subtlety altogether and thus changing the steps of the dance. Harry sat
up, hearing the quicker, more dangerous music playing. ``That might
indicate that you are choosing one side of your education over the
other.''

``A student does not choose his own House,'' said Harry.

Lucius laughed at that. Harry blinked. The chuckle was rich, with a
hiccupping sound near the end of it. It was very hard to imagine a man
who laughed like that torturing and killing children. Harry would have
been inclined to think that Lucius had a cold laugh, like the one he
heard in his dreams sometimes.

``Come, come, Harry,'' said Lucius. ``You can tell me. What did the Hat
say to you when it put you in Slytherin?''

Harry tilted his chin. What he was about to do next was dangerous, but
if he allowed the change of names to pass unremarked, then he was
accepting an unequal position to Lucius's. He would not allow that to
happen.

``Why, Lucius,'' he said, ``I imagine that it said much the same thing
it said to you.''

\emph{There,} Harry thought, as the elder Malfoy's face was wiped blank
again, \emph{let him chew on that for a while, and wonder what I meant.}

There was silence for a time, while Lucius sipped his cider and watched
Harry. Harry watched him right back, wondering what the next sally would
consist of.

``Did you know,'' Lucius said at last, his voice sinking a little,
``that your magic is very powerful, Harry? Flexible and adaptable.
Nearly as strong as I remember being when I was a child.''

Harry reached out briefly towards Lucius, but could feel nothing. He hid
his own magical strength behind a series of carefully constructed
shields. Harry nodded. He had no way of knowing whether Lucius's
statement was truth or lie, and therefore no reason to take such a
compliment seriously.

``Thank you, Lucius,'' he said. ``But, in truth, I am only the brother
of the Boy-Who-Lived.''

\emph{There.} There was one flash of wide, suddenly alert gray eyes.
Harry concealed a smile. Let that rumor guard Connor. Anything that
might protect him was a help.

Lucius surveyed him in silence again. Harry drank his cider and
pretended this was a pleasant, private meeting together.

Then someone knocked on the door of the study, at the same time as
something tapped on the window. Harry looked up and saw a magnificent
tawny owl waiting to be let in with a letter around his leg. The knocker
proved to be Draco, who was calling in the next moment, ``Father? Harry?
Are you all right?''

Lucius rose gracefully to his feet and went to let the owl in. His eyes
never left Harry as he did so, however, even as he removed the letter.

``Thank you, Harry,'' he said. ``This has been most enlightening. Now,
if you wish, please rejoin my son. He sounds anxious about you.'' He
paused for a long moment. ``I cannot imagine why.''

Taking those words as the truce offering they probably were, Harry
nodded and put his empty mug on the arm of the chair. ``Thank you for
the cider and the conversation, Lucius. Both were uniquely flavored.''

Lucius smiled, though it was less a smile than a baring of teeth. ``I
look forward to meeting with you in the future, Harry Potter,'' he said.

Harry inclined his head and went out, where he had to first reassure a
frantic Draco that nothing had happened, and then tell him that, no,
that didn't mean he'd changed his mind about Lucius being a willing
Death Eater. Then Narcissa came walking back in, a black eagle-owl that
Harry recognized as Godric on her arm. Godric bore a letter from his
twin.

Right behind him came two more owls that Harry recognized as his
mother's and Remus's. Lily's owl had two letters.

With a sigh, Harry went to read his family's anxious inquiries about
whether he had been killed, and to reply that, no, he hadn't been.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Lucius waited until the door had closed before he unfolded the letter.
Of course it was a breach of the guest-laws for a guest to attempt to
read the post uninvited, but that didn't mean that Harry Potter wouldn't
find a way.

The letter was brief, to the point, and really nothing more than a
confirmation of another letter he had received some weeks before. Lucius
wrote out a brief reply, attached it to the owl's foot, and watched it
hurtle up into the blank winter sky, heading north. That really meant
nothing, of course.

Lucius walked back to finish his cider, and consider what he had learned
in this conversation, or rather stuttering waltz, with Harry Potter.

The boy was everything his son had promised, and more. Lucius could see
why Draco was so fascinated. Harry's magic made his own pulse pound with
attraction to the power, interest in the wielder, wariness in case it
was turned on him, and the competitive desire to match that power with
his own.

What he had not known was that Harry had such full command of wandless
magic, of spellbreaking, and of pureblood courtesies. He would have done
James's grandfather, the last Potter really worthy of the name,
proud---and he would have done him proud as a scion of eighteen or
nineteen, ready to take his place as formal heir of the family. Control
like that was unnatural in a child so young, just as the powerful magic
was. Lucius knew of no reason that Harry should possess it.

Now that he was alone, he let one fist clench a little at the lost
opportunity that the \emph{Probo Memoriter} spell represented. He had
seen that the Potters had trained their elder son hard, but he had not
learned the purpose behind the training, nor what kind of education
Connor Potter might have. Of course, Draco thought the boy was weak, but
Draco was too absorbed in both Harry and himself to make rational
judgments of that kind.

And then Harry had snapped the spell with a minor effort, and acted as
an offended pureblood heir would, instead of the hot-tempered,
Muggle-loving boy Lucius had expected to find.

\emph{Well, that only makes sense, doesn't it? He does have a temper,
but he keeps it hidden. And he is not a boy, whatever his age.}

Lucius let a faint smile play around his lips. Of course, the Potters
had already chosen the side that would lose in the end---the letter he
had received today was proof of that---but he felt a fierce gladness
that he would get to face an enemy like Harry Potter on the battlefield
before that end.

\emph{If the boy} could \emph{be turned\ldots{}}

Lucius did not let himself think like that, though. It was possible that
Harry would be turned, by his friendship with Draco and his presence in
Slytherin House if nothing else, but eleven hard years of training did
not seem to have altered him into the kind of wizard who would even
entertain it as a possibility. More, the boy preferred the most ancient
ways, for all that he had followed the modern dance without missing a
step. Pureblood customs that formal most often ended by forming people
who would break before they would bend.

And yet, the boy had said \emph{Mudblood}, as if he spoke it every day.

Lucius briskly shook his head and snapped his fingers to call Dobby with
his mantle. He was spending too much thought on this young friend of his
son's. It was time that he leave on this errand for his lord. He had to
retrieve a certain item hidden on the coast of Scotland. He wanted to do
it, and then be home before lunch, so that he might spend Christmas with
his family.

\emph{And our most unusual guest, of course.}

\chapter{Interlude: Concerned Relatives}\label{chapter-18-interlude-concerned-relatives}

\emph{December 24th, 1991}

\noindent Dear Harry:

It's so lonely here without you! The tree is gleaming, and there's a big
pile of presents underneath it, and Sirius and Remus are singing silly
Muggle Christmas carols, but I still wish you were here. Did you really
\emph{have} to go to the Malfoys' house? I could have had Hermione look
in the library to see if there's a way to remove life debts without
killing the other wizard. I bet there's a way.

I'm sorry about all the Howlers Dad and Sirius sent you. I think it was
awful of them, and I made them promise to apologize. Dad's even writing
you a regular letter now. I hope it has an apology in it.

I've got to go. We're going to have mulled cider and then go walking out
in the snow. Then it's coming back and sleeping the night away until
tomorrow!

Have a Merry Christmas, and give Malfoy a big punch in the nose from me.

Love,

\emph{Connor.}

\noindent \linebreak \emph{December 26th, 1991}

\noindent Dear Connor:

I miss you, too. I meant what I said about spending every Christmas
together from now on. It feels unnatural to be apart from my twin
brother for this long.

I promise, it's not awful here. The Malfoys are purebloods, so they do
things differently than we do, but they've still made me welcome and
even comfortable, in a weird way. They gave me gifts, which they didn't
have to do. They haven't said anything disparaging about Mother or
Father, and Draco and I play in the snow all the time. You ought to see
Draco when he has snow in his hair. He's really just a normal kid,
Connor. You ought to get to know him when we're back at school.

Mrs. Malfoy is very cool and proud and elegant, and one of the most
beautiful women I've ever seen. I've treated her like I would one of
Sirius's relatives. She seems to accept that, even appreciate it. Mr.
Malfoy has also made me welcome, though he's even more reserved than his
wife. That's all right. No one's tried to kill me or poison me or stab
me with a sword in the night.

I certainly will not give Draco a punch in the nose from you. But a
snowball down the back of his jumper isn't out of the question,
especially if he doesn't stop whining at me to come play outside when I
am busy writing letters.

I'll see you in a few weeks.

Love,

\emph{Your brother, Harry.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\noindent \linebreak \emph{December 24th, 1991}

\noindent Dear son:

All right, yes, the Howlers were uncalled for. Your brother scolded me
for embarrassing you in front of the Great Hall. I remember how much I
hated it when my mother did that to me, and I apologize.

But the Malfoys! They've insulted and belittled the Potter line for as
long as both our families have existed. You don't know the terrible
things they've done to us---you were too busy learning courtesies. I
suppose the courtesies are important now, since they're helping you
survive there, but you should know that Abraxas Malfoy, Lucius's father,
once challenged my father, John, to a duel, and then tried to curse him
even before the duel properly began. You can't trust a Malfoy, just as
you can't trust a Slytherin. Be careful, son.

I've written to Headmaster Dumbledore asking about a Re-Sorting for you
again. He hasn't written back yet, but I'm hopeful.

I know that you couldn't have gotten out of the life debt, but I do wish
that you were here at Godric's Hollow with us, where you belong, rather
than in that den of snakes.

Be safe.

\emph{Your loving father, James.}

\noindent \linebreak \emph{December 26th, 1991}

\noindent Dear Father:

You don't need to apologize for the Howlers. I know that you were
worried about my safety, and I didn't answer any of the letters that you
sent me otherwise. To tell the truth, I didn't have the courage to open
them. I knew what they would probably say, and I knew I could not change
the circumstances of the life debt, and had to come with Draco anyway.

The Malfoys have been lovely to me. They even gave me gifts, which they
didn't need to do. They haven't said anything about the Potter line, and
I haven't insulted theirs. The portraits sometimes insult me, but it's
easy enough to ignore them.

I'm glad that you've written to Headmaster Dumbledore, Father, and I
wish you good luck in your query. I think he will probably say no, but
thank you for writing. It is a dream of my heart to be among
Gryffindors.

\emph{Your loving son, Harry.}

\emph{}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}


\noindent \linebreak \emph{December 24th, 1991:}

\noindent Dear my son:

I know that will return alive and well from the Malfoys', so I do not
feel the need to warn you to be careful. Here is a list of things that
you may want to look for:

Do Lucius or Narcissa Malfoy ever mention Connor in conversation?

Is Narcissa Malfoy Marked as a Death Eater? We could never find out if
she was, or if she served the Dark Lord in some less official capacity.

How jealous of Connor is Draco? I cannot trust half of what Connor says
about him, as he knows Draco mostly as a Slytherin and the boy who has
taken his brother away from him. (When you return to school, spend some
more time with your brother. He is feeling neglected).

Has either of the Malfoys made any threatening moves toward you?

Are there any Dark artifacts on display in their house?

I look forward to hearing from you, son. In the name of the trust and
honor that we both share,

\emph{Lily Evans Potter.}

\emph{December 26th, 1991}

\noindent Dear Mother:

Lucius Malfoy tried to pry information about Connor out of me, using the
\emph{Probo Memoriter} spell. I snapped it, and used pureblood
courtesies to force him to apologize. He then danced with me for a good
half hour on the topic of my training and Connor's training. I managed
to hold him off this one time, and I do not believe that he discovered
anything important. Mrs. Malfoy hasn't mentioned Connor at all.

I've seen Mrs. Malfoy's arms on several occasions as she plays the
piano. She bears no Mark.

Draco doesn't seem to think of Connor at all, now that we aren't at
school. It's odd. He always talks about him there, as the ``Gryffindor
prat'' or ``your prat of a brother,'' and seems jealous whenever I leave
to spend time with him. Here, he talks about himself and me and the
gifts that he got, and we're either playing or reading or he's begging
me to play or read. I don't know if he strictly thinks of Connor so much
as he thinks of him as a Gryffindor.

(I didn't realize that Connor was feeling neglected. Please convey my
apologies to him, and tell him that we'll certainly spend more time
together once we're back at school).

Lucius Malfoy threatened me with \emph{Probo Memoriter}, and obliquely
in our conversation, but nothing since then. Mrs. Malfoy seems glad that
I'm friends with her son, and has said nothing at all political.

There are no Dark artifacts openly kept about, though I have noticed
several of the portraits holding images of them. I suspect that the
artifacts may in fact be stored in the portraits, which is clever. I
will have to work out how they did that.

\emph{Your dutiful son, Harry}.

\emph{}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

\emph{December 24th, 1991}

\noindent Dear Harry:

Sirius has finally stopped shouting about your going to the Malfoys' for
Christmas, so it's rather quiet here. Well, it will be, once Sirius
stops singing those silly carols and pestering me to join in. I should
never have taught them to him.

I hope that you are happy with the Malfoys, and that your Christmas is
going well. I would not fear too much for your life. While you are under
their protection, and especially the life debt protection of their son,
they can do nothing to hurt you. And I know that you're too smart to
step out of those protections on purpose.

Come back safe to us, and make sure to visit with us over Easter
holidays. It seems too long since I've seen you, and I'm not used to the
noise that just one little boy makes around here! I need two!

\emph{Love, Remus Lupin.}

\emph{December 26th, 1991}

\noindent Dear Remus:

Thank you for writing to me. You didn't have to.

I'm glad that Sirius is reconciled to it now, and sorry that he was
upset. Please apologize to him for me. I know that he hasn't written me
a letter because it would be like admitting he was wrong, but you don't
have to say that part.

The Malfoys have been---a pureblood wizarding family. This isn't like
Christmas at Godric's Hollow, but it \emph{is} very interesting, and I'm
glad I came. I have learned many fascinating things to tell you over
Easter holidays, which I will certainly spend at home, which is my
proper place.

\emph{Love, Harry.}

\chapter{Between Brothers}\label{chapter-19-between-brothers}

Harry swiveled between opposing currents of air, his eyes locked onto
the gleam of gold ahead. He knew it was going to dive an instant before
it did, and he was beneath it, catching it and holding it snugly in his
palm.

The commentator, who had called each of Harry's moves before this with a
tone of shock bordering on awe, now seemed stunned into silence. It was
a moment before he could cough and call out, ``And Potter catches the
Snitch! Slytherin defeats Ravenclaw, 250-100.''

The cheer that erupted from the Slytherin stands made Harry feel good.
It was almost enough to drown out the hissing from the Ravenclaw and
Gryffindor stands, and the corresponding sink in his heart. He landed,
carefully, on the far side of the field, and climbed off the broom to
stretch his legs. He felt---all right, really. He didn't mind defeating
another team that Connor wasn't on. He would just have to watch what
happened in the Gryffindor-Hufflepuff game to insure that he wasn't
going to take the Quidditch Cup away from Gryffindor.

He only had a moment to relax before the rest of the Slytherin Quidditch
team swooped down on him with triumphant roars. Harry blinked as Marcus
Flint actually picked him up and shook him, before enveloping him in a
bone-crushing hug. He cackled and whispered gleefully in Harry's ear,
``You're all right, Potter, really,'' before opening his arms and
tossing Harry to the Beaters, so they could embrace him and roughly pat
him on the back in turn.

Harry blinked and tried to protest, but they weren't listening.
Slytherin and Ravenclaw had been tied at one hundred points each, and
the rest of the teams had, apparently, been watching the Seekers like
falcons, all the while trying to steal the Quaffle from their own very
evenly matched opponents. No one had sent Bludgers at the Seekers, too
afraid of giving the opposing team a chance to gain control of the balls
and hit their Seeker in turn.

Harry hadn't been aware of it. He'd dodged the other Seeker, sought out
the Snitch, kept it in sight, and caught it as soon as he could. He had
a distant feeling of gladness. He wouldn't have wanted the pressure.

He walked back to the changing rooms in the midst of the team, listening
to jokes cracked at the expense of the Ravenclaws in wonder. The
Slytherins had never treated him like this before. Mostly, they'd seen
him as Draco's odd little hanger-on, and treated him like an extension
of Draco, or an extension of Connor when the Gryffindors had done
something to annoy them. Harry had gotten used to having Draco as his
only friend in Slytherin, a situation that only convinced him further
that he really belonged in his brother's House.

Now he shed his green robes for the first time in comfortable
companionship, and even smiled when Marcus Flint performed an
``interpretation'' of the Ravenclaw Seeker, all flailing arms and
popping eyes, that had the others roaring in more laughter.

``Um, Harry. Can I talk to you for a minute?''

The laughter ceased at once, and Flint spun, getting between Harry and
the door. ``No hexing our Seeker allowed, Gryffie,'' he snapped. ``We
won, fair and square. Go away.''

``It's Connor,'' Harry said, shoving at Flint's shoulders. ``He's hardly
going to hex me.''

Flint stayed right where he was, blocking Harry's access to and sight of
Connor, both. ``I wouldn't put it past the Gryffindors,'' he sneered.
``They were upset that their precious Ravenclaws couldn't defeat us.
Next thing, they'll be saying that they managed to win the match we had
against them by something other than dumb luck.''

Harry could imagine how Connor's face would be flushing at \emph{that}.
He hadn't revealed the secret of Harry defeating the Lestranges to
anyone else, but he did wince every time someone mentioned his
spectacular Quidditch victory.

``Let me talk to him, Flint,'' Harry said, as calmly as he could. ``He
only does want to congratulate me on the game, I'm sure.''

Flint sneered at Connor again, and then told Harry, ``Five minutes. Then
we're having a party in the dungeons, and you better be there, or we'll
find you, turn you into a turtle, and crack your shell.'' He and the
rest of the team poured away, leaving the room suddenly thunderously
quiet. Harry blinked and rubbed his ears, grateful that he could feel
them. He'd been flying for over an hour in the chill January air, at
speeds and heights that couldn't help but steal the warmth of movement
away.

``Harry,'' said Connor. ``Congratulations on winning the game.'' His
voice was oddly formal.

Harry nodded back, at a loss for words. They'd been back at school for a
few weeks, and so far his promise to spend more time with Connor was one
he hadn't pursued. Draco kept him busy, and so did the fiendishly long
and difficult and frequent Quidditch drills before the match with
Ravenclaw. Harry had often caught sight of Connor watching him from a
distance across the Great Hall, but there was always a Slytherin in the
way when he went to talk to him. After this victory, Harry suspected,
there would be more than ever, as much out of genuine friendliness as
the need to train or a dedication to keeping him apart from Gryffindors.

Connor shifted back and forth. ``Father heard back from Dumbledore,'' he
said after a long moment. ``The request for Re-Sorting failed.''

Harry managed a smile. ``I thought it would.''

Connor leaned forward, suddenly intense. ``I only have one thing to ask
you, Harry,'' he said. ``I thought it would be more, but you have a
party to go to in five minutes, after all.'' His tone as he said that
made Harry wince.

``Go ahead, Connor.''

``Do you \emph{like} being in Slytherin?'' Connor asked him, blunt as a
hammer. ``Do you really like going to parties in the dungeons and
spending all your free time with Draco Bloody Malfoy?''

Harry winced again. His suggestion that Draco and Connor get to know
each other after Christmas holidays had gone over spectacularly badly
with both of them. The one lengthy meeting Harry had had with his twin
before this one had been to plead with him not to hex Draco's ears off,
after Draco made an ill-timed comment about Hermione.

``It's not a matter of liking, Connor,'' he said quietly. ``Most of them
are pretty indifferent to me most of the time, and I know that I'm just
a toy for Draco, a prize that he can show off. I think he'll tire of me
quickly, maybe before next year. Then I'll have more time to spend with
you.'' He smiled, hoping that was what his brother wanted to hear.

``But you don't actively hate it, and you're not pining for Gryffindor
the way you were at the beginning of the year,'' Connor summed up.

``Connor\ldots{}''

But his brother was pulling away, a grimace on his face. ``That was all
I wanted to know,'' he said, and walked away.

Harry started to go after him, but a green bolt of light he didn't
recognize barred his way, and then Flint and the others came to drag him
off to the party. Harry remembered little of it afterwards, blurred as
it was by his grief and bewilderment over Connor, except that Draco had
staged a recreation of the game that included a bunch of peas,
representing the Ravenclaws, falling all over the table in shock when a
salt shaker, representing Harry, caught the grain of salt he'd spelled
to shine gold like the Snitch.

What bothered Harry most about that memory was that he remembered
laughing, with all the others, and then wondering what he was becoming.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Harry hissed under his breath as Snape examined his potion. It wasn't
the same glass-cleansing potion as the other first-years were brewing.
Snape had assigned him a complicated sleeping potion that Harry
privately suspected was another part of the preliminary steps in the
Wolfsbane improvements. Harry hardly dared do less than his best, not
only because that might end up costing an innocent werewolf his or her
life, but because Snape would know. Snape suspected that anything less
than perfection was Harry not doing his best, in fact.

``Very good, Mr. Potter,'' Snape pronounced. ``I see that \emph{someone}
from your family has finally inherited a smidgen of talent. Fifty points
to Slytherin.''

Harry flinched and lowered his head, hearing the murmurs coming from the
Gryffindor side of the room. It was the most points Snape had ever given
in a single class, and even given the fact that he'd been handing points
to Harry since February started, it was a bit ridiculous.

Connor led the objection. Harry loved him for that, even as he feared
what would happen to his twin for exposing himself to Snape's wrath. His
brother had led Gryffindor to victory over the Hufflepuff Quidditch team
last weekend, though, and Harry doubted that he could have stopped
Connor now with anything short of a \emph{Stupefy} spell. ``Why is Harry
making a different potion than the rest of us, Professor Snape? None of
the rest of us knows how to do it. Maybe he's just boiling water over
there and tossing random ingredients in, and you're giving him points to
make yourself feel better.''

That touched off a few shocked giggles among the Gryffindors, which
lasted precisely until Snape rounded on Connor.

``Giving points to Slytherin is the only thing that makes this wretched
class tolerable for me, Mr. Potter,'' Snape said, his voice colder and
softer than Harry had ever heard it. ``It reminds me that competent
Potions students do indeed exist in the world, and that I do not need to
kill myself because none of my students can grasp the basics of my art.
I do have talented students, simply not ones who are convinced that they
know everything there is to know without my instruction---'' a glance
stabbed Hermione ``---or who add any ingredient they please without
bothering to read the instructions---'' a cool stare at Ron ``---or who
speak up and disrupt the rest of the class to distract attention from
their own incompetence.'' He was staring at Connor now. ``Detention with
me for a week, Mr. Potter, to be served at eight-o'-clock every night.''

``But---'' Connor said, and then slammed his mouth shut. He turned back
to the glass-cleansing potion, his movements furious. Harry winced as he
made three mistakes in the next minute.

Eight-o'-clock at night was the time that the Gryffindor Quidditch team
had taken to practicing on Tuesdays and Thursdays.

Harry looked up to see Snape watching him, expression merciless.
\emph{Object,} his eyes said, \emph{and I'll add more time to it.}

Harry glanced away and bottled his potion, aware of both Snape's eyes on
him, pleased, and his twin's eyes, wide and betrayed.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Harry was getting desperate.

It was the middle of March, and still neither Ron, Hermione, nor Connor
had approached him about the Philosopher's Stone. Oh, there had been
some sidelong stares, some conversations between the three of them that
hushed when Harry walked into Gryffindor Tower, and some mutters between
Ron and Hermione when he passed in the halls, but nothing like the
coordinated effort to pry his secrets out of him that Harry had expected
by now.

They \emph{had} to move soon, Harry thought. The end of the school year
was only a few months away. Come summer, Dumbledore would have the time
and the leisure to move the Stone elsewhere, and probably would; Harry
had the sense that keeping the Stone where it was had been a stopgap
measure at best, always intended to be temporary. Then Connor would lose
an easy chance at heroism, and a victory that would be truly his.

So Harry decided to lie, again. He knew that his brother's silence
around him, his faint smiles and his deliberately shorter visiting times
with Harry, were born of suspicion that Harry was actually enjoying the
dubious attractions of Slytherin House. It shouldn't be too difficult to
work with that, and get Connor to sit up and pay some fucking attention
to what he was doing.

So, on a Wednesday night just before curfew, Harry went up to Gryffindor
Tower. He gave the Fat Lady that week's password---\emph{strong of
soul}---and she opened. Harry glanced quickly around the common room,
making sure to breathe loudly enough that everyone looked up at him.

``Where's Connor?'' he asked.

``Upstairs,'' said one of the red-headed twins who were Ron's older
brothers. Then he grinned. ``Say, Harry---fancy trying a sweet?'' He
held out a tray of sweets covered with oddly-glowing spells. Harry would
have known not to try any of them even if not for Connor's emphatic
warnings to never eat anything the twins gave him, \emph{ever.}

``No, thanks,'' he said, and then ran up the stairs to the first-year
boys' room.

Connor was alone, thank Merlin, reading his Transfiguration book. He
glanced up and gave Harry a distant smile.

``Harry,'' he said. ``What's the matter?''

Harry exhaled loudly, shifted from foot to foot, and chewed his lip. He
had the feeling he was overdoing it, but if he was too subtle, then
Connor might not think anything was wrong. He did at least succeed in
gaining his brother's attention, as Connor laid down his book and leaned
forward.

``Harry,'' he said. ``What's wrong?''

``Nothing,'' said Harry, shaking his head. ``I thought I could talk to
you, but---no, this was a bad idea. I'll leave.'' He turned towards the
door.

Connor spelled the door shut before he could leave. Harry felt a moment
of odd pride. The situation reminded him of his talk with Lucius Malfoy,
though he suspected it would turn out far differently. For one thing,
Harry was utterly in control of this conversation.

That made him feel odd, so odd that he missed Connor's next query, and
only snapped back to reality when his brother shook his shoulder.
``Harry, I think we should go to Professor McGonagall,'' he said,
looking almost frightened. ``Or, at least, Hermione.''

``No,'' Harry whispered. ``I have to talk to you. You're the only one I
trust.''

Connor perked up considerably. ``What is it, Harry? You know I'll help
however I can.''

Harry met his brother's eyes and said, ``Connor, there are whispers in
the dungeons. I think that someone's plotting something. Maybe not the
Slytherins, but they all know about it. They stop talking whenever I
walk into the room.'' He made sure not to lay any emphasis on the words,
so as not to say that he thought the Gryffindors were doing the same
thing.

Connor leaned nearer, eyes wide. ``And what do you think they're talking
about?''

``The Philosopher's Stone,'' Harry whispered. ``I'm sorry that I didn't
come and talk to you about this before, Connor, but---but I suppose I
thought I was betraying Slytherin honor. I'm sorry. I didn't think.''

Connor sat back from him. ``So what changed your mind?'' he asked. ``Did
you finally realize there's no such thing as Slytherin honor?''

Harry stared at him. \emph{That}, he hadn't expected. He supposed that
Connor had been spending more and more time with Ron, since he hadn't
spent it with Harry, and that that had influenced him.

For just a moment, he felt the most nonsensical urge to insist that his
Housemates did too have honor.

Harry shook it off. He couldn't afford silliness like that. He had to
hurry up and give Connor the clues that he needed, and then get back to
the dungeons before he was missed. Snape was given to checking at least
once a week in the tunnels around the dungeons, to insure that all his
charges were safe in the common room, and he hadn't done it yet this
week.

``You could be in danger,'' he whispered. ``That's what changed my
mind.''

``Why?'' Connor asked, and his face became skeptical. That was one of
the things that Harry loved most about him, how open and malleable his
face was. His expressions changed from moment to moment, and it was
always possible to tell what he was thinking. He didn't hide his
emotions under the layers of deception that Slytherins used, that Harry
himself had learned to use before he ever came to Hogwarts. ``I don't
think the Stone has much to do with me, Harry.''

``But think who might want the Stone,'' Harry whispered. ``And think
about the way they stop talking around me.''

It didn't take Connor more than a few moments to make the connection.
His hand flew up and settled on his scar, and he winced, going pale.
``Voldemort,'' he whispered.

Harry nodded, his second impulse. His first had been to correct Connor
from the use of Voldemort's name to the use of ``Dark Lord,'' which
really \emph{was} a sign that he'd been around Slytherins too long. ``I
think that's it. And I think that you need to try and find the Stone.
I've been looking, but I don't have many clues.'' He could reveal the
clues later, dependent on another lie, if Connor really did need them.

Connor chewed his lip. ``We could find them,'' he said. ``Ron, and
Hermione, and I.''

Harry bowed his head. ``You don't trust me. I understand.''

Connor's hand touched his shoulder, and Harry looked up. ``It's not
that, Harry,'' Connor said earnestly. ``I swear it's not that.
But---well, Hermione's good at research, and Ron's good at telling me
things I never knew about wizarding history and Gryffindor history and
how everyone thinks of the Boy-Who-Lived, and I'm good at deciding what
to do. And Ron doesn't trust or like you as much anymore, and Hermione's
not sure. Please? It's just for a little while. There's no reason for
you to involved, since you're not the Boy-Who-Lived, and you'll be in
danger, now that Slytherin House is talking about it, if you show too
much interest.''

Harry felt his heart jump a little. There was both the independence and
the Gryffindor attitude he'd wished to encourage. ``All right,'' he
said. ``Whatever you think best, Connor.''

His twin hugged him, hard and unexpectedly. ``Thank you, Harry,'' he
said. ``For coming and telling me, I mean. I know that it can't have
been easy for you, even if Slytherin honor doesn't exist.''

Harry hugged him back, and hurriedly sneaked out of the Tower, since it
was almost curfew. He held the memory of the hug to himself, and the
fact that Connor trusted him, and tried to ignore the ridiculous hurt
that Connor had said those things about Slytherin House. They were true,
weren't they, to anyone outside the House?

And, besides, Harry could recognize the potentially dangerous signs in
himself. Sometimes he thought he could slide away from Connor's side, to
find friendships and causes of his own in Slytherin. And that was
something he couldn't afford. He was born and trained to fight at
Connor's side, to defend him from Voldemort until he was old enough to
save the world.

He couldn't afford any other allegiances, any other loyalties. He had to
remind himself of that.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Snape waited outside the common room door. He smirked when he saw the
lone boy trailing back towards it, face bowed so that he didn't watch
where he was going. But his head snapped up when he was still a distance
from Snape, and his eyes were wide and wary for a moment before his face
shut down even further than it did in class.

Snape was proud of that. Harry was better at controlling his emotions
than he had been when he first came to school, and that was saying
something. Someone---Lily?---had tutored him very well in that already.
Snape intended to push him until the boy could lie with his face, which
still wasn't possible for him yet. At best, he could convey blankness
that made it difficult to tell what he was feeling.

``Well, well,'' Snape drawled, stepping away from the wall. ``What do we
have here, Mr. Potter? An insistence on wandering the halls at night.
One might wonder why.''

Harry was still, not even the sound of his breathing audible. He waited
for Snape to say what he wanted to say and then leave.

Snape moved a few steps closer, bringing his shields up further. He knew
it was impossible. All the laws of magic insisted it was impossible. But
if it were not impossible, he would have said that Harry's power had
\emph{grown} since he started attending Hogwarts. Snape certainly needed
to raise his shields higher each time. Of course, that could be the
effect of familiarity with Harry.

``This next week,'' he snapped, ``you will begin working on fifth-year
potions in our class.''

Harry inclined his head, but said nothing.

``I will also begin lending you extra books on the art of potions,''
Snape continued. ``You will read them. You will master them before the
end of the year. I do not intend to let you take the books back home
with you over the summer, for one mutt to chew to pieces in his
moon-rage and another to piss on them.''

Harry's shoulders lifted, but he only nodded.

``And finally,'' Snape finished, whispering now, ``instead of creeping
off into the deserted areas of the school to practice your spells, you
will come to me. You are very good at defensive magic, Mr. Potter, but
your offensive spells need work. You must be able to attack, not only
defend. It will cost your brother dearly some day if you do not know how
to do it. You saw that with the Lestranges.''

Harry's eyes did show a bit of shock this time before they closed in
resignation. Then he nodded again. He stepped past Snape, whispered the
password, and vanished into the Slytherin common room.

Snape watched him go, well-contented. Harry had acted considerably more
Slytherin ever since he had come back from Christmas with Draco Malfoy.
That he had survived Lucius was testimony enough to the boy's
character---or, as he still insisted on seeing it, the lack of it---but
Harry had also taken to keeping secrets, talking more often with the
other Slytherin students, walking and standing like Draco, and reacting
in class like a pureblood heir. Snape wondered if the boy realized it.

Then he snorted. \emph{Of course not. If he did, he would rush to reject
such mannerisms.}

It was tiresome, sometimes, Snape reflected, that he could not merely
tell Harry what he wished to do---raise the reputation of Slytherin
House once again---appeal to the boy's ambition, and enlist him as an
ally. But he knew Harry would recoil if he suspected that real reason,
and he would utterly refuse to act against his brother if he thought
that Snape might ultimately do something worse to Connor than detentions
during Quidditch practice.

No, he had to break Harry of his loyalties first before he could explain
why he had broken them, and coax him out of Connor's shadow before he
could show him what that shadow had done.

Snape turned back to his offices with a swirl of his robes.
\emph{Patience,} he counseled himself. \emph{Patience. You have waited
this long. You have your candidate. You are training him. Before his
seventh year, everyone shall see Slytherin rise again.}

\emph{That is soon enough.}

\chapter{Putting the Pieces Together}\label{chapter-20-putting-the-pieces-together}

``But, Professor McGonagall---''

``No buts,'' said the Head of Gryffindor House's voice, which, following
on his twin's voice, made Harry anxious to know what was going on. ``I
am very disappointed in both of you, Mr. Potter, Miss Granger. To be
caught out of bed is no trivial matter. Fifty points from Gryffindor,
each, and two weeks' detention. Also for each one of you,'' she added,
as though she thought she had to make that clear.

Harry eased closer and peered around the corner. Connor stood with his
head down in front of McGonagall, looking incredibly dejected. Hermione
stood beside him, and seemed near tears. Blaise stood smugly off to the
side, arms folded and head nodding---at least until McGonagall rounded
on him in turn.

``And you, Mr. Zabini,'' she said. ``Twenty points from Slytherin for
being out of bed after curfew, and you will serve a week's detention.''

Blaise blinked and began to splutter. McGonagall swept past him, not
bothering to listen to his objections, and down the corridor. Harry, who
was returning from one of his late-night sessions with Snape in the
second floor dueling classroom but doubted that McGonagall would be in
the mood to listen to that, flattened himself against the wall and
thanked Merlin that she was taking the opposite corridor from him.
Connor and Hermione trailed back in the direction of Gryffindor Tower,
still looking dejected.

Harry watched his twin's back in frustration. It was now May, and
\emph{still} Connor hadn't come and spoken to him about the
Philosopher's Stone. Harry didn't understand what was going on. Of
course, Connor hadn't spoken to him about a lot of things, even when
they did spend time together, but Harry could not believe it was taking
this long for Connor to put together the one mysterious, guarded
location in the school where nobody was to venture upon pain of death
with the Stone.

A moment later, he shook off his disappointment. Blaise was coming down
his tunnel, since it led to the dungeons. Harry at least had the chance
to find out what had happened.

``Hi, Blaise,'' he said, stepping casually out of the shadows. ``What
was that all about?''

Blaise froze for a moment, then forced a laugh. ``Oh, just a prank on
the Gryffindors that went somewhat wrong,'' he said airily. ``They were
carrying a dragon up to the Astronomy Tower, if you can believe that. I
suppose they dumped it over the side.''

``A dragon?'' Harry's heart began to pound. He hadn't heard anything
about that. His thoughts immediately leaped to Hagrid, whom Connor had
developed a friendship with, and then to the Forbidden Forest. Had
Connor been in the Forest? Had he encountered Quirrell?

``Yeah, a Norwegian Ridgeback, one of Hagrid's pets.'' Blaise sneered.
``I saw them with it in his cabin earlier this week, and then I saw them
take it out of his house tonight. I thought I might earn some points for
Slytherin if I told McGonagall about them being out after curfew.'' He
scowled. ``But the old cat wasn't in the mood to be reasonable.''

``And what were \emph{you} doing out of bed after curfew?'' Harry asked.

``Spying on the Gryffindors,'' Blaise retorted. ``I just told you
that.''

Harry raised an eyebrow, but didn't say anything, letting his doubting
silence speak for him. Blaise scowled at him in turn and edged away.
Harry studied his face carefully. Vince and Greg had always been too
loyal to Draco to give Harry any trouble, and they shied off from
teasing Connor because Draco did. Blaise was---different. He seemed
sometimes to take it as a personal affront that a Slytherin had a
Gryffindor brother, and had started to go out of his way lately to tap
Connor on the shoulder, laugh at him, trip him, and taunt him. Harry
hadn't given it much thought, other than nodding in agreement when
Connor went on a tirade against Blaise. It was just normal House
rivalry, just normal childishness.

\emph{Wasn't it?}

``Why did you track them down in Hagrid's house and spy on them in the
first place?'' he asked, more quietly.

Blaise gave his head an arrogant toss. ``Because I wanted to know what
they were doing, of course,'' he said. ``That half-giant is a menace. I
have no idea why Dumbledore keeps him on. Having a dragon in a wooden
house, \emph{honestly}!''

Harry eyed him for a long moment, and said no more. Blaise was already
seeking to turn matters around, from the expression on his face.

``And what were \emph{you} doing out of bed after curfew?'' he asked,
trying to look as if he had a plot and failing. ``Hmmm?''

``You'll have to ask Professor Snape that,'' Harry said with a shrug,
and then turned back in the direction of the Slytherin common room.

He could feel Blaise draw in his breath to demand an explanation, but in
the end he let it go without saying anything, and followed Harry. Harry
whispered the password---\emph{rigor mortis}---and walked quickly
through the common room. He didn't want to spend a minute longer with
Blaise than necessary.

Of course, once they were both washed and in their beds, then Harry lay
awake and thought about Blaise until it was nearly dawn.

\emph{What does he want? Could he be after Connor because he's a Death
Eater?} That made Harry frown, though; Blaise's sole living relative was
his mother, and Arabella Zabini had never shown signs of being a Death
Eater. A Dark witch, yes, but the two weren't the same thing.

\emph{Could he even be the traitor who let the Lestranges through?}

Harry tensed up for a moment, then shook his head. No. Their mother had
written him several times, and whenever she talked about the treachery,
she gave the impression that it was not only an adult but someone in the
Order of the Phoenix. Blaise certainly wasn't \emph{that}, whatever else
he was.

\emph{Then what does he want?}

Harry didn't know, but he resolved, as he finally began to drift off to
sleep, to cast \emph{Consopio} on Blaise from now on, before he left for
his late-night training sessions with Snape if possible. It would do no
one any harm if Blaise was back in bed before curfew, and sleeping when
he ought to be.

\emph{And, come morning, I can just happen to mention that Blaise was
the one who lost points for us, and he won't be very popular for a
while.}

Of course, most of that was just a distraction from the one thought he
really didn't want to think.

\emph{Why didn't Connor tell me about the dragon?}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``His name is Norbert.''

Harry frowned at Connor. His brother had finally come to talk to him,
after Harry had sent a rather insistently-worded invitation via Hedwig,
this morning, right before the Slytherin-Hufflepuff Quidditch match. He
was pulling on his gloves when Connor slouched into the training room,
ignoring Flint's glare, and came up and stared at Harry.

``And?'' Harry pressed, unable to keep a certain coolness from his
voice.

Connor shrugged. ``And we gave him to Charlie Weasley---Ron's brother.
He works with dragons in Romania. Norbert will be safe there.''

Harry let his breath out. This was the question he most wanted to ask,
and it seemed that Connor wouldn't volunteer the information on his own.
``Why didn't you tell me about it?''

Connor jerked away from him, eyes wide and hair falling into them. He
looked tired, Harry noticed, and one hand went up to rub his scar in
what Harry was sure was an unconscious gesture. ``Because I don't know
if I can trust you,'' he said, loudly enough for everyone else to hear.
``You've gone over all \emph{Slytherin}, Harry.''

The rest of the team's preparations stopped. Harry closed his eyes in
dread, knowing who would speak up next.

``And so what if he has?'' drawled Marcus Flint, stepping forward. ``We
happen to like him that way.'' He was smiling, but his eyes were hard.
Harry winced. He wouldn't put it past Flint to punch Connor in the ribs,
right here and now. The Slytherin Captain wasn't forgiving of anyone who
tried to rattle his players before a game began, unless the rattling
came from him.

``It's just words, Flint,'' Harry said quickly. ``He doesn't mean
anything by it.''

``Yes, I bloody do, Harry!'' Connor stopped, their father's temper
flaring in his eyes. ``I do, and it's time I said it! You've gone too
quiet. You hang out with Slytherins when you could come up to Gryffindor
Tower. You \emph{smile} at the most awful things they say, as if they
were actually \emph{funny.} You don't even care that they think less of
you because you're a half-blood! That's disrespectful to Mum, not just
you! You've changed, Harry, and I hate the person you're becoming!''

Harry shut his eyes, feeling as if he'd been punched. He'd had arguments
with Connor before, but nothing this serious. And in that moment, he
really would have renounced everything that made the Slytherins accept
him. He wanted to beg his brother to forgive him. He'd been hurting
Connor again, just as their mum had told him in her Christmas letter,
and he hadn't made it right yet.

And then, startlingly, abruptly, and unexpectedly, at least for him, his
hurt changed to anger.

Harry opened his eyes, and saw Connor back away from him. Harry took a
step nearer. He was shaking and couldn't seem to stop, any more than he
could stop the words that flowed out of his mouth in the next moment.

``I'm just trying to make the best of the situation, Connor! No, I wasn't
happy when I got put in Slytherin, but it isn't all awful. All right, I
joke with them and spend time with them, but they're my
\emph{Housemates.} I would spend more time with you if you seemed to
want to do it! You're barely happy any time I'm there. You'd rather talk
to Ron and Hermione. I don't blame you for---for listening to them, for
picking up their prejudices, but don't say that this is all my fault!
It's partially yours, too!''

He was shouting by the end, which had \emph{never} happened. Usually
Connor got upset and Harry stayed calm, asking for forgiveness when his
brother had spent the initial flood of his temper. But now Harry's fists
were clenched, and he saw Draco, come to wish him good luck before the
match, sag against the wall, one hand on his forehead and his face pale.
Harry was glad that he didn't have his wand. He ignored the increasing
temptation to use wandless magic.

And he kept his gaze on his twin, long enough to see shock replace the
anger in Connor's eyes, and the ashes replace the fire.

``I didn't know you hated me that much, Harry,'' he whispered. ``I---''

``Get out, Gryffindor.'' Flint's voice had gone deep and quiet as the
growl of a huge dog. ``I'm giving you five seconds to get out of here
before I pound you flat, and that's only out of respect for your
brother. One. Two. Three---''

Connor turned and walked away. Harry watched him go, and waited for the
coolness of shock to crash down on him in turn.

It didn't. He still felt angry, and the foremost impulse in him was to
make Connor pay. Shutting his eyes, he tried his best to rein in his
temper.

He opened his eyes when Adrian Pucey, one of the team's other Chasers,
pounded him on the back. ``That's more like it,'' Adrian said, his voice
aglow. ``Go out there and \emph{win.} Show the bloody Gryffindors that
they can't rattle you.''

Harry nodded back, smiled tightly, and then moved out of the changing
room, leading the team onto the pitch.

Slytherin beat Hufflepuff 410 to 190, and Harry had rarely exulted in
catching the Snitch so much. The celebration afterwards, and even the
way the entire team shielded him on the way back to the dungeons, so
that, Adrian explained, he ``wouldn't have to see any Gryffindors you
don't want to see,'' weren't half-bad, either.

All the while, Harry kept waiting for his anger at Connor to transmute
to shame, the way it would have at any other time, and to feel the
impulse to apologize to his twin.

It never came. Harry had nothing to shut in the secret box of his
thoughts that night, because he couldn't convince himself that his anger
was unjustified.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

``So Connor's too stubborn to come right out and ask you where the
Philosopher's Stone is. But I'm not.''

Harry glanced up. Hermione Granger was standing next to the table he and
Draco had found for studying in the library, her arms folded and her
intimidating gaze boring into him. Harry almost smiled. Sometimes,
Gryffindor forthrightness was an advantage.

From the blaze in his eyes, Draco didn't seem to think so. ``Go
\emph{away}, Mudblood---'' he began.

Harry said, ``Draco,'' in the way he'd heard Narcissa Malfoy say it.
Draco shut up and glowered down at his book. Harry leaned across the
table to pat his shoulder. ``I'll be right back,'' he said, and then
stood and moved away from the table with Hermione, into the deeper
corners of the library, where they were less likely to be overheard. He
did find himself craning his neck for a sight of Connor---it'd been two
weeks since their fight, and still his brother hadn't approached
him---but Hermione seemed to have come alone.

``Spill,'' Hermione said. Her arms still hadn't unfolded, and she had a
look that would have put Lily's ``scolding face'' to shame. Harry
inclined his head and admitted the truth.

``The Philosopher's Stone is behind a certain door on the third floor,
being guarded by a giant dog of some kind.''

It was miraculous to watch the way Hermione's face changed, as her
racing brain put all the pieces together. A moment later, she muttered,
``\emph{Stupid,}'' and slapped her forehead, which Harry had to admit was
also gratifying in its own way.

Then she frowned at him. ``But if it's protected, then why did you want
to warn us about it?''

``Because I saw Professor Quirrell trying to get through the door a few
times,'' said Harry. ``He'd go in, talk to the dog, and then always come
running out. Then Professor Snape warned him off. I don't think he ever
did work out how to pass the dog. But---''

``Oh, no,'' Hermione whispered, and her face had gone pale.

``What?'' Harry demanded, standing up fully.

``Hagrid said---he said that the man who gave him Norbert was asking him
about Fluffy,'' Hermione said. ``That's the dog's name,'' she explained,
when she caught Harry's blank stare.

``Fluffy,'' Harry couldn't help but repeat.

``Don't \emph{ask}, it's \emph{Hagrid},'' said Hermione, as if that
explained it all, and Harry supposed it probably did, if one knew
Hagrid. He determined to get to know the half-giant a bit better next
year. ``The man was cloaked, and Hagrid couldn't see his face, but he
told him something about Fluffy being charmed by music. What if the
cloaked man was Professor Quirrell, and he's going to try again, now
that he knows how to get past the dog?'' Her face had flushed with
hectic color now, and she looked as if she would run from the library
and try to inform Professor Dumbledore immediately.

Harry put out a restraining hand. ``It's rather odd that he hasn't tried
so far, don't you think?'' he asked.

Hermione reluctantly settled herself back against the bookcase. ``Well,
yes. But then, why hasn't he?''

``He's waiting for something, I think,'' said Harry, and frowned. ``But
I don't know what that something would be. Dumbledore's probably going
to move the Stone at the end of the year. The longer Quirrell waits, the
more of a risk he runs.''

``Maybe there are other traps, too, and he doesn't know how to get past
them,'' Hermione offered. ``Or maybe there's another deadline
approaching, something he wants to do first.''

Harry stiffened. ``Hermione,'' he asked, ``where is Connor right now?''

``In Gryffindor Tower,'' she said, frowning at him. ``As you would know
if you'd bothered to come and talk to him at all in the last two
weeks.''

``We had a fight,'' Harry said shortly. ``But---listen, is there any
time when he might be alone? Without you or Ron to protect him? Out of
reach of anything the Professors can do?''

Hermione closed her eyes and assumed an expression of intense
concentration. Harry wouldn't be surprised to know she was rattling
immense amounts of information around in her head, seeking for the
perfect answer. He knew she'd found it when her eyes flared wide again.

``The detentions,'' she whispered. ``Professor McGonagall said that
Connor was going to serve detention with Hagrid in the Forbidden Forest
next week. Something's been killing unicorns, and they want to find out
what it is.''

Harry almost told her it had been Quirrell, but checked himself. Quite
apart from the inevitable questions he'd have to answer about why he
hadn't told Dumbledore yet, Hermione would go running to the Headmaster,
and then Connor would be pulled off that detention and Quirrell would
wait for another time to strike. Just as with the Quidditch game, Harry
thought, it was better to know when and where Connor's life would be in
danger rather than rush around on it.

He thought, for a fleeting moment, that that was Slytherin.

\emph{And so?} was his next thought.

``All right,'' he said. ``I'll be with him there, Hermione.''

``But \emph{you} don't have detention,'' she pointed out, frowning at him.

``I know,'' said Harry. ``I'll sneak along. Professor Quirrell won't
know I'm there. And don't tell Connor, either, or he'll try to do
something stubborn and stupid,'' he added.

Hermione sighed, made a few half-hearted protests, and then agreed.
Harry suspected she was tired of the feud between him and
Connor---Connor had apparently spent most of his time since then moping
around the Tower---and grateful for anything that would end it.

Harry watched her leave the library, then walked back to his study
corner with Draco, rehearsing everything he would need in his head. He
stopped when he reached the table and saw Draco staring expectantly at
him, rapping one finger on the corner of his parchment.

``Philosopher's Stone?'' he asked.

With a sigh, Harry sat down and began to explain. At least he could
trust that Draco wouldn't go running to Professor Dumbledore.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Harry shook his head as Hagrid split Connor and Neville Longbottom, who
had a detention for a stupid mistake he'd made in Potions, up. Both of
them were to fire red sparks into the air from their wands if they ran
into anything dangerous, and green sparks if they found the person who'd
been killing unicorns. Except that Hagrid called it a ``creature,'' of
course. Hagrid was going with Neville, and leaving his big dog, Fang,
with Connor.

Harry waited until the sound of Hagrid's crashing had faded into the
bushes, then stepped out of his hiding place and walked along beside
Connor. Connor was so caught up in his misery that he didn't even notice
Harry at first, and then he turned around and cast him an ugly
expression in the light of the lantern he was carrying. His other hand
gripped his wand.

``What do you want, Slytherin?'' he asked.

``For you to stop acting like an idiot,'' Harry replied, falling into
step with him and brushing a trailing vine out of the way. ``It's been
nearly a month since we fought, Connor. Don't you think you're dragging
this out too long? I \emph{am} your brother, in case you forgot.'' His
own hand was in his pocket, on his own wand, and he warily watched the
bushes. So far, there was no sign of Professor Quirrell, and Fang hadn't
given any warnings, but Harry was not sure how far he trusted the dog's
nose. He would trust his own magical senses more. They weren't picking
up anything either, though.

``I didn't forget,'' said Connor, his face twisted with anger and hurt
and broken shards of pride. ``That's why it hurt so much. Why did you
\emph{abandon} me, Harry? We're supposed to be twins. Best friends
forever. We're not supposed to argue and jostle each other like we've
done. Look at Fred and George Weasley. I've never seen them have a
fight.''

``They're in the same House,'' Harry said.

Connor turned away from him. ``So you're going to let that matter more
to you than our blood relationship?''

``No, or \emph{I} would be in my bedroom right now,'' Harry said, and
brushed away another vine. The trees rustled and creaked in a wind too
high for them to feel. The lantern lit the path ahead better than a
\emph{Lumos} spell would, which Harry was grateful for. ``I came out
here when I didn't have to, when I knew it'd be hard for you to run,
Connor, so we could talk.''

``Hermione told me about the Philosopher's Stone,'' said Connor. ``That
you knew right where it was all along.''

``Yes,'' Harry admitted. ``And I wanted you to be the one to discover
it, and bring the news to Professor Dumbledore. I thought that would
make you feel important, special, happy. You'd be able to claim a
victory as truly your own, and start taking your place as a leader.''

``But it would have been you buying me the victory again,'' said Connor,
his words grinding in more pain. ``I don't \emph{want} that, Harry.''

Harry turned and caught his brother's arm, spinning Connor to face him.
Connor glared at him in the lantern's light. He had the beginning of
tears in his eyes, and he brushed angrily at the tears with the back of
the hand that held his wand.

``Then decide what you do want,'' Harry said quietly. ``The reason I've
been working so hard for you, Connor, is that I want you to be the
leader. I want you to be the Boy-Who-Lived. I want people to look up to
you. It hasn't happened so far. Ron and Hermione like you, but the
Slytherins think you're a git, and the Ravenclaws and Hufflepuffs think
about you only when you do something spectacular---like the troll or the
Lestranges.'' He saw Connor wince and close his eyes. ``It's going to
take more than that. I thought pushing you into it subtly would do the
trick, but it didn't. So. Tell me what you want. What are \emph{your}
plans? What are you going to do to unite the four Houses behind you? Woo
the pureblood wizards? Make everyone trust that you have the confidence
and the strength to take on the Dark Lord? Win allies among the magical
creatures?''

``Why should I have to do all that?'' Connor protested. ``I defeated
Voldemort when I was a baby. I know more now. I should just have to face
him again, and he'll be destroyed completely.''

Harry sighed. ``I think it will take more than that, Connor.''

``Why \emph{should} it?'' Connor stepped away from him and traced his scar
with the edge of his wand. ``This is what it means to be the
Boy-Who-Lived. I have this scar, and that's all I really need.''

Harry felt his heart melt with pity, and so melt the last of his anger.
He and Lily had done no favors by keeping Connor so blind. He really
should have learned about politics in the wizarding world from the time
he could walk, even if his love was essential to defeating Voldemort.
Their mother had found a way to teach Harry in secrecy, under their
father's nose, and Sirius's and Remus's. She could have found out a way
to convince Connor of the truth without taking away his purity.

``Connor---'' he started, meaning to apologize.

Another vine dropped from the trees above them just then, and curled
around Connor's neck. He let out a startled cry and dropped the lantern.
Harry scooped it up and held it frantically higher, ready to shoot off
red sparks to let Hagrid know they were in danger.

It wasn't a vine that dropped out of the trees in the wake of that
snatch, but a huge snake, whom Harry could almost imagine was laughing
at them instead of hissing. She wound a portion of her body tight around
Connor, and then took off into the Forest, bearing him with her.

Harry shouted and fired an \emph{Incendio} at her tail, but missed, so
quickly did she slither. He ran after her, feeling his fear and anger
give his feet wings, and his scar begin to burn.

The snake disappeared among the bushes ahead of him, but Harry could
follow the trail of bent grasses and leaves she left, and the growing
pain in his head was a sign of its own. It wasn't long before he made
out the snake coming into a clearing where a cloaked figure waited. The
snake dumped Connor at its feet and then slithered behind her master,
still making that hiss that sounded like laughter.

Snarling, Harry grabbed his wand and stepped free of the bushes.

``\emph{So.}'' It wasn't Quirrell's voice speaking, but that cold one,
which Harry had heard once before. It made his scar flare like fire, and
Connor stirred and gave a weak moan as though his scar was also paining
him. ``\emph{Harry Potter. At last.}'' The figure bent over Connor.
``\emph{And the Boy-Who-Lived, who will shortly be the Boy-Who-Died. I
have waited so long for this moment.}''

Harry gathered himself, and sprang into battle.

\chapter{The Boy Who Lived}\label{chapter-21-the-boy-who-lived}

Harry's Blasting Curse melted against invisible shields, but it had the
useful effect of making Quirrell stop reaching for Connor and stare at
him. Harry readied another spell, his mind spinning through the various
effects, looking for something that would cause Quirrell considerable
pain as well as fling him backwards.

Then the snake was on him.

She moved faster than she had when dragging Connor through the bushes,
her jaws open and her body scything the grass as she struck. Harry
darted away from her, and her mouth hit the ground, but she whirled and
headed for him again. Harry cried out, ``\emph{Protego!}'', only to have
the snake's jaws shoot through the Shield Charm and rip the cloth of his
sleeve. He stepped further back, hearing her hiss as though she were
laughing, and cast a glance at Connor.

\emph{At least I know she's a real snake, not a magical one.}

``\emph{What is this?}'' the cold voice asked, its accents harsher than
ever. Harry fought the urge to sink to his knees as the pain in his scar
became worse. Quirrell was staring straight ahead, from what he could
see, and Harry could not reconcile that cold voice with the blank
expression on his face. ``\emph{Finish him, Nagini!}''

The snake---Nagini, apparently---hissed and gathered herself. Harry had
the feeling that this strike, when it came, would be too fast to avoid.

Meanwhile, Quirrell was reaching for Connor again.

Harry cast a hand out and snapped, ``\emph{Wingardium Leviosa}!'' He
performed it wandless, so as to keep his wand pointed towards Connor. It
worked. His magic arrested Nagini in the middle of her charge and
bounced her into the air like the Muggle balloons Harry had seen on one
of their birthdays.

Harry wound up the force of the spell and threw Nagini over the
Forbidden Forest. She soared away with a trailing hiss that sounded
oddly like a cry of pain. Harry dismissed that. He wasn't thinking
clearly.

He faced Quirrell and pointed his wand.

Quirrell had stopped reaching for Connor once more. His stare this time
was more pointed, but also more leisurely, and Harry went back to trying
to think of a spell that would hurt, get around the shields, and cast
Quirrell out of range of whatever protections he had. Harry had been
squinting since he came into the clearing, but he couldn't make out the
lines of wards. These spells were more complicated than the ones he'd
trained himself to see, then.

``\emph{You are unusual, boy,}'' the voice said. ``\emph{So much power. Why
did I not sense this about you at first?}''

Harry saw no point in answering such irrelevant chatter. He had chosen
his spell. Admittedly, it was an odd choice, but this was an odd battle.
Quirrell, or whoever he really was, had had time to prepare his ground,
and Harry had not.

``\emph{Reducto}!'' he intoned, and packed behind the spell all the force
of his will, joining it to the force of his wand. He envisioned the
shields splitting and cracking, the way the egg had when the centaurs
tested him.

The spell flew straight and true, and showed the shields as it smacked
against them in a rainbow aurora of light. Harry saw faint cracks
outlining its impact, and memorized their position as the light flared
and vanished. ``\emph{Reducto}!'' he cried again, this time targeting one
of the cracks.

It shattered, and some of the force of the curse got through and to
Quirrell, who staggered. Harry came in, fast and low to the ground, just
behind the spell, trying to get Connor and drag him away before Quirrell
could recover.

The cold voice said, ``\emph{Cavea},'' a spell that Harry had never heard
of before, and blue light flashed into existence around Connor. Harry
tried to thrust his hand through anyway, and recoiled. He might as well
have tried to punch a fist through solid steel.

He climbed to his feet and got in between his brother and Quirrell---an
easy task, because Quirrell showed no signs of coming closer just yet.
Harry breathed harshly. He could feel the beginnings of sweat on his
cheeks and forehead. His heart blurred and burned in his ears, loudly
enough that he found it hard to make out what Quirrell was saying.

``What should I do, master?'' whined the voice that Harry knew from
class, minus the stutter. ``The boy is too powerful for me to easily
face.''

``\emph{Unleash me.}''

Quirrell gave a little shudder, but it was gone when he looked and
smiled at Harry. ``Yes,'' he said softly. ``That might be best.'' Then
he turned his back on Harry.

Harry snapped his wand up. \emph{Is Quirrell stupid? This is such a
prime opportunity to strike---}

\emph{No, no. He's not stupid. He must be planning something.}

Warily, Harry held his spells, and watched as Quirrell began to unwrap
the back of the turban.

Harry expected to see bare skull at most. What he saw, as the purple
wrappings fell away, was a second face imposed on the back of Quirrell's
head. The nose was stretched and pressed flat, the eyes impossible
narrow slits of crimson, the mouth a gash. The eyes pierced him, and
from the mouth came the voice in a high, cold laugh familiar to Harry
from old dreams.

His scar roared fiercely to life, sending him to his knees. Harry
couldn't hold back a cry this time, and it was echoed by a choked
whimper from Connor. A quick look over his shoulder showed that his
brother was unharmed, though he felt around the edges of the cage spell
with a bewildered look on his face.

``\emph{I should have known,}'' the voice said, in a hiss that would have
done credit to Nagini. Harry forced himself to listen around the pain in
his brow. What the voice was saying could be important. ``\emph{The
prophecy was never whole, and Peter Pettigrew has always been a fool. It
was you. The older one, the more powerful one. What I saw as a nuisance
to be dismissed was in fact the object of my desires.}'' Quirrell took a
step backwards, so that the face moved closer. Harry smelled its breath,
cold and foul as grave dirt. ``\emph{How does it feel, boy, to know that
you are facing Lord Voldemort for a second time?}''

There was a pause, as though Voldemort truly expected some sort of
answer. Harry dug his hands into the ground and gave one. ``I admit I'm
impressed, since this is only the first time I've done it. But
reassured, since I have the boy who defeated you at my back.''

The voice began to laugh, and laugh. The pain in Harry's head grew
worse, strong enough that his training couldn't fight it. He catapulted
forward and lay on the ground, losing consciousness for a brief, intense
second.

When he woke, Quirrell held him, staring into his face with his own,
normal one. Harry wanted to cast a curse, but couldn't find his breath
for a long moment. When it did emerge, it was in a sob of pain. His head
felt as if it were about to crack like the egg-shaped stone.

``My lord commanded me to be done with the Boy-Who-Lived,'' Quirrell
whispered. ``I admit I didn't foresee doing it this way, but it is
useful.'' He dropped Harry and took a step backwards. Harry scrabbled
for strength, knowing that whatever was to come would be bad.

Quirrell didn't disappoint him. ``\emph{Crucio}!''

The spell snapped Harry's weakening Shield Charm. Agony exploded from
his belly this time, and traveled outward through his limbs, rivaling
and then eclipsing his scar. Harry screamed. There was no shame in
screaming, his mother had told him once, the first evening that she
revealed he was likely to be tortured. Torture often broke a man. Harry
couldn't allow it to break him, and so the worst thing to do would be to
combat and try to override the pain. He would roll with it instead,
scream, writhe, beg, do whatever he must to emerge on the other side
alive and fighting for Connor.

He was down to babbling pleas when the curse was lifted. Harry gasped
and curled up on his side, then uncurled hastily. His sides ached with
perfectly timed bursts of anguish. It felt as though one of his ribs was
broken, though so far as Harry knew that wasn't a side-effect of
\emph{Crucio.}

``\emph{That,}'' said Voldemort, ``\emph{was payment for the first few
months I spent as a bodiless spirit, powerless to affect the world,
gazing on their celebrations, the weak fools who thought they'd defeated
me. There will be many more to come. I have years and years of suffering
to pay you back for, boy.}''

Harry lifted his head. Tears blurred his sight, and he'd shaken his
glasses off, blurring it further. But he didn't think he could ever
mistake again the figure that stood before him. He would know the sight
of Quirrell, and the sound of Voldemort's voice, until the day he died.

He did wonder, hazily, what Voldemort was babbling about, but that
didn't matter. A sequence of spells had entered his head, beautifully
timed and perfectly rendered. He could pull it off, if he could only
summon enough strength to make Voldemort angry. And it had to be the
kind of anger that would make him react without thinking, charging
forward to punish Harry physically instead of with a curse from a
distance.

Harry tested his shaking limbs, and nodded. It would have to be now. He
didn't think he could run if he took another \emph{Crucio.}

``You're the weak one,'' he said, and put as much contempt into his
voice as he could. ``Not having another measure ready in case something
like this happened to you, a backup plan? What do you think you are? A
Slytherin?'' Harry laughed weakly, and then coughed. He didn't like the
sensation in his body when he coughed, or the fact that some of the
specks that landed on the back of his hand were red, but there wasn't
much he could do about that. He \emph{did} like the fact that Quirrell
had gone tense and still, that his silence was a listening one.
``\emph{Dumbledore's} twice the Slytherin that you'll ever be. At least
his plans stand a chance of \emph{working} once in a while, and he
wasn't defeated by a \emph{baby.}''

Quirrell came for him.

Harry called on his wandless magic. He couldn't hold a wand right now.
``\emph{Wingardium Leviosa}!''

Quirrell flew into the air. He performed the countercharm, of course,
and was already coming back down, but that bought Harry a few seconds.

``\emph{Cavea}!''

That did nothing at all, as Harry had expected, but it enraged
Voldemort. ``\emph{You think to use my own spell against me?}'' he asked,
hard enough that Harry thought flecks of spit were probably flying from
the mouth on the back of Quirrell's head. ``\emph{You insolent,
impudent}---''

``\emph{Expelliarmus}!'' Harry yelled, throwing such a force of will
behind that word that he felt drained afterwards. It worked. Quirrell's
wand soared out of his relaxing grip and fell to the ground beside
Harry. Harry didn't try to touch it. He still couldn't hold it, with his
hand shaking, and he didn't want to risk contamination, as he couldn't
be sure that Voldemort wasn't linked to Quirrell's wand core somehow. He
continued speaking, not giving Voldemort a chance to get a word in
edgewise. ``\emph{Fumo! Specularis! Protego}!''

Smoke washed up from the ground around him, and the Shield Charm snapped
back into existence. Harry forced himself shakily to his feet. He
\emph{had} to run, \emph{had} to move, which was the whole purpose of
the Smoke Charm. He kicked Quirrell's wand in front of him as he
staggered forward, hoping to keep it from the Death Eater's grip as long
as possible.

He darted towards Connor, whom the blue glow of the \emph{Cavea} spell
revealed pounding on the walls of his prison and mouthing what looked
like obscenities. Harry gathered will and love both as he ran. No
trouble, no trouble, harnessing love this time, when his beloved twin
was in danger.

\emph{Crack,} he told the force of the \emph{Cavea} spell.

It did nothing at all.

Harry slid to his knees beside the prison, bracing his own hands on the
blue light. Connor met him, palm-to-palm, but Harry couldn't feel him at
all. He growled and focused the clear \emph{Specularis} window on just a
tiny point right past his left hand. \emph{You will crack. I will it so.
I want}---

A powerful rope snared him around the middle and tugged him away from
the prison. Vengeful hisses in his ear told him that Nagini had
returned. Harry struggled wildly, but he was no match for a snake as
large as she was. She carried him firmly away from the spell and Connor,
and deposited him at a pair of feet as the Smoke Charm vanished
abruptly.

Quirrell said nothing for a long moment. Harry closed his eyes and tried
to breathe. His head and his ribs and the middle of his belly, where
Nagini had grabbed him, all shouted at him in a symphony of aches. He
had never hurt so much.

``\emph{You have caused me too much trouble,}'' said Voldemort's voice.
``\emph{I would have been content to torture you to death and then pass
on. That is not enough, not now. Now you must watch your brother die.}''

Harry's anger woke.

Nagini let him go with a shriek that sounded too human to Harry's ears
as her body burst into flames. Harry paid no more attention to her,
though he had the vague impression she was rolling about, trying to put
out the fire. He struggled to his feet, snapping, ``\emph{Accio} wand!''

His wand settled into his left palm a moment later, the familiar feel of
the cypress wood soothing him and solidifying his rage. Harry stalked
towards Voldemort. He felt as though he wore immense robes, like Snape's
perhaps, and couldn't understand the feeling until he saw the grass
bending away from him, some of it beginning to smoke and take fire.
\emph{This} was his magic, spreading around him like wings, rising in a
silent, deadly wash that hummed until Harry's ears burnt. He was no
longer tired, and all his pains had vanished.

Quirrell backed away a few steps. ``M-m-master?'' This time, Harry felt
certain, the stammer in his voice was real.

\emph{Not Connor. Not Connor.} The words were under Harry's skin,
blazing in his shoulders, rife in his ears, beating just beneath the
roof of his mouth. He called more magic, and then more, more than he had
ever dared summon under Lily's supervision or even in the centaurs'
trial. The air in front of him blurred with a haze of power. It wasn't
entirely unfamiliar. Harry blinked, and caught a glimpse of green light,
and a crib beside his own, and Voldemort's startled face---

Then that was gone as someone else's magic answered his, as rich, as
powerful, as destructive. It was Voldemort's, and he was laughing, a
sound of purest exultation.

``\emph{I know more than you, boy,}'' he said, while his magic locked and
linked with Harry's, bearing an answer to every defense, a sheath for
every sword, a key for every door. ``\emph{I have had time, and more than
time, to develop my defenses. You are a worthy opponent, that I will
grant you, but you simply---cannot---stand---against---me.}''

For every one of the last five words, his magic became a battering ram
and struck at Harry's. Harry gasped as his pain returned, and then new
pains started, weak points opening and running in his defenses. Once one
crack spread, a dozen new ones sprouted. Harry tried to protect himself,
tried to spread the wings and then curl them around in front of him to
shield, but he was too new at this manipulation of raw force, and
Voldemort was not.

With a shivering of the air like a fall of dust, one of Harry's weak
points gave way. He fell to the ground, feeling the Dark magic above him
flowing over his like serpents. They twined and writhed and hissed at
him, sounding as human as Nagini, and more human than Voldemort.

``\emph{Enough toying. I would have enjoyed taking longer, but we cannot.
We must retrieve the Stone. Quirrell. Take his brother, kill him, and
then turn and use the Killing Curse on the boy. We must take no
chances.}''

``Yes, Master,'' Harry heard Quirrell say, from long ago and far away
beneath a dark sea. He managed to open his eyes against pressing weight
in time to see Quirrell stride up to the blue light and dismiss it with
a gesture. Connor lay helpless before him, crawling away and probably
trying to mouth a spell, but unable to muster any defenses.

Harry tried to lunge upward. The weight of the serpents pinned him.
Desperate, writhing, hating this with every fiber of his being, he sent
a flow of love towards Connor.

\emph{I have loved you since we were children, brother, playing
together. You were destined for a life of pain. I wanted to keep you
innocent. I waited too long. I'm sorry, Connor, so sorry. Please live. I
want that more than anything. Please live.} Live.

Quirrell's left hand gripped his wand. With the right, he touched
Connor.

A moment later, he howled.

White light, bright as magnesium, enveloped his hand. He hopped
backward, wringing it and yelling, but that didn't stop the light. It
spread fiercely up his arm, eating. He whirled around, and he was near
enough now that Harry could make out the radiance crisping his skin,
sloughing it away, revealing layers of flesh and muscle beneath that it
also consumed like a starving beast.

``\emph{Shake it off! Shake it off! Fight it!}''

The weight of the Dark magic on him was gone a moment later; Harry
thought Voldemort had pulled his power home to fight the destruction of
his host body. He leaped to his feet, the pain vanishing again, the
wings spreading, his own magic roaring in gladness. He struck home, and
hard, the Blasting Curse springing from his lips and hitting Quirrell.

Quirrell, of course, was already dying. Harry had only struck to express
his own anger, and he watched, not wishing to miss a moment, as the
light spread and captured Quirrell's face, taking his head almost
gently.

Voldemort hissed, and then a mass of dark light grew like a boil on the
back of Quirrell's head and erupted, spraying like pus into the air.
Voldemort flew low over Connor as he soared free. Connor screamed and
screamed, one hand rising to clutch at his scar.

Harry ran to him and crouched over him, shielding him both from the
sight of Quirrell's last moments and from any harm that Voldemort might
try to do him. If the Dark Lord possessed his brother now, he would have
a fight on his hands. Harry would show him.

The Dark Lord did no such thing. ``\emph{Until we meet again, Harry
Potter,}'' he said, sheer hatred in his voice, and then his formless form
flowed away over the Forbidden Forest and was gone.

Harry exhaled and glanced towards Quirrell. The flame had finished its
work. For a moment, it glowed, a dying star at the heart of a black
night sky, and then it disappeared with a \emph{crack.} Quirrell's
remains collapsed into ashes.

Harry thought of something and gripped his wand, but when he looked
around, there was no sign of Nagini.

They breathed in silence for a long moment, and then Connor whispered,
his voice shaky, ``Harry, how did I do that? What happened?''

Harry smiled and pushed the hair away from his brother's scar to trace
it with a finger. Connor shivered. The heart wasn't bleeding, Harry was
glad to note, but it did have an angry silver glow to it, like the light
that had flashed between him and Draco when he accepted the life debt.
The glow faded as Harry watched. ``You don't know, Connor?'' he asked.
``You told me the answer before the snake took you and started this
whole mess.''

Connor blinked at him. ``I did?''

Harry nodded and hugged his brother close. He tried to think how near he
had come to losing him, and felt his mind recoil. He could not
comprehend that, not right now. He could feel love, and rejoice, and he
did so. ``You said that you were the Boy-Who-Lived. You are. Voldemort
couldn't touch you. The force of your love ate his flesh. That
\emph{has} to be it. Voldemort is corrupt, he couldn't bear something so
good. One touch, and Quirrell---'' He hesitated, because he had prevented
Connor from seeing that death for a reason, and then finished, ``Was
gone.''

Connor shuddered for a long moment, his breath coming short and fast.
Then he said, ``Yes. That's it, isn't it?''

Harry nodded slowly, and closed his eyes. His pains were making
themselves felt again. He coughed, and felt something thicker than
saliva bubble in the back of his throat. He wanted to sink down on the
earth and never move again.

On the other hand, Connor wasn't safely back at Hogwarts yet, and that
thought urged him to move. He stood, gently tugging on Connor's hand.
``Get up.''

``But I'm so tired,'' Connor whispered.

``Lean on me,'' said Harry, and took Connor's weight on his left side,
the less injured one. ``Where's your wand?''

After a moment of searching, Connor found it, and they proceeded slowly
back in the direction of Hogwarts. Connor paused to fire off red sparks
every few steps.

Harry, meanwhile, depended as much on his own happiness to carry him
along as his body. He wouldn't have minded doing a dance, if he had been
up to it.

\emph{This proves it. This} bloody \emph{proves it. Connor can defeat
Voldemort. He's protected from his direct touch, and if the Dark Lord
takes another host body, the same thing can happen to it. When Connor's
strong enough, he's going to face him, and he's going to rid the
wizarding world of him.}

There were the things Voldemort had said, of course, the personal hatred
in his voice for Harry and the babble about Harry being something or
other, but Harry had already decided what to believe about that.

\emph{The Dark Lord is a liar. Who can trust what comes out of his
mouth? I would rather trust the light that ate Quirrell when he tried to
touch Connor. Light tells no lies.}

\chapter{Truth}\label{chapter-22-truth}

Harry knew that Hagrid had found them, and he knew that Hagrid had sent
Neville running to the castle when Connor babbled out some version of
the past hour involving ``Voldemort'' and ``snake,'' and he knew that
Connor was safe; he would not have been able to sleep if Connor wasn't
safe.

But he didn't remember falling asleep, or falling unconscious, or
whatever he had done to wind up being carried in Hagrid's arms back to
the castle.

``What?'' he mumbled. He twisted, and then hissed as the broken rib, or
whatever it was, pierced his side.

``It's all right, Harry,'' Hagrid said, holding him more firmly. ``Yer
brother told me what happened. You-Know-Who and all.'' He shivered, a
shiver that shook Harry, and which he rode out with all the stoicism he
could muster. ``We'll soon get yeh to Dumbledore, and he can heal yeh,
and then---''

``Where are you going with my student?''

Harry started, then moaned despite himself as that caused the pain to
work deeper. \emph{Of course. Snape.} Snape would have gotten irritated
when Harry didn't show up for their training session, and then probably
resolved to look for him. Harry had expected to receive a berating about
it the next day, since no excuse he made up for missing the faux duel
would be good enough for the professor. He certainly hadn't thought
Snape would look outside, nor that he would come upon them like this.

``You leave him alone!'' said Connor's fierce voice, before Hagrid could
say anything. Twisting his head, Harry saw his brother get in between
him and the Potions professor, hands clenched. He would probably be all
but spitting as he said the words, though Harry couldn't see his
expression. His eyes would be flashing. ``He stood up for me in the
forest, when Voldemort showed his true face, and---''

``Give him to me.''

Harry felt Hagrid hold him closer. ``He's bad hurt, Professor Snape,''
the half-giant said. ``Vomitin' blood before I picked him up. I think
Dumbledore ough' ter see to him---''

``No. Not yet. Escort Mr. Potter to the Headmaster. I am sure that he
will want to know what happened,'' said Snape. ``In the meantime, I will
take care of his brother.'' Harry managed to turn his head enough to see
that Snape was actually \emph{holding out his arms,} which made him want
to laugh hysterically. Even more than that, though, he was sure that he
wanted to stay with Connor.

``Professor Snape,'' he croaked, ``really, you don't need to. Connor
might need---''

He coughed, then, and felt the stabbing pain go deeper, and then he
couldn't stop coughing. Blood stained the front of his robe. He felt his
eyes roll back in his head, and heard a tight voice saying, ``Don't be
an idiot, Potter, I have potions that will take care of this,'' and then
he was passed over.

Connor's hand briefly touched his forehead. ``Stay safe, Harry,'' he
whispered, with the first touch of fear in his voice since they'd left
Voldemort's clearing. ``I'll see you soon.''

Harry tried to say that he didn't want to stay safe, he wanted to go
with Connor, and then Snape bore him off. The professor walked more
smoothly than Hagrid. Harry gritted his teeth and closed his eyes,
concentrating on not coughing again. He didn't want Snape to have more
opportunities to attack him.

``What did this to you?''

Harry opened his eyes, but could see little, since they were already
back in Hogwarts and moving through dim corridors at a rapid pace---and
he had his head pressed into Snape's shoulder besides. Annoyed, he tried
to sit up, but the stupid agony in his ribs wouldn't let him. He decided
to answer the question, though. The sooner he did, the sooner Snape
could heal him and he would be able to rejoin Connor.

\emph{And if he's so concerned about healing me, why isn't he taking me
to the hospital wing, anyway?}

``The Cruciatus Curse,'' he whispered. He felt Snape make a small
motion, though he could not tell if it was of fear or disgust or only
remembered pain. As a Death Eater, he would certainly have used the
curse, and been subjected to it. No one had ever claimed that Voldemort
was sane in the last year of his power.

Snape bore him through a familiar door, and into his office. He shifted
Harry in his arms, muttered a spell, and Transfigured one of his chairs
into a divan. Down Harry went, and then Snape whirled and strode across
the room, searching for something in the racks of potions against the
far wall.

Harry watched him from hazy eyes. Snape was intent, frowning, and a
moment later he snatched two vials, one of them filled with a purple
liquid and one with a clear one, and came back. Harry licked his lips
nervously. Snape had no special wish to see him die---Harry would have
felt much more uneasy if he was taking care of Connor---but he
\emph{was} James's son, and Snape really \emph{should} have taken him to
Pomfrey.

``Drink this,'' Snape ordered him, holding the vial of purple liquid
out.

Harry took it, eyed it in resignation, and then swallowed the liquid.

His breathing eased at once, and a spreading warmth swallowed the pain
in his side. When he coughed again, only ordinary spittle came out.
Harry sighed as a tremor in his limbs that he'd barely noticed ceased,
and he even managed a smile at Snape. ``Thank you, sir.''

``What happened out in the Forest?'' Snape walked over to the fireplace
and called a house elf before Harry could answer, ordering a goblet of
pumpkin juice. He indicated the clear liquid when Harry started
questioningly at him. ``This one must be taken when mixed into a drink.
That does not mean that you have to gape at me like a witless idiot
until the drink arrives, Potter.''

Harry shut his mouth. ``Connor defeated Voldemort, sir.''

``As he defeated the troll, and the Lestranges,'' said Snape. ``As he
caught the Snitch in our match with Gryffindor. Of course he did.''

Harry stiffened, then winced; his muscles still ached, although the
worst consequences of the \emph{Crucio} must be almost gone. He was
thinking back on his victories earlier in the year, though, with a trace
of regret. If he had hidden them better, then Connor would not have been
under suspicion, and Snape would have had no reason to think that Harry
was telling other than the truth.

\emph{Of course,} Harry thought, as he met Snape's eyes stubbornly,
\emph{it would also help if I didn't have a bloody suspicious git of a
Head of House.}

``He did, sir,'' he said quietly. ``Voldemort was hiding---attached
somehow, I don't know how---to the back of Professor Quirrell's head.
Quirrell tried to touch Connor, and he started \emph{burning.} Voldemort
detached himself to save his own life, and then blew away over the
Forest.''

``All of which says nothing about why you have suffered the
\emph{Crucio},'' Snape noted, almost clinically. A house elf appeared,
carrying a tray on which the goblet of pumpkin juice was prominently
displayed. Snape took it; the house elf bowed and disappeared. As he
mixed the potion into the juice, the professor never removed his eyes
from Harry. ``Or why you have enough power to kill four experienced
Aurors raging around your body.''

``Everything happened the way I told you, sir,'' Harry protested.

Snape sneered at him, then strode over and handed him the goblet of
pumpkin juice. Harry downed it without protesting. It was probably
something to make him sleep, and while that would further separate him
from Connor for a time, it would also stop Snape asking him questions,
so Harry was all for it.

He blinked when he had finished the juice. It eased the pain in his body
even further, but it seemed to do that by making him not concentrate on
it. He stared at the goblet, and nearly let it fall. Snape plucked it
from his hands and set it on the desk, then swooped down in front of
Harry and stared into his face.

``I have had enough of your excuses,'' he whispered. ``I \emph{know} that
you are not telling me the whole truth. Now I intend to leave you no
choice.'' He paused, for a long moment, and then a malicious smile spread
across his face. ``That was Veritaserum that you just swallowed,
Potter.''

Harry failed to grasp the implications for a long moment. The
Veritaserum was making him think about other things---

Then he understood.

And the slight trust he'd carefully built up in Snape, through their
dueling sessions and the tasks Snape had handed him in Potions if
nothing else, vanished into a howling whirlwind of betrayal.

Harry fought. He tried to stand, tried to move away, tried to argue. He
couldn't. All his motion was in his head. He floated there, and watched
Snape's mouth open with indifference, at the same time as his magic
strained to get at the Potions professor.

``Why were you outside, Potter?''

``I learned from Hermione last week that Connor would be serving a
detention tonight in the Forbidden Forest,'' said Harry's mouth, without
his will guiding it. ``I thought Quirrell might try to strike at him
then, since there wouldn't be any adults around. I tagged along so I
could keep him safe.''

Snape's eyes narrowed slightly. ``Why would you think the Forbidden
Forest was the likeliest place for an attack?''

``Because I saw Quirrell there in November, drinking unicorns' blood.''

Snape looked as if he would gag for a moment; his eyes certainly grew
wider. ``Merlin,'' he breathed. Then he stood and paced around the desk
for a moment. Harry took the chance to struggle against the Veritaserum
again. It didn't move, continuing to feel like a combination of stony
weight on his chest and airy lightness in his head.

Snape whirled back around. ``November. When in November?''

``A week before the Quidditch match and the Lestranges' attack,'' said
Harry's traitorous mouth. ``I knew that something would happen then,
although I didn't know that he'd be able to set Death Eaters free. I
knew there was a traitor among Dumbledore's friends. I trained and
practiced until I thought I was ready for anything, and I was.''

Snape narrowed his eyes to slits. ``You stupid, \emph{stupid} boy,'' he
hissed. ``Why didn't you come to me? Or to Dumbledore?''

``I thought that Dumbledore would tell the traitor,'' said Harry. ``And
I've always protected Connor. That's my task.''

Snape tilted his head. ``Task?''

``Since Voldemort's attack,'' Harry continued, serenely on the surface
while shrieking inside, ``it's been my job to defend Connor. Mum told me
so. That's why I learned the extra magic. I want to be able to protect
him, to kill for him and to die for him if necessary. And I want to make
myself look ordinary, so that everyone else thinks the magic is
Connor's.''

Harry didn't understand the expression on Snape's face at that. Surprise
he'd expected, but not black fury, nor the brief flash of a look that
made him seem close to vomiting.

Snape closed his eyes and hissed for a long moment, as if he needed the
sound to calm him down. Then he opened his eyes. ``Do continue about
tonight,'' he said. ``What happened when Quirrell attacked your
brother?''

``He sent a snake first---'' Harry began.

He told the whole story all the way through, punctuated only now and
then by Snape's questions, mostly asking him to clarify what spells he'd
used or to talk in more detail about Voldemort's babble. Harry let his
mouth prattle on. He sank down beneath the surface of his thoughts,
grimly examining the pale chains that the Veritaserum had wound about
his free will. He knew that he should be able to shatter them, as he'd
shattered the stone, but he'd never seen anything like them before. And
he was exhausted from the battle with Voldemort. He didn't know if he
could work up the strength to break them for some hours yet.

He finished the story, and Snape stared at him in silence for a moment.
Then he stood up and took a long, smooth step towards Harry. Harry
instinctively cowered back on the divan.

``This proves it, Mr. Potter,'' Snape whispered. ``\emph{You} are the
Boy-Who-Lived.''

Harry shook his head. ``That's not true,'' he said, and the Veritaserum
let Snape hear that it was what he really thought.

``Yes, it is,'' said Snape, his voice acquiring force, though it didn't
rise in volume. ``You are the one whose scar burned in the presence of
the Dark Lord. You are the one whom he cursed and laughed at, saying he
would pay you back for his years of suffering. He recognized his
opponent. And your power, Mr. Potter. Near a match for his. Training
will make you stronger. \emph{You} are the one who will rid our world of
him, perhaps before you leave school.''

``He wanted to kill Connor,'' said Harry. The Veritaserum insured that
everything he said was born of his ultimate convictions. ``Connor's scar
hurt when Voldemort passed above him. And he called him the
Boy-Who-Lived. If you're going to believe anything, believe that. My
scar's just a---a scar. Connor's scar is a connection to \emph{him}.''

``I would think you would want to believe me.'' Snape sneered, eyes
alight in a way that Harry had never seen before. ``After all, it would
spare your beloved twin pain.''

Harry answered reluctantly again. Merely doing so was going against the
rule he talked about. ``But it would draw attention to me. That can't
happen. Everyone's supposed to think of me as just an ordinary student.
That's the way Mum and I planned. I promised. I haven't been very good
at sparing myself attention so far, but I've got to get better.''

Snape laughed at him. ``You are \emph{not} ordinary, Mr. Potter,'' he
said. ``You never will be. I know of no other \emph{child} with your
power. I know of no \emph{child} who would receive the blast of
\emph{Crucio} and yet go on fighting. Any ordinary \emph{boy} would run
to his professors the moment he found out Quirrell's plans, or be found
and killed. You fought and planned as though it were a battle, and you
\emph{won}.'' He still had that strange light in his eyes, as if he
thought that Harry would want anything to do with him after this. ``You
are a soldier.''

``Yes,'' Harry acknowledged unwillingly. ``Mum trained me to be. But a
quiet one.''

Snape shook his head. ``I will make sure that everyone knows of this,''
he said. ``Unless you go to Headmaster Dumbledore yourself and tell him
what truly happened.'' He bowed his head and surveyed Harry mockingly
from beneath half-lowered eyelids.

Harry found himself doubting that Snape would really tell
everyone---that would just make Harry a target, and Snape didn't seem to
want that---but even a few people could be disastrous. Harry could
hardly bear being a rival to his brother in Potions or Quidditch. He
shuddered to think of what would happen if that arena should expand.

But there was an out. There had to be.

He muttered, dropping his eyes, ``All right, I'll tell the Headmaster.
But, the white light from Connor. How do you explain \emph{that}?''

Snape waved a hand. ``There are many old enchantments, Potter, magics
based on sacrifice. The life debt is merely the most common and
well-known one. You love your brother. I believe that it was your love
that spared him, not his own innate strengths, of which---'' here he
sneered again---``I believe him to have few.''

Harry snorted, but nodded as if he agreed. \emph{I know too much about
the world to produce that kind of love. I've argued too much with
Connor. It has to be his own innocence and purity that produced it. I'm
too much like Voldemort.}

``You will learn to love Slytherin that way,'' Snape said softly, his
tone a promise. ``I will see to it.'' Harry stared at him incredulously,
but he showed no sign of realizing that what he had said was completely
and utterly mad.

He stepped away, and his face became neutral again, save for a hint of
glee in the dark eyes. ``I have done enough this night,'' he said. ``Go
to Headmaster Dumbledore, and tell him the truth, or be assured I shall
find out about it.''

``Of course, Professor Snape,'' Harry murmured respectfully, and then
stood and limped to the door of the room.

``Harry.''

Harry blinked and glanced over his shoulder. Professor Snape was staring
at him, and he had no expression on his face, or in his eyes, at all.

``Well done,'' he said softly.

Harry shook his head. He knew how rare compliments from Snape were, but
he did not care to acknowledge this one.

\emph{He forced Veritaserum on me.}

Harry made his way carefully towards the Headmaster's office, willing to
seek out one of the other Professors if he had to so he could learn the
password. The Veritaserum's influence on him was fading. He would have
to choose his words carefully, but he rather thought he could convince
the Headmaster of what he wanted him to believe. He had always been a
good liar, and besides, he had the force of truth---\emph{ultimate}
truth, a power stronger than sneaky Slytherins and their underhanded
games---on his side.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\newpage

Snape smirked as he glanced around the Great Hall. It was the
end-of-term feast, and Slytherin had done well. The walls were draped
with green banners, and the cheerful noise from his charges' table was
loud, while the Gryffindors cowered at theirs and looked sullen and
resentful. The Quidditch Cup was theirs, thanks in large part to Harry
Potter's beautiful flying, and they also led in House points, so the
House Cup would be theirs in a few moments.

Harry Potter sat next to Draco Malfoy near the far end of the Slytherin
table. He was quiet, as he had been since that day Snape had forced him
to tell the truth, only rubbing his forehead occasionally. He had
managed to tame his power, and it no longer tore at Snape's shields as
it had when he first came back. Snape knew his impressions earlier in
the term had been correct, though. The boy's power \emph{had} grown.
That was supposed to be impossible.

Snape was coming to accept that the impossible was the usual with Harry
Potter, and he had decided to work with that. The boy had returned his
Potions books to him promptly, and had shown himself willing to master
fifth-year work. His dueling spells were stronger than they had been.
Snape had given the boy ``extra'' summer homework intended to improve
both his knowledge and his power, and Harry had accepted without
complaint. His rebelliousness had not gone away yet, but Snape had cowed
him sufficiently that it had been driven back underground for the time
being.

Dumbledore tapped his fork on his silver goblet and rose to his feet
just then. The chatter ceased at once, and the students turned and
looked expectantly at the Headmaster.

``I think it only fitting,'' Dumbledore was saying, ``as we cross into
summer, a time of hope and renewal for most of us, and of rest from
school---''

Most of the students cheered then, the Weasley twins the loudest. Snape
rolled his eyes. The longer they cheered, the longer they would be held
here. \emph{Idiots.}

``That we get around to the rewarding of the House Cup, the symbol of so
much effort and work during the school year,'' Dumbledore finished.
``And, I must say, all our Houses have done exceptionally well this
year.''

Snape snorted and looked at the green banners. Everyone already knew who
had won. The Slytherins waited with smiles, while the other Houses
muttered and cast harsh glances at their table.

``In fourth place, with three hundred twenty-seven House points,''
Dumbledore began, ``Hufflepuff House.''

Polite applause, mingled with sneers, from the others. Snape leaned
forward and wished Dumbledore would get on with it. Since he knew the
old man wouldn't, he began daydreaming of what James Potter would say
when he realized that his elder son had helped win both House Cup and
Quidditch Cup for Slytherin. True, Dumbledore hadn't awarded Harry any
points for that night in the Forest, but his Potions work was a large
part of the reason that Slytherin was so far ahead.

``In third place, with three hundred forty House points, Ravenclaw
House.''

Snape contemplated sending a taunting letter to James Potter smeared
with one of his experimental potions, one that would let him see the
expression on Potter's face when he read it. That might be worth it.

``In second place, with three hundred seventy-two House points,
Gryffindor House.''

Snape roused himself to glance at the Gryffindor table and smirk at the
scowling face of the boy hero. Connor Potter needed to grow up and be
reminded of his place, though not as badly as his brother had a
fortnight ago. This would not teach him that place, but it would be a
first, and most pleasant, step on that journey.

``And in first place, with four hundred seventy-two points, Slytherin
House.''

The cheers from his students were deafening. Snape moved his gaze over
them, and paused when he saw Harry was not cheering. On the other hand,
he watched the head table intently, as if he could change the figures by
sheer force of will.

Snape smirked. \emph{Not this time, boy. There are some things that are}
not \emph{going to go your brother's way.}

``But,'' Dumbledore continued, ``it seems to me that the awarding of
House points is not yet finished.''

Snape frowned at him. \emph{What is the old man babbling about now? No
one has awarded points at the feast before.}

He felt a sudden, and odd, and brief, surge of hope. \emph{Perhaps he
means to award Harry his points in front of everyone. Then he cannot
hide. On the other hand, would that be wise? To reveal to everyone all
at once that their beloved savior is not who they believe him to be?}

``We have among us students who relied on evidence not only from rumor
and hearsay,'' Dumbledore continued, ``but from their own eyes and ears.
They sought out an artifact they believed was in danger, and then
reported to me that it \emph{was} in danger, and, not least, from whom,
on the night that Lord Voldemort was prevented from seizing it.'' He
smiled amid the buzz and gasp of gossip as rumor was at last proved
fact, and smiled at two of the Gryffindor students. ``To Ron Weasley and
Hermione Granger, fifty points each for acts of tact, bravery, and
intelligence far beyond their years.''

Snape clenched the table so hard that he felt blood vessels break in his
hands. \emph{No. He cannot do this.}

``And there is among us even a greater example,'' Dumbledore went on,
voice softening perceptibly. ``To Connor Potter, who faced and defeated
the Dark Lord in the Forbidden Forest by the power of love alone, one
hundred points.''

He paused for a moment as the noise grew tumultuous, then said, with an
even wider smile, ``I believe that necessitates a color change in our
banners.''

He clapped his hands, and a wind appeared to blow through the Hall,
changing every banner it touched to Gryffindor red. The noise from the
Gryffindor table was now a happy shout. The boy hero's face had changed
completely.

Snape was shaking, and a red haze threatened to blur his vision.
\emph{There is no doubt at all of which House you prefer, Albus,} he
thought violently. \emph{No doubt at all.}

Dumbledore raised his goblet in a toast to the students. Only the
Gryffindors, Ravenclaws, and Hufflepuffs echoed him. The Slytherins
remained white, silent, and motionless to a student.

When the Headmaster sat back down, Snape leaned towards him and hissed,
``How could you do that?''

Dumbledore glanced at him and chuckled lightly. ``Now, Severus, I feel
that what young Mr. Weasley and Miss Granger did deserves some
recognition. Not least young Mr. Potter. It is not every day that a
child fights the Dark Lord and survives.''

Snape snarled. ``Then Harry Potter did not tell you what happened in the
Forest?''

Dumbledore raised his eyebrows. ``Of course he did. And his testimony
agreed with his brother's, jot and tittle. I suggested a much greater
reward, actually, at first, but young Harry was the one who persuaded me
that House points would be a fairer method of settling the debt that
Hogwarts owes to our brave Gryffindors.''

Snape snapped his head around, facing the Slytherin table. Harry was
leaning forward, staring at him.

Snape could read the ``Fuck you'' in his eyes from this distance.

He had not tamed Harry Potter's rebelliousness, after all.

Snape opened his mouth. With a few words, he could cleave this farce
apart and restore the world to the way it should be, the House Cup to
its rightful owners---

And then he would have to reveal how he had gotten the information. From
forcing Veritaserum on a helpless child.

Or, at least, a child who could play helpless with unnatural intensity,
and who was also a skilled and accomplished liar.

Snape clenched his fists. It would have been intolerable for any other
Potter to best him at this game.

But \emph{this} Potter was a Slytherin, and strong enough to down four
Aurors.

And, Snape was now convinced, the true Boy-Who-Lived.

Snape swallowed his anger. He took up his own goblet and raised it, in a
late, private toast, to the only person who would understand the
gesture, and to whom it would matter.

Harry regarded him for a long moment. Then he inclined his head in a
slight bow and swept his half-open hand in front of him at chest height.

The gesture of a challenge given and accepted, Snape found, after
racking his brain for a moment. An ancient one, one that not even
purebloods used very often anymore.

Snape sat back in his seat, sipping his goblet and watching as Draco
distracted Harry and began complaining, probably about the general
unfairness of life, and Harry answered, his hands gradually moving in
more and more animated gestures. Snape couldn't be sure whether Harry
was agreeing or disagreeing with Draco.

It didn't matter. Snape was sure that, either way, Harry would return
next year just as ready to defy him, and just as full of power and so
much a Slytherin that he remained Snape's best chance for earning his
House respect.

Forcing him to be what he was was going to be a challenge, indeed.

\emph{One}, Snape thought, as he emptied his goblet, \emph{that I am}
quite \emph{looking forward to.}

\end{document}
